### 2019-11-13 IEEE article template/conference-template.tex
before text improvements

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-11-13 article/conference-text.tex
before text improvements

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\usepackage{diagbox}
\usepackage{amsthm}
\usepackage[formats]{listings}
\graphicspath{{images/}}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\theoremstyle{plane}
\newtheorem{theorem}{Theorem}[section]

\begin{document}

\title{Unified data structures to optimize solving a complex of interrelated geometric problems\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}
\author{
\IEEEauthorblockN{1\textsuperscript{st} Vasyl Tereshchenko}
\IEEEauthorblockA{\textit{Faculty of computer science and cybernetics} \\
\textit{Taras Shevchenko National University of Kyiv}\\
Kyiv , Ukraine \\
vtereshch@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Semen Chudakov}
\IEEEauthorblockA{\textit{Faculty of computer science and cybernetics} \\
\textit{Taras Shevchenko National University of Kyiv}\\
Kyiv , Ukraine \\
semen.chudakov7@gmail.com}
}
\maketitle

\begin{abstract}
The paper is devoted to the development of efficient algorithmic tools for solving a set of interrelated problems of computational geometry. To do this, we propose to create a single algorithmic environment with unified data structures that will allow you to generate simple and fast procedures for solving problems as a whole. We build the generator on the basis of the strategy "divide and conquer". We can consider and other computational models that have integral properties for solving problems. For example, we can use a Voronoi Diagram or a Delaunay Triangulation.
Because a convex hull is key to a set of computational geometry tasks, we offer unified data structures to support it and other geometric objects based on a binary tree and, in particular, a weighted concatenable queue. This allows you to perform procedures for a set of tasks within no more than 
$O(\log n)$ time. In this case, a consistent and parallel implementation is possible.
\end{abstract}

\begin{IEEEkeywords}
Algorithmic tools,   Computational geometry, Interrelated problems set, Single algorithmic environment, A weighted concatenable queue
\end{IEEEkeywords}

\section{Introduction}
\textbf{The current situation in the field of research.} The convex hull problem arises not only in many practical applications, but also is an core tool for solving many others computational geometry problems.

There are implicit relations between such problems. Currently, the state of the art approach for solving such sets of problems is the single algorithmic environment, which takes advantage of those implicit relations to create a final software product. An example to such approach may be the usage of a generic data structures for solving different problems. Thus, the algorithmic environment allows to reduce complex problems to some basic computations.

This article introduces a new approach for solving the convex hull problem on a static set of points. Here the divide and conquer strategy is used as a base for the algorithm and the actual convex hull is maintained with a concatenable queue during the computations. The resulting algorithm has the worst case complexity of $O(n\log n)$, whereas the subroutine of merging 2 convex hull has a complexity of $O(log n)$, where $n$ is the number of points.

Henceforth a notion of a single algorithmic environment is introduced that formalizes the divide and conquer algorithm from a programmatic standpoint. The formalization allows to create a level of abstraction upon an actual implementation of an algorithm and therefore perform computations sequentially and in parallel on a more generic level.

\textbf{Relevance} consist in a large specter of application problems that computational geometry allows to solve with its methodology. Implementation of those algorithms enables in an single algorithmic environment allows to use them in the development of modern technology and apply them on large datasets.

\textbf{The goals of this article} is to design an optimal algorithms for solving the convex hull problem on a static set of points and to create a single algorithmic environment on the divide and conquer principle which allows to execute its algorithms both sequentially and in parallel.

\textbf{Tasks:}

\begin{enumerate}
	\item
	To systematize and analyze existing approaches to solve the aforementioned problem.
	\item
	Create a formal description of a new algorithm.
	\item
	Formally prove its computational complexity.
	\item
	Implement the algorithm and create.
	\item 
	Create a single algorithmic environment which allows to execute computational geometry algorithms based on divide and conquer principle sequentially and in parallel.
	\item
	Describe practical use cases of the developed software.
\end{enumerate}

\textbf{Object of research} is methods of convex hull computation, applting the divide and conquer strategy for designing computational geometry algorithms, programmatic tools for executing computations in parallel. To achieve the goals the following \textbf{methods of research} are used: collection the information, information analysis, formalizing of the collected data and method of proving the scientific hypothesis.

\textbf{The application scope} of the results described in this article includes designing of dentures and corsets, where it is necessary to solve a large set of computational geometry problems on large inputs.

\section{Convex hull algorithm}
\subsection{Previous work}

The notion of a convex hull is simple. For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$. 
The problem of building such a set has a long history. In practice to solve such problem, means to find a subset of $S$, which can a "skeleton" for the convex hull.

Despite its simplicity, the definition mentioned earlier does not allow to build on its basis an algorithm. To find a solution, it is needed to introduce more notions that will address the nature of the problem in a more detailed way and allow to solve it in a constructively.

It is differentiated between two types of points set in this case: a static and a dynamic one. In the first case all points are known in advance. The algorithms for solving that kind of problem are well researched and described in \cite{jarvis, graham, quickhull}. In the letter case an algorithm should be able to address the problem on a new points being added to the initial set and some others being removed from it after a certain period of time. Initially a set of points can either contain points or be empty.

The first known algorithm for solve such problem was introduces by Preparata in \cite{preparata}. Convex hull is maintained in a form of an AVL tree, that allows to perform operations of adding new points form it. The split and finding of tangents is performed in optimal time of $O(\log n)$. The major drawback of this method is that there is no mean to remote points from the set.

Soon after Overmars and van Leeuwen described a method of how a concatenable queue can be used to maintain the convex hull \cite{overmars}. This, as well as special data structure that is based on a balanced binary tree and maintain the information gathered during previous queries, allows to support fully dynamic sets of points and perform a add or remove query  $O(\log^2 n)$ in the worst case.

\subsection{Concatenable queue}

Concatenable queue is an Abstract Data Type (ADT), that supports following operations:

\begin{itemize}
	\item
	ADD\_ELEMENT();
	\item
	REMOVE\_ELEMENT();
	\item
	GET\_MINIMUM();
	\item
	CONTAINS();
	\item
	SPLIT();
	\item
	MERGE().
\end{itemize}

By default the elements in a concatenable queue are kept i a certain predefined order \cite{aho}.

Here the concatenable queue is implemented as a binary  $B+$ tree. Its elements are divided into non-leaf and leaf elements. The leaf elements contain all data kept in a tree. Every element has a pointer to its left and right child element. For the leaf elements those pointers point to the elements left and right neighbors or $null$ if the element is utmost in the tree. 
Additionally every element keep a pointer to the largest element in its left sub-tree, which  allows to perform binary search \cite{aho}.  An example of such tree is given on fig. 1. The height of earch element is kept for the balancing process during the split and merge operations. It is measured as a maximum amount of steps it is possible to do in order to reach a leaf element.

\begin{figure}[htbp]
	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{cq_example}}
	\caption{Example of a concatenable queue.}
	\label{cq_example}
\end{figure}

From now we will go into details on how this data structure is implemented. So on the list. 1 its formal definition is provided:

\begin{figure}[htbp]
	\begin{lstlisting}[caption={Structure of a concatenable queue vertex},captionpos=b]
	class Node:
	int data		
	int height

	Node left
	Node right
	Node leftSubtreeMax

	boolean isLeaf

	class ConcatenableQueue:
	Node root
	Node minNode
	Node maxNode
	\end{lstlisting}
\end{figure}

The contains operations uses binary search by the tree elements so its complexity is $O(\log n)$, where $n$ hereafter denotes the numbers of elements in the queue.

Algorithm of insertion an element in a queue looks like as follows. First, the position of a new element is searched. Then the connections between adjacent leaf elements are broken to insert a new element. Going back a new non-leaf element is created - parent for the new element and one of its neighbor. The algorithm is formally described on the list. 2.

\begin{figure}[htbp]
\begin{lstlisting}[caption={Queue element insertion algorithm},captionpos=b]
Node insert(Node node, int e):
Node result = nil
if e <= node.leftSubtreeMax.data: 
if node.isLeaf:
if e == node.data:
node.data = e
else:
Node createdLeaf = 
createLeafBetween(e, node.left, node)
result = 
Node(createdLeaf, createdLeaf, node)
else:
node.left = insert(node.left, e)
else:
if node.isLeaf: 
Node createdLeaf = 
createLeafBetween(e, node, node.right)
result = Node(node, node, createdLeaf)
else: 
// go left and update node.right pointer
node.right = insert(node.right, e)

if result == nil:
result = node

updateHeight(result)
return result
\end{lstlisting}
\end{figure}

The \textit{updateHeight} subroutine updates the value of an element height, the \textit{createLeafBetween} subroutine breaks the connection between adjacent elements and insertion of a new one.

The \textit{insert} operation. On the first step we find out if $leftSubtreeMax$ point to an element with greater value than the value to be inserted $e$. If so, then if current element is a leaf, a new element is created between the current element and its left neighbor. Otherwise the search proceeds on the left sub-tree of the current element. The case, when $leftSubtreeMax$ is smaller than the value $e$ is analogous. The procedure ends with updating the height on a newly created element. The element is returned as its result value.

Since on every step we perform a constant amount of work, the complexity of the procedure is $O(h)=O(\log n)$, where $h$ hereafter denotes the height of the tree.

The operation of removing an element from the queue is performed analogously.

The split operation is a bit more complex. As an input the corresponding procedure receives current element and value based on which the split is performed. As a result two independent queues are formed. The value, by which the split has been performed, belongs to the left sub-queue. The procedure is described formally on the list. 3.

\begin{lstlisting}[caption={Queue plit algorithm},captionpos=b]
split(Node node, int e, 
ConcatenableQueue leftQueue, 
ConcatenableQueue rightQueue): 
if node.isLeaf
leftQueue.root = node
leftQueue.maxNode = node

rightQueue.minNode = node.right	
cut(node)
else:
if e == node.leftSubtreeMax.data:
leftQueue.root = node.left
leftQueue.maxNode = node.leftSubtreeMax

rightQueue.root = node.right
rightQueue.minNode = node.leftSubtreeMax.right

cut(node.leftSubtreeMax)
else if e < node.leftSubtreeMax.data:
split(node.left, e, leftQueue, rightQueue)
rightQueue.root =
concatenateNodes(rightQueue.root, 
node.right, node.leftSubtreeMax)
else:
split(node.right, e, leftQueue, rightQueue)
leftQueue.root = 
concatenateNodes(node.left, 
leftQueue.root, node.leftSubtreeMax)
\end{lstlisting}

Here the $concatenateNodes$ procedure is used. It performs concatenation of two arbitrary elements and uses theirs heights to balance the resulting queue. Its implementation is described further in the work. The $cut$ procedure breaks connection between two adjacent leaf elements in a queue and therefore is trivial. On the first step in the $split$ operation we check, is the current element is a leaf. Is so, its connection are broken and the value of $maxNode$ is updated for the left queue as well as the value of $minNode$ for the right queue. If element is not a leaf, then the procedure continues of either left or right sub-tree. Here a special corner cases is considered, where $leftSubtreeMax$ contain the dividing value. Then the analogous action to the usual search are performed.

The algorithm of the $concatenateNodes$ procedure is described on the list. 4.

\begin{lstlisting}[caption={Merging two queues using heights},captionpos=b]
Node concatenateNodes(Node leftNode, 
Node rightNode, Node leftSubtreeMax) {
if leftNode == nil:
return rightNode
else if rightNode == nil: 
return leftNode
else if leftNode.height == rightNode.height:
Node result = Node(leftSubtreeMax, 
leftNode, rightNode)
updateHeight(result)
return result
else if leftNode.height < rightNode.height:
rightNode.left = concatenateNodes(leftNode, 
rightNode.left, leftSubtreeMax)
updateHeight(rightNode)
return rightNode
else
leftNode.right = 
concatenateNodes(leftNode.right, 
rightNode, leftSubtreeMax)
updateHeight(leftNode)
return leftNode
\end{lstlisting}

First, we consider corner cases where one of the elements is $null$. This is required to ensure correctness of the recursion. Then, if the left element is higher than the right, one step down is taken for the left element. If the right element is higher - we take a step down for it. If the heights are equal, the joining point is found and a new element must be created. At each step, it is necessary to update the height of current element as it changes.

We begin by analyzing the complexity of the $split$ procedure by determining the complexity of the $concatenateNodes$ procedure. At each iteration, the step is performed either to the left son of the current element or to the right. The execution of the recursive procedure is finished by merging two elements. Since each step moves us down one level and a constant amount of work is performed for each level, the total complexity of the $concatenateNodes$ procedure is $O(h)=O(\log n)$.

The $split$ procedure uses the $concatenateNodes$ function as a subroutine. The complexity a $split$ call is equal to the complexity of $concatenateNodes$. The number of recursive calls $split$ for one split is $\log n$, so the total complexity of the procedure $\log^2 n$.

The merge operation of two queues is reduced to the clamping of their root vertices by the $concatenateNodes$ procedure, so its complexity is $O(\log n)$.

\subsection{Precomputation}

In the pre-processing stage, the "inner" points, which lie on a horizontal or vertical line, are removed from the set. Formally, the removal criterion is formulated as follows. For $a = (x_a, y_a)$ we denote $x(a)=x_a$, $y(a)=y_a$. Let points $a_1, a_2, ..., a_k$ lie on one horizontal line and $x(a_1) < x(a_2) <... <x (a_k) $. Then, by the criterion, the points $a_2, a_3, ..., a_{k-1}$ must be removed. Similarly for the vertical case.

Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last (if the repetition is more than two). The description of the algorithm is given in Listing 5.

\begin{lstlisting}[caption={Algorithm of removing duplicates in a sorted array},captionpos=b]
removeDuplicated(int[] points) {
int n = points.length

if n == 0:
return

it1 = 1
it2 = 0

while it2 < n:
if it2 + 1 > 0 && it2 + 1 < n - 1:
int previous = points[it2-1]
int current = points[it2]
int next = points[it2+1]

if previous != current || current != next:
points[it1] = current
if it1 < n-1:
++it1
else if it2 + 1 == 0:
if it1 < n-1:
++it1
++it2
else:
points[it1] = points[it2]

if it1 < n-1:
while it1 + 1 != points.length:
delete points[n - 1]
\end{lstlisting}

The idea behind the algorithm is to use two pointers to delete repetitions by overwriting their place with other non-repeating element. In this way, additional memory usage can be reduced to a constant value. The algorithm makes one pass through the array. At each step, a constant amount of work is performed to decide whether to delete the current item. Given this, the complexity of the above algorithm is $O(n)$.

To perform the above pre-processing, it is needed to:

\begin{enumerate}
	\item
	Sort points by $y$ (if $y$ coordinates are equal, the $x$ coordinates are compared).
	\item
	Delete repetitions by $y$ coordinate using the described algorithm.
	\item
	Sort points by $x$ (if $x$ coordinates are equal, the $y$ coordinates are compared).
	\item
	Delete repetitions by $x$ coordinate using the described algorithm.
\end{enumerate}

\subsection{The divide and conquer principle}

At the stage of splitting the initial problem, the current set of points is divided into left and right parts of equal size. Since a list is used to store the points, this operations can be completed by $O(1)$ using the formula

\begin{equation}
M_{i,j}=\frac{i+j}{2}
\end{equation}

The recursion stops when there are no more than $3$ points in the set.

For the base case, the set of points can have $2$ or $3$ elements. In the first case, as shown in fig. 2, the highest of two points forms the upper part of the hull, and the lower - the lower part.

\begin{figure}[htbp]
	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{base_case_2}}
	\caption{Base case for 2 points}
	\label{base_case_2}
\end{figure}

To consider the base case of $3$ points, we introduce an additional notion of the tangent slope given by two points on the plane. For arbitrary points $a_1, a_2$ such that $x(a_1)<x(a_2)$ slope is denoted as $\lambda$:

\begin{equation}
\lambda(a_1, a_2)=\frac{y(a_2)-y(a_1)}{x(a_2)-x(a_1)}
\end{equation}

According to this definition, the possible cases for points $a_1,a_2,a_3$ are given in table. 1 and shown in fig. 3:

\begin{table}[htbp]
	\caption{Position of 3-points base case}
	\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{$\lambda(a_1, a_2) > \lambda(a_2, a_3)$} & \textbf{$y(a_1) < y(a_2)$} & upper sub-hull & lower sub-hull \\
			\hline
			false & false & $a_1, a_3$ & $a_2$ \\
			\hline
			false & true & $a_1, a_3$ & $a_2$ \\
			\hline
			true & false & $a_2, a_3$ & $a_1$ \\
			\hline
			true & true & $a_1, a_2$ & $a_3$ \\
			\hline
		\end{tabular} 
	\end{center}
\end{table}

\begin{figure}[htbp]
	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{base_case_3}}
	\caption{Base cases for a set of 3 points}
	\label{base_case_3}
\end{figure}

\subsection{The merge step}

\cite{overmars} provides an algorithm for merging two convex hulls. The essence of the algorithm is to maintain the hull with the help of two concatenated queues. The hull is divided into two parts. In this article, the separation occurs from top to bottom. Then, using the two-pointer technique and the cases described in \cite{overmars}, the proper tangent line is searched. It remains to split the two queues at the 2 found vertices that form the tangent and to merge the remaining parts. An example of performing such a procedure is shown in fig. 4.

\begin{figure}[htbp]
	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{ch_union}}
	\caption{Merging step of two hulls}
	\label{ch_union}
\end{figure}

It remains to consider the corner cases that arise when performing the merging. The first of these cases is related to the ambiguity of the position of the utmost points in the described representation of the convex hull. The leftmost point of the left hull and the rightmost point of the right hull must belong to the upper parts of the view before finding the tangent line, because otherwise such tangent may be found incorrectly. An example of such incorrect search is given in fig. 5.

\begin{figure}[htbp]
	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_search}}
	\caption{Example of an incorrect position of the utmost left in the left sub-hull}
	\label{incorect_search}
\end{figure}

To avoid such a situation, it is necessary to move the indicated points of their upper parts before merging the sub-hulls.

For the rightmost point of the left hull and the leftmost point of the right hull we have the following cases. Similarly to the previous argument, they must be transferred to the upper parts of the hulls. And after merging these points must be transferred to the lower parts of the hull, if they do not belong to the created upper part of the final hull. Otherwise, the formed hull may be incorrect. An example of such case is shown in fig. 6.

\begin{figure}[htbp]
	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_edge_points}}
	\caption{Example of a convex hull for a wrong position of the utmost left points of the left sub-hull}
	\label{incorect_edge_points}
\end{figure}

After combining the parts of the convex hulls, another corner case might take place. The search for the tangent for the upper parts of the hulls does not take into account the position of the lower parts and vice versa. As a result, the upper and lower parts of the final hull may not form a coherent structure. An example of such a situation is shown in Fig. 7.

\begin{figure}[htbp]
	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_lower_subhull}}
	\caption{An example of a non-integral hull after merging along the reference lines}
	\label{incorect_lower_subhull}
\end{figure}

To avoid such a situation, it is necessary to perform the step of cutting off the redundant parts of the formed lower sub-hull. Then searching for the left and right pivoting vertices in the concatenable queue is performed. After that, the queue is splits over the found vertices.

The cases corresponding to the left search are shown in fig. 8, and those corresponding to the right - in fig. 9. Fig. 10 shows correctly constructed convex hull.

\begin{figure}[htbp]
	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{correct_convex_hull}}
	\caption{Correctly constructed convex hull}
	\label{correct_convex_hull}
\end{figure}

\subsection{Algorithm complexity}

\begin{theorem}
	The complexity of the described convex hull construction algorithm for a static set of points is $O(n\log n)$ with sequential execution.
\end{theorem}

\begin{proof}
	We will argue the complexity of the algorithm by listing the complexities of the main stages it consists of.

	\begin{itemize}
		\item
		Precomputation $O(n\log n)$.
		\item
		Recursive descent and splitting the set into 2 parts $O(1)$.
		\item
		Recursive ascent and merging parts of the convex hull $O(\log n)$.
		\begin{itemize}
			\item
			Transfer of the utmost points to upper parts of convex hulls $O(\log n)$.
			\item
			Finding the tangent for the upper parts of the hulls $O(\log n)$.
			\item
			Splitting and merging the upper parts $O(\log^2 n)$.
			\item
			Moving the utmost points to the bottom of the hulls $O(\log n)$.
			\item
			Finding the tangent for the upper parts of the hulls $O(\log n)$.
			\item
			Splitting and merging the upper parts $O(\log^2 n)$.
			\item
			Merging the lower parts of the hull $O(\log n)$.
			\item
			Normalization of the obtained lower part $O(\log n)$.
		\end{itemize}
	\end{itemize}

	The complexity of pre-processing directly depends on the complexity of the sort algorithm . Using fast sorting algorithms \cite[page~159]{cormen}, this procedure can be performed in the optimal time of $O(n\log n)$.

	To estimate the complexity of the recursive procedure for constructing a convex hull, we make the following equation:

	\begin{equation*}
	T(n) = 2T(\frac{n}{2}) + O(\log^2 n)
	\end{equation*}

	According to the well-known result from the theory of algorithmic complexity we have that the solution of this equation is:

	\begin{equation*}
	T(n)=O(n)
	\end{equation*}

	Thus, taking into account the pre-processing, we get the total complexity of the algorithm $O(n\log n)$
\end{proof}

\begin{theorem}
	The complexity of the recursive convex hull construction is $O(\log^3n)$ when executed concurrently on $\frac{n}{2}$ processors.
\end{theorem}

\begin{proof}
	The recursion tree has a height of no more than $\log n$ levels. At the lowest level, the number of subtasks created is $\frac{n}{2}$. Thus, each subtask takes not more than $\frac{n}{2}$ time.

	Next, $O(\log^2 n)$ work is performed at each level. Having the height of the recursion tree, we get the total complexity of the algorithm

	\begin{equation*}
	T(n) = O(\log^3 n)
	\end{equation*}
\end{proof}

\section{Single algorithmic environment}

\subsection{Divide and conquer algorithm interface}

The next goal of this work is to build a single algorithmic environment. The construction of such an object requires the combination of an algorithmic database together with the necessary data structures. It will allow to incorporate all implemented algorithms together, without necessity to know their internal implementation. In fact, it is necessary to create an interface of generic algorithm based on divide and conquer strategy, which will then be used on a specific set of input data.

We start creating the generic interface by listing its components:

\begin{itemize}
	\item 
	Precomputation.
	\item 
	Splitting task into sub-tasks.
	\item 
	Solving sub-tasks.
	\item 
	Merging obtained results.
	\item 
	Checking, if a given input data is a base case for the algorithm.
	\item 
	Solving the base case.
\end{itemize}

Each of these components will represent a function of the future interface. Here there is a clear separation between the input type for the algorithm and the type of result it returns. These two types should be parameters of the algorithm model to be built. One should also pay attention to the types of functions input and output types of the interface.

A large number of computational geometry algorithms, such as computing minimal spanning tree, the Delaunay triangulation, the Voronoi diagram and the convex hull accept the list of points. However, it is not possible limit the type of input to the algorithm interface in a single algorithmic environment. The reason for this is that some algorithms can use the results of other algorithms as input data. A well known example is the construction of a Delaunay triangulation given the Voronoi diagram represented in a special data structure \cite[pp.~209]{shamos}.

Listing 6 shows the constructed algorithm model:

\begin{lstlisting}[caption={Algorithm model based on the divide and conquer principle},captionpos=b]
interface DaCAlgorithm[IT, OT]:
boolean isBaseCase(IT input)
int inputSize(IT input)
OT solveBaseCase(IT input)
OT merge(OT first, OT second)
Pair[IT, IT] divide(IT input)
IT precompute(IT input)
\end{lstlisting}

\subsection{Sequential and parallel execution}

Although this model very accurately describes the class of algorithms, it does not make it possible to solve the problem directly by having input data, which in fact enables to the algorithm from how it will be executed. In this part of the article, principles of sequential and parallel execution are considered.

When executing sequentially an algorithm, its individual subtasks computed one by one. Such algorithm is shown in Listing 7:

\begin{lstlisting}[caption={Sequential execution algorithm},captionpos=b]
OT solveRecursively(IT input,
 DaCAlgorithm[IT, OT] algorithm):
if algorithm.isBaseCase(input):
return algorithm.solveBaseCase(input)

Pair[IT, IT] p = algorithm.divide(input)
IT left = p[0]
IT right = p[1]

OT leftResult = solveRecursively(left)
OT rightResult = solveRecursively(right)

return algorithm.merge(leftResult, rightResult)
\end{lstlisting}

In parallel execution, it is necessary to take into account that the individual subtasks can be calculated independently, which significantly speeds up the execution of the algorithm.

To construct the concurrent algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$, which runs the functions $function1$ and $function2$ in parallel.

Listing 8 contains the main steps of this implementation.

\begin{lstlisting}[caption={Parallel execution algorithm},captionpos=b]
OT compute(IT input, 
DaCAlgorithm[IT, OT] algorithm):
if algorithm.isBaseCase(input):
return algorithm.solveBaseCase(input)

Pair[IT, IT] p = algorithm.divide(input)
IT left = p[0]
IT right = p[1]

OT leftResult,rightResult = 
computeInParallel(solveRecursively(left),
solveRecursively(right))

return algorithm.merge(leftResult, rightResult)
\end{lstlisting}

From the standpoint of the practical implementation the performance of such algorithm was improved bt introducing a limit on the size of subtasks that can be calculated in parallel.

\subsection{Performance comparison}

A number of algorithm performance measurements were performed for different input sizes and the average number of recursive tasks per thread. The results are shown in Table. 2 and 3.

\begin{table}[htbp]
	\caption{Sequential execution performance}
	\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Number of points} & 1000000 & 10000000 & 10000000 \\
			\hline
			&52.207 (ms)&648.621 (ms)&1302.485 (ms)\\
			\hline
		\end{tabular} 
	\end{center}
\end{table}

\begin{table}[htbp]
	\caption{Parallel execution performance}
	\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{NosptNop} & 1000000 & 10000000 & 10000000 \\
			\hline
			20 &52.434 (ms)&458.921 (ms)&969.243 (ms)\\

			\hline
			30 &53.615 (ms)&472.127 (ms)&845.707 (ms)\\

			\hline
			40 &52.797 (ms)&464.418 (ms)&907.498 (ms)\\

			\hline
			50 &53.189 (ms)&474.804 (ms)&905.952 (ms)\\	
			\hline
		\end{tabular} 
	\end{center}
\end{table}

\section*{Conclusion}

As a result of the work, existing methods for constructing a convex hull were analyzed and a new algorithm was proposed to solve this problem for a static set of points. A unified algorithmic environment was also created on the basis of divide and conquer algorithms, which allows to develop efficient implementation of such algorithms quickly and enables to execute them both sequentially and in parallel. The described object was implemented in Java software using standard library tools. Additionally, a tool was developed to visualize the results of the convex hull construction.

The implemented of data structures and other elements are does not use other libraries. This makes it independent and easy to use.

The main advantages of the developed algorithm are the optimization of the preprocessing stage and the effective application of such data structures as the concatenable queue, which allows to spend minimum time for the merging step of the convex hulls construction. In the preprocessing stage constant memory usage is achieved.

The performance comparison of the developed algorithm for both types of execution allows to conclude that it has high degree of parallelism. The speedup was $31\%$ percent in the best case. It is worth noting that the use of parallel execution is only necessary for very large input data.

The architecture of the created algorithmic environment makes it easy to expand its capabilities: add new as well as modify existing algorithms, implement the necessary data and extend the programmatic representation of the algorithm based on the divide and conquer scheme. This flexibility of the software product is achieved by using the modular principle in its design. In the future, it is necessary to investigate the possibility of performing parallel preprocessing. The basis for this research is given in \cite{parallel_merge_sort}.

The results of this work can be incorporated in the development of modern high-precision 3D models. The concept of a single algorithmic environment has proven to be highly relevant and effective for constructing a software for solving complex problems of computational geometry. This, along with the ease of extending the product created, makes research in this area extremely relevant.

\begin{thebibliography}{00}
	\bibitem{jarvis} Jarvis, R. A. (1973). ``On the identification of the convex hull of a finite set of points in the plane'' Information Processing Letters. 2: 18–21. DOI=10.1016/0020-0190(73)90020-3

	\bibitem{graham} 
	Graham, R.L. (1972). 
	``An Efficient Algorithm for Determining the Convex Hull of a Finite Planar Set'' Information Processing Letters. 1 (4): 132–133. DOI=10.1016/0020-0190(72)90045-2

	\bibitem{quickhull} 
	Barber, C. Bradford; Dobkin, David P.; Huhdanpaa, Hannu (1 December 1996).
	``The quickhull algorithm for convex hulls''
	ACM Transactions on Mathematical Software. 22 (4): 469–483. DOI:10.1145/235815.235821

	\bibitem{preparata} 
	F. P. Preparata and S. J. Hong. 1977. 
	``Convex hulls of finite sets of points in two and three dimensions''
	Commun. ACM 20, 2 (February 1977), 87-93. DOI=10.1145/359423.359430

	\bibitem{overmars}
	Overmars, Mark H. and Jan van Leeuwen.  
	``Maintenance of Configurations in the Plane''
	J. Comput. Syst. Sci. 23 (1981): 166-204.

	\bibitem{aho}
	Alfred V. Aho 
	``The Design and Analysis of Computer Algorithms'' (1st ed.). / John E. Hopcroft., John E. Ulman. -
	Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA 1974. ISBN 0201000296

	\bibitem{cormen}
	``Introduction to Algorithms'' / (3rd ed.).
	[Cormen, Thomas H., Leiserson, Charles E., Rivest, Ronald L., Stein, Clifford] (2009) - MIT Press and McGraw-Hill.\\ ISBN 0-262-03384-4.

	\bibitem{parallel_merge_sort} Richard Cole. 1988.  
	``Parallel merge sort'' SIAM J. Comput. 17, 4 (August 1988), 770-785. DOI=10.1137/0217049

	\bibitem{shamos}
	Franco P. Preparata and  Michael I. Shamos. ``Computational Geometry: an Introduction'' - Springer-Verlag, Berlin, Heidelberg 1985.
	ISBN 0-387-96131-3

	\bibitem{tarjan}
	Cheriton, David R. and Robert E. Tarjan.
	``Finding Minimum Spanning Trees''
	SIAM J. Comput. 5 (1976): 724-742.	
\end{thebibliography}
\end{document}

### 2019-11-13 article/article.tex
renamed .tex file: "conference-text" -> "article"

--- 2019-11-13 article/conference-text.tex
@@
 \begin{abstract}
-The paper is devoted to the development of efficient algorithmic tools for solving a set of interrelated problems of computational geometry.
-To do this, we propose to create a single algorithmic environment with unified data structures that will allow you to generate simple and fast procedures for solving problems as a whole.
-We build the generator on the basis of the strategy "divide and conquer".
-We can consider and other computational models that have integral properties for solving problems.
-For example, we can use a Voronoi Diagram or a Delaunay Triangulation.
-Because a convex hull is key to a set of computational geometry tasks, we offer unified data structures to support it and other geometric objects based on a binary tree and, in particular, a weighted concatenable queue.
-This allows you to perform procedures for a set of tasks within no more than
-$O(\log n)$ time. In this case, a consistent and parallel implementation is possible.
+The paper is devoted to the development of an efficient algorithmic tools for solving a set of interrelated computational geometry problems.
+To do this, a single algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources.
+We build the environment on the basis of the ``divide and conquer'' strategy.
+Once a convex hull is key to a set of computational geometry problems, we offer a special weighted concatenable queue data structure to maintain it.
+The data structure is implemented in a form of a binary tree.
+\textcolor{red}{This allows to perform procedures for a set of tasks within no more than $O(\log n)$ time.} Furthermore we offer a way to execute the algorithms both sequentially and in parallel.
+In the future the algorithmic environment can be improved to support other \textcolor{blue}{computational models} with similar \textcolor{red}{integral properties} for solving problems.
+As an example, the Voronoi Diagram or the Delaunay Triangulation can be considered.
 \end{abstract}

### 2019-11-14 article/article.tex
rewritten introduction

@@
 The data structure is implemented in a form of a binary tree.
-\textcolor{red}{This allows to perform procedures for a set of tasks within no more than $O(\log n)$ time.} Furthermore we offer a way to execute the algorithms both sequentially and in parallel.
-In the future the algorithmic environment can be improved to support other \textcolor{blue}{computational models} with similar \textcolor{red}{integral properties} for solving problems.
+This allows to perform operations needed in algorithm for a set of tasks within no more than $O(\log n)$ time.
+Furthermore we offer a way to execute the algorithms both sequentially and in parallel.
+In the future the algorithmic environment can be improved to support other \textcolor{blue}{computational models} with similar properties for solving problems.
 As an example, the Voronoi Diagram or the Delaunay Triangulation can be considered.
@@
 \section{Introduction}
-\textbf{The current situation in the field of research.} The convex hull problem arises not only in many practical applications, but also is an core tool for solving many others computational geometry problems.
 
-There are implicit relations between such problems.
-Currently, the state of the art approach for solving such sets of problems is the single algorithmic environment, which takes advantage of those implicit relations to create a final software product.
-An example to such approach may be the usage of a generic data structures for solving different problems.
-Thus, the algorithmic environment allows to reduce complex problems to some basic computations.
+The notion of a convex hull is simple.
+For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$.
+The problem of building such a set has a long history.
+In practice to solve such problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
 
-This article introduces a new approach for solving the convex hull problem on a static set of points.
-Here the divide and conquer strategy is used as a base for the algorithm and the actual convex hull is maintained with a concatenable queue during the computations.
-The resulting algorithm has the worst case complexity of $O(n\log n)$, whereas the subroutine of merging 2 convex hull has a complexity of $O(log n)$, where $n$ is the number of points.
-
-Henceforth a notion of a single algorithmic environment is introduced that formalizes the divide and conquer algorithm from a programmatic standpoint.
-The formalization allows to create a level of abstraction upon an actual implementation of an algorithm and therefore perform computations sequentially and in parallel on a more generic level.
-
-\textbf{Relevance} consist in a large specter of application problems that computational geometry allows to solve with its methodology.
-Implementation of those algorithms enables in an single algorithmic environment allows to use them in the development of modern technology and apply them on large datasets.
-
-\textbf{The goals of this article} is to design an optimal algorithms for solving the convex hull problem on a static set of points and to create a single algorithmic environment on the divide and conquer principle which allows to execute its algorithms both sequentially and in parallel.
-
-\textbf{Tasks:}
-
-\begin{enumerate}
-	\item
-	To systematize and analyze existing approaches to solve the aforementioned problem.
-	\item
-	Create a formal description of a new algorithm.
-	\item
-	Formally prove its computational complexity.
-	\item
-	Implement the algorithm and create.
-	\item 
-	Create a single algorithmic environment which allows to execute computational geometry algorithms based on divide and conquer principle sequentially and in parallel.
-	\item
-	Describe practical use cases of the developed software.
-\end{enumerate}
-
-\textbf{Object of research} is methods of convex hull computation, applting the divide and conquer strategy for designing computational geometry algorithms, programmatic tools for executing computations in parallel.
-To achieve the goals the following \textbf{methods of research} are used: collection the information, information analysis, formalizing of the collected data and method of proving the scientific hypothesis.
-
-\textbf{The application scope} of the results described in this article includes designing of dentures and corsets, where it is necessary to solve a large set of computational geometry problems on large inputs.
-
-\section{Convex hull algorithm}
-\subsection{Previous work}
-
-The notion of a convex hull is simple. For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$. 
-The problem of building such a set has a long history. In practice to solve such problem, means to find a subset of $S$, which can a "skeleton" for the convex hull.
-
-Despite its simplicity, the definition mentioned earlier does not allow to build on its basis an algorithm.
-To find a solution, it is needed to introduce more notions that will address the nature of the problem in a more detailed way and allow to solve it in a constructively.
-
-It is differentiated between two types of points set in this case: a static and a dynamic one.
+It is differentiated between two types of point sets in this case: a static and a dynamic one.
 In the first case all points are known in advance.
 The algorithms for solving that kind of problem are well researched and described in \cite{jarvis, graham, quickhull}.
-In the letter case an algorithm should be able to address the problem on a new points being added to the initial set and some others being removed from it after a certain period of time.
-Initially a set of points can either contain points or be empty.
+In the letter case an algorithm should be able to handle new points which are being added to the initial set and some  being removed from it in real time.
+\textcolor{teal}{Initially a set of points can either contain points or be empty.}
 
@@
 Soon after Overmars and van Leeuwen described a method of how a concatenable queue can be used to maintain the convex hull \cite{overmars}.
-This, as well as special data structure that is based on a balanced binary tree and maintain the information gathered during previous queries, allows to support fully dynamic sets of points and perform a add or remove query  $O(\log^2 n)$ in the worst case.
+This, as well as special data structure that is based on a balanced binary tree and maintains the information gathered during previous queries, allows to support fully dynamic sets of points and perform add or remove query  $O(\log^2 n)$ in the worst case.
+
+% new algorithm
+This article introduces a new approach for solving the convex hull problem on a static set of points.
+Here the ``divide-and-conquer'' strategy is used and the actual convex hull is maintained in a form of a concatenable queue during the computations.
+The resulting algorithm has the worst case complexity of $O(n\log n)$, whereas the subroutine of merging 2 convex hull has a complexity of $O(log n)$, where $n$ denotes the number of points.
+
+% unified algorithmic environment
+\textcolor{teal}{The convex hull problem arises not only in many practical applications, but also is an core method for solving many others computational geometry problems.
+There are implicit relations between such problems.} Currently, the state of the art approach for solving such sets of problems is the single algorithmic environment, which takes advantage of those implicit relations to implement efficient solving methods.
+An example to such approach may be the usage of a generalized data structures that can be used in different algorithms.
+\textcolor{teal}{Thus, the algorithmic environment allows to reduce complex problems to some basic computations.}
+
+In the algorithmic environment the ``divide-and-conquer'' algorithm is formalizes from a programmatic standpoint.
+The formalization allows to create a level of abstraction upon an actual implementation of an algorithm and therefore perform computations sequentially and in parallel.
+
+\section{Convex hull algorithm}
+\subsection{Previous work}
 

### 2019-11-16 article/article.tex
updated introduction

@@
 
-\title{Unified data structures to optimize solving a complex of interrelated geometric problems\\
+\title{Unified data structures to optimize solving a complex of interrelated geometric problems*\\
 %{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used}
@@
 
+% relevance
+Nowadays, computational capabilities make it possible to state and to solve more sophisticated problems for which complex mathematical models must be created.
+This is particularly the case for generic parameterized problems, which parameters may depend on the domain-specific features and can vary over time.
+As such, the modeling of thermodynamical, biological and chemical processes can be exemplified.
+
+In practice, the ability to observe the aforementioned processes in real time is particularly valuable.
+In order to construct an exact visual model of those processes, one need to simultaneously solve a set of geometrical problems.
+A good approach in this case is to design and implement efficient algorithms with further possibility to parallelize them.
+There are two options of how to apply this method.
+
+% design withought single algorithmic environemnt 
+The first option is to design algorithms to solve the problems independently, so that no results obtained during one algorithm are used in the others.
+The are many efficient parallel algorithms, which are base on this approach.
+The corresponding results are discussed in [1], where the ''divide-and-conquer``scheme is used to construct the convex hull for two- and three-dimensional space and the Voronoi diagram for two-dimensional space in $O(log N)$ time for the \textcolor{red}{CREW and EREW} computational models.
+Furthermore, a rather detailed analysis of other efficient algorithms for the segment intersection and polygon triangulation problems is present.
+
+% design using single algorithmic environemnt
+However, sometimes the use of independent algorithms does not provide the desirable efficiency.
+Therefore, the second option is to implement the algorithms while getting benefit of theirs similarities, such as common data structures.
+A further step might be taken to separate stages of algorithms and reuse computation results to achieve better performance.
+Considering the fact that the majority of computational geometry problems use ''divide and conquer`` principle and therefore can be parallelized, it is a good point from where to start the construction of a unified algorithmic environment.
+
+% previous work in the convex hull domain
+The first known algorithm for solve the convex hull problem was introduces by Preparata in \cite{preparata}.
+Convex hull is maintained in a form of an AVL tree, that allows to perform operations of adding new points form it.
+The split and finding of tangents is performed in optimal time of $O(\log n)$.
+The major drawback of this method is that there is no mean to remote points from the set.
+Soon after Overmars and van Leeuwen described a method of how a concatenable queue can be used to maintain the convex hull \cite{overmars}.
+This, as well as special data structure that is based on a balanced binary tree and maintains the information gathered during previous queries, allows to support fully dynamic sets of points and perform add or remove query  $O(\log^2 n)$ in the worst case.
+
+% scope of this article
+In this article we solve \textcolor{red}{a collection of computational geometry problems} with a \textcolor{red}{generalized parallel-recursive} algorithm based on ``divide-and-conquer'' principle in $O(NlogN)$ time.
+We first describe how the algorithm can be applied to compute the convex hull.
+From there we consider several other problems where results gained from constructing the convex hull might be used.
+The partitioning stage of the initial points set is identical for all problems and the results of individual subproblems are maintained in the same data structure, namely, the concatenable queue.
+This yields good performance in comparison the approach, where intermediate results are recomputed every time.
+
+\section{Convex hull algorithm}
+\subsection{Problem statement}
+
 The notion of a convex hull is simple.
@@
 \textcolor{teal}{Initially a set of points can either contain points or be empty.}
-
-The first known algorithm for solve such problem was introduces by Preparata in \cite{preparata}.
-Convex hull is maintained in a form of an AVL tree, that allows to perform operations of adding new points form it.
-The split and finding of tangents is performed in optimal time of $O(\log n)$.
-The major drawback of this method is that there is no mean to remote points from the set.
-
-Soon after Overmars and van Leeuwen described a method of how a concatenable queue can be used to maintain the convex hull \cite{overmars}.
-This, as well as special data structure that is based on a balanced binary tree and maintains the information gathered during previous queries, allows to support fully dynamic sets of points and perform add or remove query  $O(\log^2 n)$ in the worst case.
-
-% new algorithm
-This article introduces a new approach for solving the convex hull problem on a static set of points.
-Here the ``divide-and-conquer'' strategy is used and the actual convex hull is maintained in a form of a concatenable queue during the computations.
-The resulting algorithm has the worst case complexity of $O(n\log n)$, whereas the subroutine of merging 2 convex hull has a complexity of $O(log n)$, where $n$ denotes the number of points.
-
-% unified algorithmic environment
-\textcolor{teal}{The convex hull problem arises not only in many practical applications, but also is an core method for solving many others computational geometry problems.
-There are implicit relations between such problems.} Currently, the state of the art approach for solving such sets of problems is the single algorithmic environment, which takes advantage of those implicit relations to implement efficient solving methods.
-An example to such approach may be the usage of a generalized data structures that can be used in different algorithms.
-\textcolor{teal}{Thus, the algorithmic environment allows to reduce complex problems to some basic computations.}
-
-In the algorithmic environment the ``divide-and-conquer'' algorithm is formalizes from a programmatic standpoint.
-The formalization allows to create a level of abstraction upon an actual implementation of an algorithm and therefore perform computations sequentially and in parallel.
-
-\section{Convex hull algorithm}
-\subsection{Previous work}
 

### 2019-11-17 article/article.tex
updated introduction 2

@@
 % previous work in the convex hull domain
-The first known algorithm for solve the convex hull problem was introduces by Preparata in \cite{preparata}.
+For the convex hull problem it is differentiated between two types of point sets: a static and a dynamic one.
+In the first case all points are known in advance.
+The algorithms for solving that kind of problem are well researched and described in \cite{jarvis, graham, quickhull}.
+In the letter case an algorithm should be able to handle new points which are being added to the initial set and some  being removed from it in real time.
+The first known algorithm for solving such problem was introduces by Preparata in \cite{preparata}.
 Convex hull is maintained in a form of an AVL tree, that allows to perform operations of adding new points form it.
@@
 The partitioning stage of the initial points set is identical for all problems and the results of individual subproblems are maintained in the same data structure, namely, the concatenable queue.
-This yields good performance in comparison the approach, where intermediate results are recomputed every time.
+This yields good performance comparing to the case, where intermediate results are recomputed every time.
 
@@
 For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$.
-The problem of building such a set has a long history.
 In practice to solve such problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
-
-It is differentiated between two types of point sets in this case: a static and a dynamic one.
-In the first case all points are known in advance.
-The algorithms for solving that kind of problem are well researched and described in \cite{jarvis, graham, quickhull}.
-In the letter case an algorithm should be able to handle new points which are being added to the initial set and some  being removed from it in real time.
-\textcolor{teal}{Initially a set of points can either contain points or be empty.}
 

### 2019-11-17 article/article.tex
updated introduction 3 (by VT)

--- 2019-11-14 article/article.tex
@@
 
+Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of \textcolor{red}{science and technology objectives}.
+The core of this set are problems of computational geometry and computer graphics.
+To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time.
+Existing methods (iLastic[1], IMARIS [2], ImageJ (або FiJi) [3]), that are based on set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy.
+It is worse noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems [4-14].
+Every such algorithm requires its own computational resources and is executed independently from others.
+In such case some identical steps, such as precomputation and building data structures, are performed several times.
+
+Therefore, a important objective in developing of the algorithmic models is to create a universal tool, which would have means to efficiently solve a problems in the set.
+This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of the common data structures.
+In [15] the notion of a single algorithmic environment is introduced, which is based on the ``divide-and-conquer'' principle and takes into account the aforementioned features of the algorithms.
+In particular, the precomputation and splitting the initial set of data to form the recursion tree is common for all the problems is as s result is executed only once.
+During the merge stage the intermediate results are maintained in the weighted concatenable queue.
+This model does not repeat computations and the intermediate results are highly reused during the algorithms, which yields good performance.
+
+\textcolor{blue}{This article provides detailed explanation on how the common data structures from [15] are implemented on the example of a convex hull algorithm.}
+
+\section{Convex hull algorithm}
+\subsection{Problem statement}
+
 The notion of a convex hull is simple.
 For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$.
-The problem of building such a set has a long history.
 In practice to solve such problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
-
-It is differentiated between two types of point sets in this case: a static and a dynamic one.
-In the first case all points are known in advance.
-The algorithms for solving that kind of problem are well researched and described in \cite{jarvis, graham, quickhull}.
-In the letter case an algorithm should be able to handle new points which are being added to the initial set and some  being removed from it in real time.
-\textcolor{teal}{Initially a set of points can either contain points or be empty.}
-
-The first known algorithm for solve such problem was introduces by Preparata in \cite{preparata}.
-Convex hull is maintained in a form of an AVL tree, that allows to perform operations of adding new points form it.
-The split and finding of tangents is performed in optimal time of $O(\log n)$.
-The major drawback of this method is that there is no mean to remote points from the set.
-
-Soon after Overmars and van Leeuwen described a method of how a concatenable queue can be used to maintain the convex hull \cite{overmars}.
-This, as well as special data structure that is based on a balanced binary tree and maintains the information gathered during previous queries, allows to support fully dynamic sets of points and perform add or remove query  $O(\log^2 n)$ in the worst case.
-
-% new algorithm
-This article introduces a new approach for solving the convex hull problem on a static set of points.
-Here the ``divide-and-conquer'' strategy is used and the actual convex hull is maintained in a form of a concatenable queue during the computations.
-The resulting algorithm has the worst case complexity of $O(n\log n)$, whereas the subroutine of merging 2 convex hull has a complexity of $O(log n)$, where $n$ denotes the number of points.
-
-% unified algorithmic environment
-\textcolor{teal}{The convex hull problem arises not only in many practical applications, but also is an core method for solving many others computational geometry problems.
-There are implicit relations between such problems.} Currently, the state of the art approach for solving such sets of problems is the single algorithmic environment, which takes advantage of those implicit relations to implement efficient solving methods.
-An example to such approach may be the usage of a generalized data structures that can be used in different algorithms.
-\textcolor{teal}{Thus, the algorithmic environment allows to reduce complex problems to some basic computations.}
-
-In the algorithmic environment the ``divide-and-conquer'' algorithm is formalizes from a programmatic standpoint.
-The formalization allows to create a level of abstraction upon an actual implementation of an algorithm and therefore perform computations sequentially and in parallel.
-
-\section{Convex hull algorithm}
-\subsection{Previous work}
 

### 2019-11-20 article/article.tex
text restructuring

@@
 \begin{abstract}
-The paper is devoted to the development of an efficient algorithmic tools for solving a set of interrelated computational geometry problems.
-To do this, a single algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources.
+		The paper is devoted to the development and implementation of an efficient algorithmic model for solving a set of interrelated computational geometry problems.
+To do this, a unified algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources.
 We build the environment on the basis of the ``divide and conquer'' strategy.
-Once a convex hull is key to a set of computational geometry problems, we offer a special weighted concatenable queue data structure to maintain it.
+		Once a convex hull is key to a set of computational geometry problems, we offer a concatenable queue data structure to maintain it.
 The data structure is implemented in a form of a binary tree.
@@
 Furthermore we offer a way to execute the algorithms both sequentially and in parallel.
-In the future the algorithmic environment can be improved to support other \textcolor{blue}{computational models} with similar properties for solving problems.
+		In the future the algorithmic environment can be improved to support other computational models with similar properties for solving problems.
 As an example, the Voronoi Diagram or the Delaunay Triangulation can be considered.
@@
 \begin{IEEEkeywords}
-Algorithmic tools,   Computational geometry, Interrelated problems set, Single algorithmic environment, A weighted concatenable queue
+Algorithmic tools,   Computational geometry, Interrelated problems set, Unified algorithmic environment, Concatenable queue
 \end{IEEEkeywords}
@@
 
-Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of \textcolor{red}{science and technology objectives}.
+		Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of computational problems.
 The core of this set are problems of computational geometry and computer graphics.
 To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time.
-Existing methods (iLastic[1], IMARIS [2], ImageJ (або FiJi) [3]), that are based on set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy.
-It is worse noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems [4-14].
+Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy.
+It is worth noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems \cite{aggarwal,atallah,cole,amato,chen,berkman,goodman,akl,jaja,leeuwen,reif}.
 Every such algorithm requires its own computational resources and is executed independently from others.
-In such case some identical steps, such as precomputation and building data structures, are performed several times.
+In such case some identical steps, such as preprocessing and building data structures, are performed several times.
 
@@
 This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of the common data structures.
-In [15] the notion of a single algorithmic environment is introduced, which is based on the ``divide-and-conquer'' principle and takes into account the aforementioned features of the algorithms.
-In particular, the precomputation and splitting the initial set of data to form the recursion tree is common for all the problems is as s result is executed only once.
-During the merge stage the intermediate results are maintained in the weighted concatenable queue.
+In \cite{tereshchenko} the notion of a unified algorithmic environment is introduced, which is based on the ``divide-and-conquer'' principle and takes into account the aforementioned features of the algorithms.
+In particular, the preprocessing and splitting the initial set of data to form the recursion tree is common for all problems and is executed only once.
+During the merge stage intermediate results are maintained in a weighted concatenable queue.
 This model does not repeat computations and the intermediate results are highly reused during the algorithms, which yields good performance.
 
-\textcolor{blue}{This article provides detailed explanation on how the common data structures from [15] are implemented on the example of a convex hull algorithm.}
+		This article provides detailed explanation on how the concatenable queue used in \cite{tereshchenko} is implemented.
+It is then used to design an algorithm for the convex hull problem on a static set of points.
+Finally we provide implementation details and performance analysis for the designed algorithm.
 
-\section{Convex hull algorithm}
-\subsection{Problem statement}
+\section{Unified algorithmic environment}
+\subsection{Algorithms stages}
+
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+% ----------------------------------------------- PROBLEM STATEMENT --------------------------------------------------------
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+
+		In this section we describe the principle of how we decompose each algorithm into distinct parts.
+This partition is then used to avoid repeating the computations in the algorithmic environment.
+The principle will be show on a convex hull algorithm which is similar to the one describe in \cite{overmars} but operates on a static set of points.
 
@@
 
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+% ----------------------------------------------- PREPROCESSING ------------------------------------------------------------
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+
+		In the preprocessing stage, the "inner" points, which lie on a horizontal or vertical line, are removed from the set.
+Formally, the removal criterion is formulated as follows.
+For $a = (x_a, y_a)$ we denote $x(a)=x_a$, $y(a)=y_a$.
+Let points $a_1, a_2, ..., a_k$ lie on one horizontal line and $x(a_1) < x(a_2) <...
+<x (a_k) $.
+Then, by the criterion, the points $a_2, a_3, ..., a_{k-1}$ must be removed.
+Similarly for the vertical case.
+
+		Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last (if the repetition is more than two).
+The idea behind the algorithm is to use two pointers to delete repetitions by overwriting their place with other non-repeating element.
+In this way, additional memory usage can be reduced to a constant value.
+The algorithm makes one pass through the array.
+At each step, a constant amount of work is performed to decide whether to delete the current item.
+Given this, the complexity of the above algorithm is $O(n)$.
+
+		To perform the preprocessing described above, it is needed to:
+
+		\begin{enumerate}
+			\item
+			Sort points by $y$ (if $y$ coordinates are equal, the $x$ coordinates are compared).
+			\item
+			Delete repetitions by $y$ coordinate using the described algorithm.
+			\item
+			Sort points by $x$ (if $x$ coordinates are equal, the $y$ coordinates are compared).
+			\item
+			Delete repetitions by $x$ coordinate using the described algorithm.
+		\end{enumerate}
+
+		In the result we get a set of points for which we can apply the recursive convex hull algorithm.
+
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+% ----------------------------------------------- SPLIT ------------------------------------------------------------
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+
+		At the stage of splitting the initial problem, the current set of points is divided into left and right parts of equal size.
+Since a list is used to store the points, this operations can be completed in $O(1)$ using the formula below:
+
+		\begin{equation}
+			M_{i,j}=\frac{i+j}{2}
+		\end{equation}
+		The recursion stops when there are no more than $3$ points in the set.
+
+		For the base case, the set of points can have $2$ or $3$ elements. In the first case the highest of two points forms the upper part of the hull, and the lower - the lower part.
+		To consider the base case of $3$ points, we introduce an additional notion of the tangent slope given by two points on the plane.
+For arbitrary points $a_1, a_2$ such that $x(a_1)<x(a_2)$ slope is denoted as $\lambda$:
+
+		\begin{equation}
+			\lambda(a_1, a_2)=\frac{y(a_2)-y(a_1)}{x(a_2)-x(a_1)}
+		\end{equation}
+		According to this definition, the possible cases for points $a_1,a_2,a_3$ are given in Table \ref{table:3points}:
+
+		\begin{table}[htbp]
+			\caption{3-points base cases}
+			\label{table:3points}
+			\begin{center}
+				\begin{tabular}{|c|c|c|c|}
+					\hline
+					\textbf{$\lambda(a_1, a_2) > \lambda(a_2, a_3)$} & \textbf{$y(a_1) < y(a_2)$} & upper part & lower part\\
+					\hline
+					false & false & $a_1, a_3$ & $a_2$ \\
+					\hline
+					false & true & $a_1, a_3$ & $a_2$ \\
+					\hline
+					true & false & $a_2, a_3$ & $a_1$ \\
+					\hline
+					true & true & $a_1, a_2$ & $a_3$ \\
+					\hline
+				\end{tabular} 
+			\end{center}
+		\end{table}
+
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+% --------------------------------   THE MERGE STEP ------------------------------------------------------------------------
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+
+		\cite{overmars} provides an algorithm for merging two convex hulls.
+The essence of the algorithm is to maintain the hull with the help of two concatenated queues.
+The hull is divided into two parts.
+In this article, the separation occurs from top to bottom.
+Then, using the two-pointer technique and the cases described in \cite{overmars}, the proper tangent line is searched.
+It remains to split the two queues at the 2 found vertices that form the tangent and to merge the remaining parts.
+An example of performing such a procedure is shown in Fig.
+\ref{fig:ch_union}.
+
+		\begin{figure}[htbp]
+			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{ch_union}}
+			\caption{Merging step of two hulls}
+			\label{fig:ch_union}
+		\end{figure}
+
+		It remains to consider the corner cases that arise when performing the merging.
+The first of these cases is related to the ambiguity of the position of the utmost points in the described representation of the convex hull.
+The leftmost point of the left hull and the rightmost point of the right hull must belong to the upper parts of the view before finding the tangent line, because otherwise such tangent may be found incorrectly.
+An example of such incorrect search is given in Fig.
+\ref{fig:incorect_search}.
+
+		\begin{figure}[htbp]
+			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_search}}
+			\caption{Example of an incorrect position of the utmost left in the left sub-hull}
+			\label{fig:incorect_search}
+		\end{figure}
+
+		To avoid such a situation, it is necessary to move the indicated points from their upper parts before merging the sub-hulls.
+For the rightmost point of the left hull and the leftmost point of the right hull we have the following cases.
+Similarly to the previous argument, they must be transferred to the upper parts of the hulls.
+And after merging these points must be transferred to the lower parts of the hull, if they do not belong to the created upper part of the final hull.
+Otherwise, the formed hull may be incorrect.
+An example of such case is shown in Fig.
+\ref{fig:incorect_edge_points}.
+
+		\begin{figure}[htbp]
+			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_edge_points}}
+			\caption{Example of a convex hull for a wrong position of the utmost left points of the left sub-hull}
+			\label{fig:incorect_edge_points}
+		\end{figure}
+
+		After combining the parts of the convex hulls, another corner case might take place.
+The search for the tangent for the upper parts of the hulls does not take into account the position of the lower parts and vice versa.
+As a result, the upper and lower parts of the final hull may not form a coherent structure.
+An example of such a situation is shown in Fig.
+\ref{fig:incorect_lower_subhull}.
+
+		\begin{figure}[htbp]
+			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_lower_subhull}}
+			\caption{An example of a non-integral hull after merging along the reference lines}
+			\label{fig:incorect_lower_subhull}
+		\end{figure}
+
+		To avoid such a situation, it is necessary to perform the step of cutting off the redundant parts of the formed lower sub-hull.
+Then searching for the left and right pivoting vertices in the concatenable queue is performed.
+After that, the queue is splits over the found vertices.
+		Fig. \ref{fig:correct_convex_hull} shows correct convex hull.
+
+		\begin{figure}[htbp]
+			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{correct_convex_hull}}
+			\caption{Correctly constructed convex hull}
+			\label{fig:correct_convex_hull}
+		\end{figure}
+
+\subsection{``Divide-and-conquer'' algorithm interface}
+
+		The next goal of this work is to build a unified algorithmic environment.
+The construction of such an object requires the combination of an algorithmic database together with the necessary data structures.
+In fact, it is necessary to create an interface of generic algorithm based on ``divide-and-conquer'' strategy, which will then be used on a specific set of input data.
+
+		We start creating the generic interface by listing its components:
+
+		\begin{itemize}
+			\item 
+			Preprocessing.
+			\item 
+			Splitting task into sub-tasks.
+			\item 
+			Solving sub-tasks.
+			\item 
+			Merging obtained results.
+			\item 
+			Checking, if a given input data is a base case for the algorithm.
+			\item 
+			Solving the base case.
+		\end{itemize}
+
+		Each of these components will represent a function in the future interface.
+Here there is a clear separation between the input type for the algorithm and the type of result it returns.
+These two types should be parameters of the algorithm model.
+One should also pay attention to the input and output types of functions  in the interface.
+
+		A large number of computational geometry algorithms, such as computing minimal spanning tree, the Delaunay triangulation, the Voronoi diagram and the convex hull accept the list of points.
+However, would be wrong limit the input type in the algorithm interface to a list of points.
+The reason for this is that some algorithms can use the results of other algorithms as input data.
+A well known example is the construction of a Delaunay triangulation based on the Voronoi diagram maintained in a special data structure.
+
+		Listing \ref{lst:algmodel} shows the constructed algorithm model. $IT$ denotes the input type and $OT$ - output type.
+
+		\begin{lstlisting}[caption={Algorithm model based on the ``divide-and-conquer'' principle},label={lst:algmodel},captionpos=b]
+interface DaCAlgorithm[IT, OT]:
+
+  boolean isBaseCase(IT input)
+  int inputSize(IT input)
+  OT solveBaseCase(IT input)
+  OT merge(OT first, OT second)
+  Pair[IT, IT] divide(IT input)
+  IT preprocess(IT input)
+		\end{lstlisting}
+
+\subsection{Sequential and parallel execution}
+
+		Although this model very accurately describes the class of algorithms, it does not make it possible to solve the problem directly by having input data, which in fact enables to the algorithm from how it will be executed.
+Here the principles of sequential and parallel execution are explained.
+
+		When executing sequentially an algorithm, its individual sub-tasks computed one by one.
+We first check if current input is a base case and if so we can directly compute it by calling $solveBaseCase$ procedure.
+Otherwise input is split with $divide$ and separate sub-problem are solved sequentially.
+Finally obtained results are merged with $merge$ procedure.
+
+		In parallel execution, it is necessary to take into account that the individual sub-problems can be calculated independently, which significantly speeds up the execution of the algorithm.
+
+		To construct the concurrent algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$.
+which runs the functions $function1$ and $function2$ in simultaneously.
+We use it solve sub-problem obtained after the splitting the given input.
+Other than that parallel version is identical to the sequential one.
+
+		From the standpoint of the practical implementation the performance of such algorithm was improved by introducing a limit on the size of sub-tasks that can be calculated in parallel.
+This allowed to put a threshold on the amount of work for one thread.
+
+\section{Implementation details}
 \subsection{Concatenable queue}
 
-Concatenable queue is an Abstract Data Type (ADT), that supports following operations:
+		Concatenable queue is an Abstract Data Type, that supports following operations:
 
@@
 
-Here the concatenable queue is implemented as a binary  $B+$ tree.
-Its elements are divided into non-leaf and leaf elements.
-The leaf elements contain all data kept in a tree.
-Every element has a pointer to its left and right child element.
-For the leaf elements those pointers point to the elements left and right neighbors or $null$ if the element is utmost in the tree.
-Additionally every element keep a pointer to the largest element in its left sub-tree, which  allows to perform binary search \cite{aho}.
+		In this article the concatenable queue is implemented as a binary  $B+$ tree.
+Its vertices are divided into non-leaf and leaf vertices.
+The leaf vertices contain all data kept in a tree.
+Every vertex has a pointer to its left and right child.
+For the leaf vertices those pointers point to the left and right neighbors or $null$ if the vertex is utmost in the tree.
+		Additionally every vertex keeps a pointer to a vertex with the largest element in its left sub-tree, which  allows to perform binary search \cite{aho}.
 An example of such tree is given on fig.
 1.
-The height of earch element is kept for the balancing process during the split and merge operations.
-It is measured as a maximum amount of steps it is possible to do in order to reach a leaf element.
+The height of each vertex is kept for the balancing during the split and merge operations.
+It is measured as a maximum amount of steps it is possible to do in order to reach a leaf vertex.
+
+		From now we will go into details on how this data structure is implemented.
+
+		The contains operations is pretty straightforward and uses binary search over the tree vertices so its complexity is $O(\log n)$, where $n$ hereafter denotes the numbers of vertices in the queue.
+
+		Algorithm of inserting an element in a queue looks like as follows.
+First, the position of a new vertex is searched.
+Then the connections between adjacent leaf vertices are broken to insert a new one.
+Going back a new non-leaf vertices a new vertex is created - parent for the new element and one of its neighbor.
+The algorithm is formally described on the Listing \ref{lst:insert-alg}.
 
 		\begin{figure}[htbp]
-	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{cq_example}}
-	\caption{Example of a concatenable queue.}
-	\label{cq_example}
-\end{figure}
-
-From now we will go into details on how this data structure is implemented. So on the list. 1 its formal definition is provided:
-
-\begin{figure}[htbp]
-	\begin{lstlisting}[caption={Structure of a concatenable queue vertex},captionpos=b]
-	class Node:
-	int data		
-	int height
-
-	Node left
-	Node right
-	Node leftSubtreeMax
-
-	boolean isLeaf
-
-	class ConcatenableQueue:
-	Node root
-	Node minNode
-	Node maxNode
-	\end{lstlisting}
-\end{figure}
-
-The contains operations uses binary search by the tree elements so its complexity is $O(\log n)$, where $n$ hereafter denotes the numbers of elements in the queue.
-
-Algorithm of insertion an element in a queue looks like as follows.
-First, the position of a new element is searched.
-Then the connections between adjacent leaf elements are broken to insert a new element.
-Going back a new non-leaf element is created - parent for the new element and one of its neighbor.
-The algorithm is formally described on the list.
-2.
-
-\begin{figure}[htbp]
-\begin{lstlisting}[caption={Queue element insertion algorithm},captionpos=b]
+			\begin{lstlisting}[caption={Queue element insertion algorithm},label={lst:insert-alg},captionpos=b]
 Node insert(Node node, int e):
@@
   createLeafBetween(e, node.left, node)
-result = 
-Node(createdLeaf, createdLeaf, node)
+  result = Node(createdLeaf, createdLeaf, node)
   else:
@@
 
-The \textit{updateHeight} subroutine updates the value of an element height, the \textit{createLeafBetween} subroutine breaks the connection between adjacent elements and insertion of a new one.
+		Here the \textit{updateHeight} subroutine updates the value of an element height, the \textit{createLeafBetween} subroutine breaks the connection between adjacent elements and insertion of a new one.
 
@@
 The value, by which the split has been performed, belongs to the left sub-queue.
-The procedure is described formally on the list.
-3.
+The procedure is described formally on the Listing \ref{lst:split-alg}.
 
-\begin{lstlisting}[caption={Queue plit algorithm},captionpos=b]
+		\begin{lstlisting}[caption={Queue plit algorithm},label={lst:split-alg},captionpos=b]
 split(Node node, int e, 
@@
   leftQueue.maxNode = node	
-
   rightQueue.minNode = node.right	
@@
   rightQueue.root = node.right
-rightQueue.minNode = node.leftSubtreeMax.right
+  rightQueue.minNode = 
+  node.leftSubtreeMax.right
 
@@
 
-The algorithm of the $concatenateNodes$ procedure is described on the list. 4.
+		The algorithm of the $concatenateNodes$ procedure is described on the Listing \ref{lst:concatenate-als}.
 
-\begin{lstlisting}[caption={Merging two queues using heights},captionpos=b]
+		\begin{lstlisting}[caption={Merging two queues using heights},label={lst:concatenate-als},captionpos=b]
 Node concatenateNodes(Node leftNode, 
@@
 
-\subsection{Precomputation}
-
-In the pre-processing stage, the "inner" points, which lie on a horizontal or vertical line, are removed from the set.
-Formally, the removal criterion is formulated as follows.
-For $a = (x_a, y_a)$ we denote $x(a)=x_a$, $y(a)=y_a$.
-Let points $a_1, a_2, ..., a_k$ lie on one horizontal line and $x(a_1) < x(a_2) <...
-<x (a_k) $.
-Then, by the criterion, the points $a_2, a_3, ..., a_{k-1}$ must be removed.
-Similarly for the vertical case.
-
-Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last (if the repetition is more than two).
-The description of the algorithm is given in Listing 5.
-
-\begin{lstlisting}[caption={Algorithm of removing duplicates in a sorted array},captionpos=b]
-removeDuplicated(int[] points) {
-int n = points.length
-
-if n == 0:
-return
-
-it1 = 1
-it2 = 0
-
-while it2 < n:
-if it2 + 1 > 0 && it2 + 1 < n - 1:
-int previous = points[it2-1]
-int current = points[it2]
-int next = points[it2+1]
-
-if previous != current || current != next:
-points[it1] = current
-if it1 < n-1:
-++it1
-else if it2 + 1 == 0:
-if it1 < n-1:
-++it1
-++it2
-else:
-points[it1] = points[it2]
-
-if it1 < n-1:
-while it1 + 1 != points.length:
-delete points[n - 1]
-\end{lstlisting}
-
-The idea behind the algorithm is to use two pointers to delete repetitions by overwriting their place with other non-repeating element.
-In this way, additional memory usage can be reduced to a constant value.
-The algorithm makes one pass through the array.
-At each step, a constant amount of work is performed to decide whether to delete the current item.
-Given this, the complexity of the above algorithm is $O(n)$.
-
-To perform the above pre-processing, it is needed to:
-
-\begin{enumerate}
-	\item
-	Sort points by $y$ (if $y$ coordinates are equal, the $x$ coordinates are compared).
-	\item
-	Delete repetitions by $y$ coordinate using the described algorithm.
-	\item
-	Sort points by $x$ (if $x$ coordinates are equal, the $y$ coordinates are compared).
-	\item
-	Delete repetitions by $x$ coordinate using the described algorithm.
-\end{enumerate}
-
-\subsection{The divide and conquer principle}
-
-At the stage of splitting the initial problem, the current set of points is divided into left and right parts of equal size.
-Since a list is used to store the points, this operations can be completed by $O(1)$ using the formula
-
-\begin{equation}
-M_{i,j}=\frac{i+j}{2}
-\end{equation}
-
-The recursion stops when there are no more than $3$ points in the set.
-
-For the base case, the set of points can have $2$ or $3$ elements. In the first case, as shown in fig. 2, the highest of two points forms the upper part of the hull, and the lower - the lower part.
-
-\begin{figure}[htbp]
-	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{base_case_2}}
-	\caption{Base case for 2 points}
-	\label{base_case_2}
-\end{figure}
-
-To consider the base case of $3$ points, we introduce an additional notion of the tangent slope given by two points on the plane.
-For arbitrary points $a_1, a_2$ such that $x(a_1)<x(a_2)$ slope is denoted as $\lambda$:
-
-\begin{equation}
-\lambda(a_1, a_2)=\frac{y(a_2)-y(a_1)}{x(a_2)-x(a_1)}
-\end{equation}
-
-According to this definition, the possible cases for points $a_1,a_2,a_3$ are given in table. 1 and shown in fig. 3:
-
-\begin{table}[htbp]
-	\caption{Position of 3-points base case}
-	\begin{center}
-		\begin{tabular}{|c|c|c|c|}
-			\hline
-			\textbf{$\lambda(a_1, a_2) > \lambda(a_2, a_3)$} & \textbf{$y(a_1) < y(a_2)$} & upper sub-hull & lower sub-hull \\
-			\hline
-			false & false & $a_1, a_3$ & $a_2$ \\
-			\hline
-			false & true & $a_1, a_3$ & $a_2$ \\
-			\hline
-			true & false & $a_2, a_3$ & $a_1$ \\
-			\hline
-			true & true & $a_1, a_2$ & $a_3$ \\
-			\hline
-		\end{tabular} 
-	\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{base_case_3}}
-	\caption{Base cases for a set of 3 points}
-	\label{base_case_3}
-\end{figure}
-
-\subsection{The merge step}
-
-\cite{overmars} provides an algorithm for merging two convex hulls.
-The essence of the algorithm is to maintain the hull with the help of two concatenated queues.
-The hull is divided into two parts.
-In this article, the separation occurs from top to bottom.
-Then, using the two-pointer technique and the cases described in \cite{overmars}, the proper tangent line is searched.
-It remains to split the two queues at the 2 found vertices that form the tangent and to merge the remaining parts.
-An example of performing such a procedure is shown in fig.
-4.
-
-\begin{figure}[htbp]
-	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{ch_union}}
-	\caption{Merging step of two hulls}
-	\label{ch_union}
-\end{figure}
-
-It remains to consider the corner cases that arise when performing the merging.
-The first of these cases is related to the ambiguity of the position of the utmost points in the described representation of the convex hull.
-The leftmost point of the left hull and the rightmost point of the right hull must belong to the upper parts of the view before finding the tangent line, because otherwise such tangent may be found incorrectly.
-An example of such incorrect search is given in fig.
-5.
-
-\begin{figure}[htbp]
-	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_search}}
-	\caption{Example of an incorrect position of the utmost left in the left sub-hull}
-	\label{incorect_search}
-\end{figure}
-
-To avoid such a situation, it is necessary to move the indicated points of their upper parts before merging the sub-hulls.
-
-For the rightmost point of the left hull and the leftmost point of the right hull we have the following cases.
-Similarly to the previous argument, they must be transferred to the upper parts of the hulls.
-And after merging these points must be transferred to the lower parts of the hull, if they do not belong to the created upper part of the final hull.
-Otherwise, the formed hull may be incorrect.
-An example of such case is shown in fig.
-6.
-
-\begin{figure}[htbp]
-	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_edge_points}}
-	\caption{Example of a convex hull for a wrong position of the utmost left points of the left sub-hull}
-	\label{incorect_edge_points}
-\end{figure}
-
-After combining the parts of the convex hulls, another corner case might take place.
-The search for the tangent for the upper parts of the hulls does not take into account the position of the lower parts and vice versa.
-As a result, the upper and lower parts of the final hull may not form a coherent structure.
-An example of such a situation is shown in Fig.
-7.
-
-\begin{figure}[htbp]
-	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_lower_subhull}}
-	\caption{An example of a non-integral hull after merging along the reference lines}
-	\label{incorect_lower_subhull}
-\end{figure}
-
-To avoid such a situation, it is necessary to perform the step of cutting off the redundant parts of the formed lower sub-hull.
-Then searching for the left and right pivoting vertices in the concatenable queue is performed.
-After that, the queue is splits over the found vertices.
-
-The cases corresponding to the left search are shown in fig. 8, and those corresponding to the right - in fig. 9. Fig. 10 shows correctly constructed convex hull.
-
-\begin{figure}[htbp]
-	\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{correct_convex_hull}}
-	\caption{Correctly constructed convex hull}
-	\label{correct_convex_hull}
-\end{figure}
-
-\subsection{Algorithm complexity}
+\section{Algorithm analysis and performance evaluation}
+\subsection{Complexity}
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+% ----------------------------------------------- COMPLEXITY ---------------------------------------------------------------------
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
 
@@
 				\item
-		Precomputation $O(n\log n)$.
+				Preprocessing $O(n\log n)$.
 				\item
@@
 
-	The complexity of pre-processing directly depends on the complexity of the sort algorithm .
-Using fast sorting algorithms \cite[page~159]{cormen}, this procedure can be performed in the optimal time of $O(n\log n)$.
+			Using known algorithms we can perform sorting in $O(n\log n)$. To estimate the complexity of the recursive procedure for constructing a convex hull, we make the following equation:
 
-	To estimate the complexity of the recursive procedure for constructing a convex hull, we make the following equation:
+			\begin{equation}
+			  T(n) = 2T(\frac{n}{2}) + O(\log^2 n)
+			\end{equation}
 
-	\begin{equation*}
-	T(n) = 2T(\frac{n}{2}) + O(\log^2 n)
-	\end{equation*}
+			According to result from the theory of algorithmic complexity we have that the solution of this equation is:
 
-	According to the well-known result from the theory of algorithmic complexity we have that the solution of this equation is:
+			\begin{equation}
+			  T(n)=O(n)
+			\end{equation}
 
-	\begin{equation*}
-	T(n)=O(n)
-	\end{equation*}
-
-	Thus, taking into account the pre-processing, we get the total complexity of the algorithm $O(n\log n)$
+			Thus, taking into account the preprocessing, we get the total complexity of the algorithm $O(n\log n)$.
 		\end{proof}
@@
 		\begin{proof}
-	The recursion tree has a height of no more than $\log n$ levels. At the lowest level, the number of subtasks created is $\frac{n}{2}$. Thus, each subtask takes not more than $\frac{n}{2}$ time.
+			The recursion tree has a height of no more than $\log n$ levels. At the lowest level, the number of sub-tasks created is $\frac{n}{2}$. Thus, each sub-task takes no more than $\frac{n}{2}$ time.
 
-	Next, $O(\log^2 n)$ work is performed at each level. Having the height of the recursion tree, we get the total complexity of the algorithm
-
-	\begin{equation*}
-	T(n) = O(\log^3 n)
-	\end{equation*}
+			Next, $O(\log^2 n)$ work is performed at each level. Having the height of the recursion tree, we get the total final complexity of the algorithm.
 		\end{proof}
 
-\section{Single algorithmic environment}
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+% ----------------------------------------------- PERFORMANCE ---------------------------------------------------------------------
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
 
-\subsection{Divide and conquer algorithm interface}
+\subsection{Performance}
+		A number of algorithm performance measurements were performed for different input sizes and the average number of recursive tasks per thread. The results are shown on the Fig. \ref{fig:performance}.
 
-The next goal of this work is to build a single algorithmic environment.
-The construction of such an object requires the combination of an algorithmic database together with the necessary data structures.
-It will allow to incorporate all implemented algorithms together, without necessity to know their internal implementation.
-In fact, it is necessary to create an interface of generic algorithm based on divide and conquer strategy, which will then be used on a specific set of input data.
-
-We start creating the generic interface by listing its components:
-
-\begin{itemize}
-	\item 
-	Precomputation.
-	\item 
-	Splitting task into sub-tasks.
-	\item 
-	Solving sub-tasks.
-	\item 
-	Merging obtained results.
-	\item 
-	Checking, if a given input data is a base case for the algorithm.
-	\item 
-	Solving the base case.
-\end{itemize}
-
-Each of these components will represent a function of the future interface.
-Here there is a clear separation between the input type for the algorithm and the type of result it returns.
-These two types should be parameters of the algorithm model to be built.
-One should also pay attention to the types of functions input and output types of the interface.
-
-A large number of computational geometry algorithms, such as computing minimal spanning tree, the Delaunay triangulation, the Voronoi diagram and the convex hull accept the list of points.
-However, it is not possible limit the type of input to the algorithm interface in a single algorithmic environment.
-The reason for this is that some algorithms can use the results of other algorithms as input data.
-A well known example is the construction of a Delaunay triangulation given the Voronoi diagram represented in a special data structure \cite[pp.~209]{shamos}.
-
-Listing 6 shows the constructed algorithm model:
-
-\begin{lstlisting}[caption={Algorithm model based on the divide and conquer principle},captionpos=b]
-interface DaCAlgorithm[IT, OT]:
-boolean isBaseCase(IT input)
-int inputSize(IT input)
-OT solveBaseCase(IT input)
-OT merge(OT first, OT second)
-Pair[IT, IT] divide(IT input)
-IT precompute(IT input)
-\end{lstlisting}
-
-\subsection{Sequential and parallel execution}
-
-Although this model very accurately describes the class of algorithms, it does not make it possible to solve the problem directly by having input data, which in fact enables to the algorithm from how it will be executed.
-In this part of the article, principles of sequential and parallel execution are considered.
-
-When executing sequentially an algorithm, its individual subtasks computed one by one. Such algorithm is shown in Listing 7:
-
-\begin{lstlisting}[caption={Sequential execution algorithm},captionpos=b]
-OT solveRecursively(IT input,
- DaCAlgorithm[IT, OT] algorithm):
-if algorithm.isBaseCase(input):
-return algorithm.solveBaseCase(input)
-
-Pair[IT, IT] p = algorithm.divide(input)
-IT left = p[0]
-IT right = p[1]
-
-OT leftResult = solveRecursively(left)
-OT rightResult = solveRecursively(right)
-
-return algorithm.merge(leftResult, rightResult)
-\end{lstlisting}
-
-In parallel execution, it is necessary to take into account that the individual subtasks can be calculated independently, which significantly speeds up the execution of the algorithm.
-
-To construct the concurrent algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$, which runs the functions $function1$ and $function2$ in parallel.
-
-Listing 8 contains the main steps of this implementation.
-
-\begin{lstlisting}[caption={Parallel execution algorithm},captionpos=b]
-OT compute(IT input, 
-DaCAlgorithm[IT, OT] algorithm):
-if algorithm.isBaseCase(input):
-return algorithm.solveBaseCase(input)
-
-Pair[IT, IT] p = algorithm.divide(input)
-IT left = p[0]
-IT right = p[1]
-
-OT leftResult,rightResult = 
-computeInParallel(solveRecursively(left),
-solveRecursively(right))
-
-return algorithm.merge(leftResult, rightResult)
-\end{lstlisting}
-
-From the standpoint of the practical implementation the performance of such algorithm was improved bt introducing a limit on the size of subtasks that can be calculated in parallel.
-
-\subsection{Performance comparison}
-
-A number of algorithm performance measurements were performed for different input sizes and the average number of recursive tasks per thread. The results are shown in Table. 2 and 3.
-
-\begin{table}[htbp]
-	\caption{Sequential execution performance}
-	\begin{center}
-		\begin{tabular}{|c|c|c|c|}
-			\hline
-			\textbf{Number of points} & 1000000 & 10000000 & 10000000 \\
-			\hline
-			&52.207 (ms)&648.621 (ms)&1302.485 (ms)\\
-			\hline
-		\end{tabular} 
-	\end{center}
-\end{table}
-
-\begin{table}[htbp]
-	\caption{Parallel execution performance}
-	\begin{center}
-		\begin{tabular}{|c|c|c|c|}
-			\hline
-			\textbf{NosptNop} & 1000000 & 10000000 & 10000000 \\
-			\hline
-			20 &52.434 (ms)&458.921 (ms)&969.243 (ms)\\
-
-			\hline
-			30 &53.615 (ms)&472.127 (ms)&845.707 (ms)\\
-
-			\hline
-			40 &52.797 (ms)&464.418 (ms)&907.498 (ms)\\
-
-			\hline
-			50 &53.189 (ms)&474.804 (ms)&905.952 (ms)\\	
-			\hline
-		\end{tabular} 
-	\end{center}
-\end{table}
-
-\section*{Conclusion}
-
-As a result of the work, existing methods for constructing a convex hull were analyzed and a new algorithm was proposed to solve this problem for a static set of points.
-A unified algorithmic environment was also created on the basis of divide and conquer algorithms, which allows to develop efficient implementation of such algorithms quickly and enables to execute them both sequentially and in parallel.
-The described object was implemented in Java software using standard library tools.
-Additionally, a tool was developed to visualize the results of the convex hull construction.
-
-The implemented of data structures and other elements are does not use other libraries. This makes it independent and easy to use.
-
-The main advantages of the developed algorithm are the optimization of the preprocessing stage and the effective application of such data structures as the concatenable queue, which allows to spend minimum time for the merging step of the convex hulls construction.
-In the preprocessing stage constant memory usage is achieved.
-
-The performance comparison of the developed algorithm for both types of execution allows to conclude that it has high degree of parallelism.
-The speedup was $31\%$ percent in the best case.
-It is worth noting that the use of parallel execution is only necessary for very large input data.
-
-The architecture of the created algorithmic environment makes it easy to expand its capabilities: add new as well as modify existing algorithms, implement the necessary data and extend the programmatic representation of the algorithm based on the divide and conquer scheme.
-This flexibility of the software product is achieved by using the modular principle in its design.
-In the future, it is necessary to investigate the possibility of performing parallel preprocessing.
-The basis for this research is given in \cite{parallel_merge_sort}.
-
-The results of this work can be incorporated in the development of modern high-precision 3D models.
-The concept of a single algorithmic environment has proven to be highly relevant and effective for constructing a software for solving complex problems of computational geometry.
-This, along with the ease of extending the product created, makes research in this area extremely relevant.
+		\begin{figure}[htbp]
+			\centerline{\includegraphics[width=0.5\textwidth, height=0.3\textheight]{performance}}
+			\caption{Performance data}
+			\label{fig:performance}
+		\end{figure}
+\section{Conclusion}
 
 \begin{thebibliography}{00}
-	\bibitem{jarvis} Jarvis, R. A. (1973). ``On the identification of the convex hull of a finite set of points in the plane'' Information Processing Letters. 2: 18–21. DOI=10.1016/0020-0190(73)90020-3
+	\bibitem{ilastik} C.
+Sommer, C.
+Straehle, U.
+Köthe and F.
+A.
+Hamprecht, ``Ilastik: Interactive learning and segmentation toolkit,'' 2011 IEEE International Symposium on Biomedical Imaging: From Nano to Macro, Chicago, IL, 2011, pp.
+230-233.
+	doi: 10.1109/ISBI.2011.5872394
 
-	\bibitem{graham} 
-	Graham, R.L. (1972). 
-	``An Efficient Algorithm for Determining the Convex Hull of a Finite Planar Set'' Information Processing Letters. 1 (4): 132–133. DOI=10.1016/0020-0190(72)90045-2
+	\bibitem{imaris} IMARIS Software. Accessed on: 15.04.2019. [Online]. Available: https://imaris.oxinst.com
 
-	\bibitem{quickhull} 
-	Barber, C. Bradford; Dobkin, David P.; Huhdanpaa, Hannu (1 December 1996).
-	``The quickhull algorithm for convex hulls''
-	ACM Transactions on Mathematical Software. 22 (4): 469–483. DOI:10.1145/235815.235821
+	\bibitem{imagej} ImageJ: An open platform for scientific image analysis. Accessed on: 15.04.2019. [Online]. Available: https://imagej.net/Welcome
 
-	\bibitem{preparata} 
-	F. P. Preparata and S. J. Hong. 1977. 
-	``Convex hulls of finite sets of points in two and three dimensions''
-	Commun. ACM 20, 2 (February 1977), 87-93. DOI=10.1145/359423.359430
+	\bibitem{aggarwal} А. Aggarwal et al., ``Parallel computational geometry,'' Algorithmica 3, 1-4 (November 1988), pp. 293-327.
 
-	\bibitem{overmars}
-	Overmars, Mark H. and Jan van Leeuwen.  
-	``Maintenance of Configurations in the Plane''
-	J. Comput. Syst. Sci. 23 (1981): 166-204.
+	\bibitem{atallah} M.J. Atallah, R. Cole, M.T. Goodrich, ``Cascading divide-and-conquer: a technique for designing parallel algorithms,'' SIAM J. Comput. 18, 1989, pp. 499-532.
 
-	\bibitem{aho}
-	Alfred V. Aho 
-	``The Design and Analysis of Computer Algorithms'' (1st ed.). / John E. Hopcroft., John E. Ulman. -
-	Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA 1974. ISBN 0201000296
+	\bibitem{cole} R.
+Cole, M.T.
+Goodrich, ``Optimal parallel algorithms for polygon and point-set problems,'' In Proceedings of the fourth annual symposium on Computational geometry (SCG '88), ACM, New York, NY, USA, pp.
+201-210.
 
-	\bibitem{cormen}
-	``Introduction to Algorithms'' / (3rd ed.).
-	[Cormen, Thomas H., Leiserson, Charles E., Rivest, Ronald L., Stein, Clifford] (2009) - MIT Press and McGraw-Hill.\\ ISBN 0-262-03384-4.
+	\bibitem{amato} N.
+M.
+Amato, M.
+T.
+Goodrich and E.
+A.
+Ramos, ``Parallel algorithms for higher-dimensional convex hulls,'' Proceedings 35th Annual Symposium on Foundations of Computer Science, Santa Fe, NM, USA, 1994, pp.
+683-694.
 
-	\bibitem{parallel_merge_sort} Richard Cole. 1988.  
-	``Parallel merge sort'' SIAM J. Comput. 17, 4 (August 1988), 770-785. DOI=10.1137/0217049
+	\bibitem{chen} D. Z. Chen, ``Efficient geometric algorithms on the EREW PRAM,'' in IEEE Transactions on Parallel and Distributed Systems, vol. 6, no. 1, pp. 41-47, Jan. 1995.
+	doi: 10.1109/71.363412
 
-	\bibitem{shamos}
-	Franco P. Preparata and  Michael I. Shamos. ``Computational Geometry: an Introduction'' - Springer-Verlag, Berlin, Heidelberg 1985.
-	ISBN 0-387-96131-3
+	\bibitem{berkman} O. Berkman, B. Schieber, U. Vishkin, ``A fast parallel algorithm for finding the convex hull of a sorted point set,'' Internat. J. Comput. Geom. Appl. 6, 1996, pp. 231-242.
 
-	\bibitem{tarjan}
-	Cheriton, David R. and Robert E. Tarjan.
-	``Finding Minimum Spanning Trees''
-	SIAM J. Comput. 5 (1976): 724-742.	
+	\bibitem{goodman} J.E. Goodman and J. O'Rourke, editors,  Handbook of Discrete and Computational Geometry, CRC Press LLC, Boca Raton, FL, 2004.
+
+	\bibitem{akl} Selim G. Akl and Kelly A. Lyons, Parallel Computational Geometry. Englewood Cliffs: Prentice-Hall, 1993.
+
+	\bibitem{jaja} J. JaJa, An Introduction to Parallel Algorithms, Amsterdam: Addison-Wesley, 1992.
+
+	\bibitem{leeuwen} J. Van Leeuwen, Handbook of Theoretical Computer Science, Amsterdam: Elsevier/The MIT
+	Press, 1990.
+
+	\bibitem{reif} J.H. Reif, Synthesis of Parallel Algorithms, San Mateo: Morgan Kaufmann, 1993.
+
+	\bibitem{tereshchenko} V. N. Tereshchenko, A. V. Anisimov, Recursion and parallel algorithms in geometric modeling
+	problems, Journal: Cybernetics and Systems Analysis: Vol. 46, N 2 (2010), pp. 173-184.
 \end{thebibliography}

### 2019-11-20 article/article.tex
finished text

@@
 \usepackage[formats]{listings}
+\lstset{
+	language=Java,
+	basicstyle=\small,
+	breaklines,
+}
 \graphicspath{{images/}}
@@
 
-\title{Unified data structures to optimize solving a complex of interrelated geometric problems*\\
-%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used}
-%\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{Unified data structures for solving optimally a set of interrelated computational geometry problems*}
 \author{
@@
 \begin{abstract}
-		The paper is devoted to the development and implementation of an efficient algorithmic model for solving a set of interrelated computational geometry problems.
+		The paper is devoted to the development and  of an efficient algorithmic model for solving a set of interrelated computational geometry problems.
 To do this, a unified algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources.
@@
 The data structure is implemented in a form of a binary tree.
-This allows to perform operations needed in algorithm for a set of tasks within no more than $O(\log n)$ time.
+This allows to perform operations needed in algorithm for a set of problems in $O(\log n)$ time.
 Furthermore we offer a way to execute the algorithms both sequentially and in parallel.
 		In the future the algorithmic environment can be improved to support other computational models with similar properties for solving problems.
-As an example, the Voronoi Diagram or the Delaunay Triangulation can be considered.
+As an example, the Voronoi diagram or the Delaunay triangulation can be considered.
 \end{abstract}
@@
 
-		Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of computational problems.
+		Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of problems.
 The core of this set are problems of computational geometry and computer graphics.
 To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time.
-Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy.
-It is worth noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems \cite{aggarwal,atallah,cole,amato,chen,berkman,goodman,akl,jaja,leeuwen,reif}.
+Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy.
+It is worth noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems such as in \cite{aggarwal,atallah,cole,amato,chen,berkman,goodman,akl,jaja,leeuwen,reif}.
 Every such algorithm requires its own computational resources and is executed independently from others.
@@
 
-		Therefore, a important objective in developing of the algorithmic models is to create a universal tool, which would have means to efficiently solve a problems in the set.
-This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of the common data structures.
+		Therefore, an important objective in developing the algorithmic models is to create a universal tool, which would have means to efficiently solve a set of problems.
+This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of the unified data structures.
 In \cite{tereshchenko} the notion of a unified algorithmic environment is introduced, which is based on the ``divide-and-conquer'' principle and takes into account the aforementioned features of the algorithms.
@@
 
-		This article provides detailed explanation on how the concatenable queue used in \cite{tereshchenko} is implemented.
-It is then used to design an algorithm for the convex hull problem on a static set of points.
-Finally we provide implementation details and performance analysis for the designed algorithm.
+		In this article we first describe how the convex hull algorithm for a static set of points is decomposed into separate stages and incorporated into our unified algorithmic environment model (UAEM).
+Then we provide detailed explanation on how the concatenable queue which is used in the algorithm is implemented.
+Finally we make complexity analysis for the algorithm and evaluate its performance.
 
@@
 Then, by the criterion, the points $a_2, a_3, ..., a_{k-1}$ must be removed.
-Similarly for the vertical case.
+Analogously for the vertical case.
 
-		Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last (if the repetition is more than two).
-The idea behind the algorithm is to use two pointers to delete repetitions by overwriting their place with other non-repeating element.
-In this way, additional memory usage can be reduced to a constant value.
+		Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last one (if there are more than two repetitions).
+The idea behind the algorithm is to use two pointers technique to delete repetitions by overwriting their place with other non-repeating element.
+This way, additional memory usage can be reduced to a constant value.
 The algorithm makes one pass through the array.
@@
 
-		At the stage of splitting the initial problem, the current set of points is divided into left and right parts of equal size.
-Since a list is used to store the points, this operations can be completed in $O(1)$ using the formula below:
+		At the stage of splitting the initial problem, the set of points is divided into left and right parts of equal size.
+Since a array-like data structure is used to store the points, this operations can be completed in $O(1)$ using the formula below:
 
@@
 
-		For the base case, the set of points can have $2$ or $3$ elements. In the first case the highest of two points forms the upper part of the hull, and the lower - the lower part.
+		For the base case, the set of points can have $2$ or $3$ elements.
+In the first case the highest of two points forms the upper part of the hull, and the lower - the lower part.
 To consider the base case of $3$ points, we introduce an additional notion of the tangent slope given by two points on the plane.
@@
 
-		\cite{overmars} provides an algorithm for merging two convex hulls.
-The essence of the algorithm is to maintain the hull with the help of two concatenated queues.
+		In \cite{overmars} an algorithm for merging two convex hulls is described.
+The idea of this algorithm is to maintain the hull in two concatenated queues.
 The hull is divided into two parts.
-In this article, the separation occurs from top to bottom.
+In this article it is divided into the upper and the lower sub-hulls.
 Then, using the two-pointer technique and the cases described in \cite{overmars}, the proper tangent line is searched.
-It remains to split the two queues at the 2 found vertices that form the tangent and to merge the remaining parts.
+It remains to split the two queues at the found vertices that form the tangent and to merge the remaining parts.
 An example of performing such a procedure is shown in Fig.
@@
 		It remains to consider the corner cases that arise when performing the merging.
-The first of these cases is related to the ambiguity of the position of the utmost points in the described representation of the convex hull.
+The first of these cases is related to the ambiguity of the position of the utmost points in the described representation.
 The leftmost point of the left hull and the rightmost point of the right hull must belong to the upper parts of the view before finding the tangent line, because otherwise such tangent may be found incorrectly.
@@
 
-		To avoid such a situation, it is necessary to move the indicated points from their upper parts before merging the sub-hulls.
+		To avoid such a situation, it is necessary to move the indicated points to the upper sub-hulls before merging them.
 For the rightmost point of the left hull and the leftmost point of the right hull we have the following cases.
 Similarly to the previous argument, they must be transferred to the upper parts of the hulls.
-And after merging these points must be transferred to the lower parts of the hull, if they do not belong to the created upper part of the final hull.
+And after merging these points must be transferred to the lower parts of the hull, if they do not belong to the resulting upper part of the final hull.
 Otherwise, the formed hull may be incorrect.
@@
 Then searching for the left and right pivoting vertices in the concatenable queue is performed.
-After that, the queue is splits over the found vertices.
-		Fig. \ref{fig:correct_convex_hull} shows correct convex hull.
+After that, the queue is split over the found vertices.
+Fig.
+\ref{fig:correct_convex_hull} shows correct convex hull.
 
@@
 The construction of such an object requires the combination of an algorithmic database together with the necessary data structures.
-In fact, it is necessary to create an interface of generic algorithm based on ``divide-and-conquer'' strategy, which will then be used on a specific set of input data.
+In fact, it is needed to create an interface of generic algorithm based on ``divide-and-conquer'' strategy, which will then be used on a specific input data.
 
@@
 		Each of these components will represent a function in the future interface.
-Here there is a clear separation between the input type for the algorithm and the type of result it returns.
+Here there is a clear separation between the input type for the algorithm and the type of the result it returns.
 These two types should be parameters of the algorithm model.
@@
 		A large number of computational geometry algorithms, such as computing minimal spanning tree, the Delaunay triangulation, the Voronoi diagram and the convex hull accept the list of points.
-However, would be wrong limit the input type in the algorithm interface to a list of points.
-The reason for this is that some algorithms can use the results of other algorithms as input data.
+However, it would be wrong to limit the input type in the algorithm interface to a list of points.
+The reason for this is the fact that some algorithms can use the results of other algorithms as input data.
 A well known example is the construction of a Delaunay triangulation based on the Voronoi diagram maintained in a special data structure.
@@
   int inputSize(IT input)
+
   OT solveBaseCase(IT input)
+  IT preprocess(IT input)
+
   OT merge(OT first, OT second)
   Pair[IT, IT] divide(IT input)
-  IT preprocess(IT input)
+
 		\end{lstlisting}
@@
 
-		Although this model very accurately describes the class of algorithms, it does not make it possible to solve the problem directly by having input data, which in fact enables to the algorithm from how it will be executed.
-Here the principles of sequential and parallel execution are explained.
+		Although this model very accurately describes the class of algorithms, it does not make it possible to solve the problem directly by having input data.
+This in fact allows to divide implementation of the algorithm from how it is executed.
+Next the principles of sequential and parallel execution are discussed.
 
-		When executing sequentially an algorithm, its individual sub-tasks computed one by one.
+		When executing sequentially an algorithm, its individual sub-problems are computed one by one.
 We first check if current input is a base case and if so we can directly compute it by calling $solveBaseCase$ procedure.
-Otherwise input is split with $divide$ and separate sub-problem are solved sequentially.
+Otherwise input is split with $divide$ and obtained sub-problem are solved sequentially.
 Finally obtained results are merged with $merge$ procedure.
 
-		In parallel execution, it is necessary to take into account that the individual sub-problems can be calculated independently, which significantly speeds up the execution of the algorithm.
+		In parallel execution, we take into account that the individual sub-problems can be calculated independently, which significantly speeds up the execution of the algorithm.
 
-		To construct the concurrent algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$.
-which runs the functions $function1$ and $function2$ in simultaneously.
-We use it solve sub-problem obtained after the splitting the given input.
+		To construct the concurrent execution algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$.
+which runs the functions $function1$ and $function2$ simultaneously.
+We use it to solve sub-problem obtained after splitting a given input.
 Other than that parallel version is identical to the sequential one.
 
-		From the standpoint of the practical implementation the performance of such algorithm was improved by introducing a limit on the size of sub-tasks that can be calculated in parallel.
+		Practically, from the implementation standpoint performance of parallel execution was improved by introducing a limit on the size of sub-tasks that can be calculated in parallel.
 This allowed to put a threshold on the amount of work for one thread.
@@
 \subsection{Concatenable queue}
+
+		As shown in \cite{overmars}, the concatenable queue is the key data structure for the algorithm described above and is therefore the basis for the UAEM.
+Now we will focus on how to efficiently implement it in our algorithmic environment.
 
@@
 
-		By default the elements in a concatenable queue are kept i a certain predefined order \cite{aho}.
+		By default the elements in a concatenable queue are kept i a certain predefined order \cite[pp..~155-157]{aho}.
 
 		In this article the concatenable queue is implemented as a binary  $B+$ tree.
-Its vertices are divided into non-leaf and leaf vertices.
+Its vertices are divided into non-leaf and leaf ones.
 The leaf vertices contain all data kept in a tree.
 Every vertex has a pointer to its left and right child.
-For the leaf vertices those pointers point to the left and right neighbors or $null$ if the vertex is utmost in the tree.
-		Additionally every vertex keeps a pointer to a vertex with the largest element in its left sub-tree, which  allows to perform binary search \cite{aho}.
-An example of such tree is given on fig.
-1.
+For the leaf vertices those pointers point to the left and right neighboring leaf vertices or $null$ if the vertex is utmost in the tree.
+		Additionally every vertex keeps a pointer to a vertex with the largest element in its left sub-tree, which  allows to perform binary search \cite[pp..~155-157]{aho}.
 The height of each vertex is kept for the balancing during the split and merge operations.
@@
 
-		The contains operations is pretty straightforward and uses binary search over the tree vertices so its complexity is $O(\log n)$, where $n$ hereafter denotes the numbers of vertices in the queue.
+		The contains operations is pretty straightforward and uses binary search over the tree so its complexity is $O(\log n)$, where $n$ hereafter denotes the numbers of vertices in the queue.
 
@@
 Then the connections between adjacent leaf vertices are broken to insert a new one.
-Going back a new non-leaf vertices a new vertex is created - parent for the new element and one of its neighbor.
+Going back a new non-leaf vertex is created - the parent for the new element and one of its neighbor.
 The algorithm is formally described on the Listing \ref{lst:insert-alg}.
@@
 		\begin{figure}[htbp]
-			\begin{lstlisting}[caption={Queue element insertion algorithm},label={lst:insert-alg},captionpos=b]
+			\begin{lstlisting}[caption={Queue insertion algorithm},label={lst:insert-alg},captionpos=b]
 Node insert(Node node, int e):
@@
   	  else:
-  Node createdLeaf = 
-  createLeafBetween(e, node.left, node)
+        Node createdLeaf = createLeafBetween(e, node.left, node)
         result = Node(createdLeaf, createdLeaf, node)
@@
     if node.isLeaf: 
-  Node createdLeaf = 
-  createLeafBetween(e, node, node.right)
+      Node createdLeaf = createLeafBetween(e, node, node.right)
       result = Node(node, node, createdLeaf)
     else: 
-  // go left and update node.right pointer
       node.right = insert(node.right, e)
@@
 
-		Here the \textit{updateHeight} subroutine updates the value of an element height, the \textit{createLeafBetween} subroutine breaks the connection between adjacent elements and insertion of a new one.
+		Here the \textit{updateHeight} subroutine updates the height value for a given vertex, the \textit{createLeafBetween} subroutine breaks the connection between adjacent vertices ot insert a new one.
 
-		The \textit{insert} operation.
 		On the first step we find out if $leftSubtreeMax$ point to an element with greater value than the value to be inserted $e$.
-If so, then if current element is a leaf, a new element is created between the current element and its left neighbor.
+If so, then, if current element is a leaf, a new element is created between the current element and its left neighbor.
 Otherwise the search proceeds on the left sub-tree of the current element.
@@
 		Since on every step we perform a constant amount of work, the complexity of the procedure is $O(h)=O(\log n)$, where $h$ hereafter denotes the height of the tree.
-
 The operation of removing an element from the queue is performed analogously.
@@
 		The split operation is a bit more complex.
-As an input the corresponding procedure receives current element and value based on which the split is performed.
+As an input the procedure takes current element and value based on which the split is performed.
 As a result two independent queues are formed.
 The value, by which the split has been performed, belongs to the left sub-queue.
-The procedure is described formally on the Listing \ref{lst:split-alg}.
+The procedure is formally described on the Listing \ref{lst:split-alg}.
 
-		\begin{lstlisting}[caption={Queue plit algorithm},label={lst:split-alg},captionpos=b]
-split(Node node, int e, 
-  ConcatenableQueue leftQueue, 
-  ConcatenableQueue rightQueue): 
+		\begin{lstlisting}[caption={Queue split algorithm},label={lst:split-alg},captionpos=b]
+split(Node node, int e, ConcatenableQueue leftQueue, ConcatenableQueue rightQueue): 
   if node.isLeaf
@@
      rightQueue.root = node.right
-  rightQueue.minNode = 
-  node.leftSubtreeMax.right
+     rightQueue.minNode = node.leftSubtreeMax.right
 
@@
      split(node.left, e, leftQueue, rightQueue)
-  rightQueue.root = 
-  concatenateNodes(rightQueue.root, 
-  node.right, node.leftSubtreeMax)
+     rightQueue.root = concatenateNodes(rightQueue.root, node.right, node.leftSubtreeMax)
    else:
      split(node.right, e, leftQueue, rightQueue)
-  leftQueue.root = 
-  concatenateNodes(node.left, 
-  leftQueue.root, node.leftSubtreeMax)
+     leftQueue.root = concatenateNodes(node.left,  leftQueue.root, node.leftSubtreeMax)
 		\end{lstlisting}
@@
 It performs concatenation of two arbitrary elements and uses theirs heights to balance the resulting queue.
-Its implementation is described further in the work.
 The $cut$ procedure breaks connection between two adjacent leaf elements in a queue and therefore is trivial.
@@
 
-		\begin{lstlisting}[caption={Merging two queues using heights},label={lst:concatenate-als},captionpos=b]
-Node concatenateNodes(Node leftNode, 
-  Node rightNode, Node leftSubtreeMax) {
+		\begin{lstlisting}[caption={Merging two queues},label={lst:concatenate-als},captionpos=b]
+Node concatenateNodes(Node leftNode, Node rightNode, Node leftSubtreeMax) {
   if leftNode == nil:
@@
   else if leftNode.height == rightNode.height:
-  Node result = Node(leftSubtreeMax, 
-  leftNode, rightNode)
+    Node result = Node(leftSubtreeMax, leftNode, rightNode)
     updateHeight(result)
@@
   else if leftNode.height < rightNode.height:
-  rightNode.left = concatenateNodes(leftNode, 
-  rightNode.left, leftSubtreeMax)
+    rightNode.left = concatenateNodes(leftNode, rightNode.left, leftSubtreeMax)
     updateHeight(rightNode)
     return rightNode
-  else
-  leftNode.right = 
-  concatenateNodes(leftNode.right, 
-  rightNode, leftSubtreeMax)
+  else:
+    leftNode.right = concatenateNodes(leftNode.right, rightNode, leftSubtreeMax)
     updateHeight(leftNode)
@@
 		First, we consider corner cases where one of the elements is $null$.
-This is required to ensure correctness of the recursion.
+This is needed to ensure correctness of the recursion.
 Then, if the left element is higher than the right, one step down is taken for the left element.
@@
 If the heights are equal, the joining point is found and a new element must be created.
-At each step, it is necessary to update the height of current element as it changes.
+At each step, it is necessary to update the height of current element because it changes.
 
-		We begin by analyzing the complexity of the $split$ procedure by determining the complexity of the $concatenateNodes$ procedure.
-At each iteration, the step is performed either to the left son of the current element or to the right.
-The execution of the recursive procedure is finished by merging two elements.
+		We begin analyzing the complexity of the $split$ procedure by determining the complexity of the $concatenateNodes$ procedure.
+At each iteration, a step is performed either to the left son of the current element or to the right one.
+The execution of the recursive procedure finishes by merging two elements.
 Since each step moves us down one level and a constant amount of work is performed for each level, the total complexity of the $concatenateNodes$ procedure is $O(h)=O(\log n)$.
@@
 		The $split$ procedure uses the $concatenateNodes$ function as a subroutine.
-The complexity a $split$ call is equal to the complexity of $concatenateNodes$.
-The number of recursive calls $split$ for one split is $\log n$, so the total complexity of the procedure $\log^2 n$.
+The complexity of a $split$ call is equal to the complexity of $concatenateNodes$.
+The number of recursive $split$ calls for one such operation is $\log n$, so the total complexity of the procedure $\log^2 n$.
 
@@
 
-			Next, $O(\log^2 n)$ work is performed at each level. Having the height of the recursion tree, we get the total final complexity of the algorithm.
+			Next, $O(\log^2 n)$ work is performed at each level. Having the height of the recursion tree, we get the total complexity of the algorithm.
 		\end{proof}
@@
 
+We`ve considered in details the process of designing and implementing the UAEM as well unified data structures for it.
+In this model a generic interface of a ``divide-and-conquer'' algorithm was created.
+This allows us to execute the algorithms which are implemented according to this model both sequentially and in parallel.
+Apart from that concatenable queue was implemented and served as the basis for the model described above.
+
+Using the data structure allowed to significantly reduce the time and computational resources for solving set of problems, such as constructing the convex hull.
+The algorithmic environment was implemented in Java programming language using its standard library.
+The main advantages of the developed algorithm are optimized preprocessing stage and the efficiently implemented merge step, due to the usage of concatenable queue.
+
+The performance comparison for both types of execution allows to conclude that the algorithm has high level of parallelism.
+We`ve achieved speedup of $28\%$ in the best case.
+It is easy to extend functionality of the created environment either by adding new or modifying existing algorithms.
+This flexibility is achieved by using the modular principle in its design and choosing optimal abstractions to represent algorithms.
+
 \begin{thebibliography}{00}
@@
 A.
-Hamprecht, ``Ilastik: Interactive learning and segmentation toolkit,'' 2011 IEEE International Symposium on Biomedical Imaging: From Nano to Macro, Chicago, IL, 2011, pp.
+Hamprecht, ``Ilastik: Interactive learning and segmentation toolkit,'' 2011 IEEE International Symposium on Biomedical Imaging: From Nano to Macro, Chicago, IL, 2011, pp..
 230-233.
@@
 
-	\bibitem{aggarwal} А. Aggarwal et al., ``Parallel computational geometry,'' Algorithmica 3, 1-4 (November 1988), pp. 293-327.
+	\bibitem{aggarwal} А. Aggarwal et al., ``Parallel computational geometry,'' Algorithmica 3, 1-4 (November 1988), pp.. 293-327.
 
-	\bibitem{atallah} M.J. Atallah, R. Cole, M.T. Goodrich, ``Cascading divide-and-conquer: a technique for designing parallel algorithms,'' SIAM J. Comput. 18, 1989, pp. 499-532.
+	\bibitem{atallah} M.J. Atallah, R. Cole, M.T. Goodrich, ``Cascading divide-and-conquer: a technique for designing parallel algorithms,'' SIAM J. Comput. 18, 1989, pp.. 499-532.
 
@@
 Cole, M.T.
-Goodrich, ``Optimal parallel algorithms for polygon and point-set problems,'' In Proceedings of the fourth annual symposium on Computational geometry (SCG '88), ACM, New York, NY, USA, pp.
+Goodrich, ``Optimal parallel algorithms for polygon and point-set problems,'' In Proceedings of the fourth annual symposium on Computational geometry (SCG '88), ACM, New York, NY, USA, pp..
 201-210.
 
-	\bibitem{amato} N.
-M.
-Amato, M.
-T.
-Goodrich and E.
-A.
-Ramos, ``Parallel algorithms for higher-dimensional convex hulls,'' Proceedings 35th Annual Symposium on Foundations of Computer Science, Santa Fe, NM, USA, 1994, pp.
+	\bibitem{amato} N.M.
+Amato, M.T.
+Goodrich and E.A.
+Ramos, ``Parallel algorithms for higher-dimensional convex hulls,'' Proceedings 35th Annual Symposium on Foundations of Computer Science, Santa Fe, NM, USA, 1994, pp..
 683-694.
 
-	\bibitem{chen} D. Z. Chen, ``Efficient geometric algorithms on the EREW PRAM,'' in IEEE Transactions on Parallel and Distributed Systems, vol. 6, no. 1, pp. 41-47, Jan. 1995.
+	\bibitem{chen} D.Z. Chen, ``Efficient geometric algorithms on the EREW PRAM,'' in IEEE Transactions on Parallel and Distributed Systems, vol. 6, no. 1, pp.. 41-47, Jan. 1995.
 	doi: 10.1109/71.363412
 
-	\bibitem{berkman} O. Berkman, B. Schieber, U. Vishkin, ``A fast parallel algorithm for finding the convex hull of a sorted point set,'' Internat. J. Comput. Geom. Appl. 6, 1996, pp. 231-242.
+	\bibitem{berkman} O. Berkman, B. Schieber, U. Vishkin, ``A fast parallel algorithm for finding the convex hull of a sorted point set,'' Internat. J. Comput. Geom. Appl. 6, 1996, pp.. 231-242.
 
@@
 
-	\bibitem{akl} Selim G. Akl and Kelly A. Lyons, Parallel Computational Geometry. Englewood Cliffs: Prentice-Hall, 1993.
+	\bibitem{akl} Selim G. Akl and Kelly A. Lyons, Parallel Computational Geometry, Englewood Cliffs: Prentice-Hall, 1993.
 
@@
 
-	\bibitem{leeuwen} J. Van Leeuwen, Handbook of Theoretical Computer Science, Amsterdam: Elsevier/The MIT
-	Press, 1990.
+	\bibitem{leeuwen} J. Van Leeuwen, Handbook of Theoretical Computer Science, Amsterdam: Elsevier/The MIT Press, 1990.
 
@@
 
-	\bibitem{tereshchenko} V. N. Tereshchenko, A. V. Anisimov, Recursion and parallel algorithms in geometric modeling
-	problems, Journal: Cybernetics and Systems Analysis: Vol. 46, N 2 (2010), pp. 173-184.
+	\bibitem{tereshchenko} V.
+N.
+Tereshchenko, A.
+V.
+Anisimov, Recursion and parallel algorithms in geometric modeling problems, Journal: Cybernetics and Systems Analysis: Vol.
+46, N 2 (2010), pp..
+173-184.
+
+	\bibitem{overmars} Mark H. Overmars, Jan van Leeuwen, ``Maintenance of configurations in the plane,'' Journal of Computer and System Sciences, Volume 23, Issue 2, 1981, pp.. 166-204.
+
+	\bibitem{aho} Alfred V. Aho and John E. Hopcroft, The Design and Analysis of Computer Algorithms, 1st ed. Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA, 1974.
 \end{thebibliography}

### 2019-12-23 SoCG EA/article-SoCG-EA.tex
SoCG EA, SoCG, acm siggraph + restructuring

--- 2019-11-20 article/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\documentclass[a4paper,UKenglish,cleveref, autoref]{socg-lipics-v2019}
+%This is a template for producing LIPIcs articles. 
+%See lipics-manual.pdf for further information.
+%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
+%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
+%for section-numbered lemmas etc., use "numberwithinsect"
+%for enabling cleveref support, use "cleveref"
+%for enabling cleveref support, use "autoref"
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
 
-\usepackage{diagbox}
-\usepackage{amsthm}
-\usepackage[formats]{listings}
+\bibliographystyle{plainurl}% the mandatory bibstyle
+\graphicspath{{images/}}
+\DeclareGraphicsExtensions{.pdf,.png,.jpg}
 \lstset{
 	language=Java,
-	basicstyle=\small,
 	breaklines,
 }
-\graphicspath{{images/}}
-\DeclareGraphicsExtensions{.pdf,.png,.jpg}
-\theoremstyle{plane}
-\newtheorem{theorem}{Theorem}[section]
+
+\title{Unified data structures for solving optimally a set of interrelated computational geometry problems} 
+\titlerunning{Data structures for solving a set of computational geometry problems}%optional, please use if title is longer than one line
+
+\author{Vasyl Tereshchenko}{
+	Faculty of computer science and cybernetics, Taras Shevchenko National University of Kyiv, Ukraine}
+{vtereshch@gmail.com}{}{}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
+Please provide at least the name of the affiliation and the country.
+The full address is optional
+%\footnote{}
+\author{Semen Chudakov}{Faculty of computer science and cybernetics, Taras Shevchenko National University of Kyiv, Ukraine}
+{semen.chudakov7@gmail.com}{}{}
+
+\authorrunning{V. Tereshchenko and S. Chudakov}%TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+
+\Copyright{Vasyl Tereshchenko and Semen Chudakov}%TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\ccsdesc[500]{Theory of computation~Computational geometry}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+
+\keywords{Algorithmic tools,   Computational geometry, Interrelated problems set, Unified algorithmic environment, Concatenable queue}%TODO mandatory; please add comma-separated list of keywords
+
+\category{}%optional, e.g. invited paper
+
+\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+%\relatedversion{A full version of the paper is available at \url{...}.}
+
+\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+
+%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
+Please enter author specific funding statements as fifth argument of the \author macro.
+
+\acknowledgements{}%optional
+
+%\nolinenumbers %uncomment to disable line numbering
+
+%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{}
+\EventNoEds{2}
+\EventLongTitle{36th International Symposium on Computational Geometry (SoCG 2020)}
+\EventShortTitle{SoCG 2020}
+\EventAcronym{SoCG}
+\EventYear{2020}
+\EventDate{June  23--26, 2020}
+\EventLocation{Zürich, Switzerland}
+\EventLogo{socg-logo}
+\SeriesVolume{}
+\ArticleNo{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{Unified data structures for solving optimally a set of interrelated computational geometry problems*}
-\author{
-\IEEEauthorblockN{1\textsuperscript{st} Vasyl Tereshchenko}
-\IEEEauthorblockA{\textit{Faculty of computer science and cybernetics} \\
-\textit{Taras Shevchenko National University of Kyiv}\\
-Kyiv , Ukraine \\
-vtereshch@gmail.com}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Semen Chudakov}
-\IEEEauthorblockA{\textit{Faculty of computer science and cybernetics} \\
-\textit{Taras Shevchenko National University of Kyiv}\\
-Kyiv , Ukraine \\
-semen.chudakov7@gmail.com}
-}
 \maketitle
 
+%TODO mandatory: add short abstract of the document
 \begin{abstract}
@@
 
-\begin{IEEEkeywords}
-Algorithmic tools,   Computational geometry, Interrelated problems set, Unified algorithmic environment, Concatenable queue
-\end{IEEEkeywords}
-
 \section{Introduction}
+\label{sec:introduction}
 
@@
 \section{Unified algorithmic environment}
+\label{sec:unified-algorithmic-environment}
 \subsection{Algorithms stages}
@@
 	\end{equation}
-		According to this definition, the possible cases for points $a_1,a_2,a_3$ are given in Table \ref{table:3points}:
-
-		\begin{table}[htbp]
-			\caption{3-points base cases}
-			\label{table:3points}
-			\begin{center}
-				\begin{tabular}{|c|c|c|c|}
-					\hline
-					\textbf{$\lambda(a_1, a_2) > \lambda(a_2, a_3)$} & \textbf{$y(a_1) < y(a_2)$} & upper part & lower part\\
-					\hline
-					false & false & $a_1, a_3$ & $a_2$ \\
-					\hline
-					false & true & $a_1, a_3$ & $a_2$ \\
-					\hline
-					true & false & $a_2, a_3$ & $a_1$ \\
-					\hline
-					true & true & $a_1, a_2$ & $a_3$ \\
-					\hline
-				\end{tabular} 
-			\end{center}
-		\end{table}
 
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{ch_union}}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.8\textwidth, height=0.3\textheight]{ch_union}
 		\caption{Merging step of two hulls}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_search}}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.8\textwidth, height=0.3\textheight]{incorect_search}
 		\caption{Example of an incorrect position of the utmost left in the left sub-hull}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_edge_points}}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.8\textwidth, height=0.3\textheight]{incorect_edge_points}
 		\caption{Example of a convex hull for a wrong position of the utmost left points of the left sub-hull}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_lower_subhull}}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.8\textwidth, height=0.3\textheight]{incorect_lower_subhull}
 		\caption{An example of a non-integral hull after merging along the reference lines}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{correct_convex_hull}}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.8\textwidth, height=0.3\textheight]{correct_convex_hull}
 		\caption{Correctly constructed convex hull}
@@
 
-		\begin{lstlisting}[caption={Algorithm model based on the ``divide-and-conquer'' principle},label={lst:algmodel},captionpos=b]
+	\begin{lstlisting}[caption={Algorithm model based on the ``divide-and-conquer'' principle},label={lst:algmodel},captionpos=t,float,abovecaptionskip=-\medskipamount]
 interface DaCAlgorithm[IT, OT]:
-
     boolean isBaseCase(IT input)
@@
     Pair[IT, IT] divide(IT input)
-
 	\end{lstlisting}
 
-\subsection{Sequential and parallel execution}
+\section{Algorithm analysis and performance evaluation}
+\label{sec:algorithm-analysis-and-performance-evaluation}
+\subsection{Complexity}
 
-		Although this model very accurately describes the class of algorithms, it does not make it possible to solve the problem directly by having input data.
-This in fact allows to divide implementation of the algorithm from how it is executed.
-Next the principles of sequential and parallel execution are discussed.
-
-		When executing sequentially an algorithm, its individual sub-problems are computed one by one.
-We first check if current input is a base case and if so we can directly compute it by calling $solveBaseCase$ procedure.
-Otherwise input is split with $divide$ and obtained sub-problem are solved sequentially.
-Finally obtained results are merged with $merge$ procedure.
-
-		In parallel execution, we take into account that the individual sub-problems can be calculated independently, which significantly speeds up the execution of the algorithm.
-
-		To construct the concurrent execution algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$.
-which runs the functions $function1$ and $function2$ simultaneously.
-We use it to solve sub-problem obtained after splitting a given input.
-Other than that parallel version is identical to the sequential one.
-
-		Practically, from the implementation standpoint performance of parallel execution was improved by introducing a limit on the size of sub-tasks that can be calculated in parallel.
-This allowed to put a threshold on the amount of work for one thread.
-
-\section{Implementation details}
-\subsection{Concatenable queue}
-
-		As shown in \cite{overmars}, the concatenable queue is the key data structure for the algorithm described above and is therefore the basis for the UAEM.
-Now we will focus on how to efficiently implement it in our algorithmic environment.
-
-		Concatenable queue is an Abstract Data Type, that supports following operations:
-
-		\begin{itemize}
-			\item
-			ADD\_ELEMENT();
-			\item
-			REMOVE\_ELEMENT();
-			\item
-			GET\_MINIMUM();
-			\item
-			CONTAINS();
-			\item
-			SPLIT();
-			\item
-			MERGE().
-		\end{itemize}
-
-		By default the elements in a concatenable queue are kept i a certain predefined order \cite[pp..~155-157]{aho}.
-
-		In this article the concatenable queue is implemented as a binary  $B+$ tree.
-Its vertices are divided into non-leaf and leaf ones.
-The leaf vertices contain all data kept in a tree.
-Every vertex has a pointer to its left and right child.
-For the leaf vertices those pointers point to the left and right neighboring leaf vertices or $null$ if the vertex is utmost in the tree.
-		Additionally every vertex keeps a pointer to a vertex with the largest element in its left sub-tree, which  allows to perform binary search \cite[pp..~155-157]{aho}.
-The height of each vertex is kept for the balancing during the split and merge operations.
-It is measured as a maximum amount of steps it is possible to do in order to reach a leaf vertex.
-
-		From now we will go into details on how this data structure is implemented.
-
-		The contains operations is pretty straightforward and uses binary search over the tree so its complexity is $O(\log n)$, where $n$ hereafter denotes the numbers of vertices in the queue.
-
-		Algorithm of inserting an element in a queue looks like as follows.
-First, the position of a new vertex is searched.
-Then the connections between adjacent leaf vertices are broken to insert a new one.
-Going back a new non-leaf vertex is created - the parent for the new element and one of its neighbor.
-The algorithm is formally described on the Listing \ref{lst:insert-alg}.
-
-		\begin{figure}[htbp]
-			\begin{lstlisting}[caption={Queue insertion algorithm},label={lst:insert-alg},captionpos=b]
-Node insert(Node node, int e):
-  Node result = nil
-  if e <= node.leftSubtreeMax.data: 
-  	if node.isLeaf:
-  	  if e == node.data:
-        node.data = e
-  	  else:
-        Node createdLeaf = createLeafBetween(e, node.left, node)
-        result = Node(createdLeaf, createdLeaf, node)
-    else:
-      node.left = insert(node.left, e)
-  else:
-    if node.isLeaf: 
-      Node createdLeaf = createLeafBetween(e, node, node.right)
-      result = Node(node, node, createdLeaf)
-    else: 
-      node.right = insert(node.right, e)
-
-  if result == nil:
-  	result = node
-
-  updateHeight(result)
-  return result
-			\end{lstlisting}
-		\end{figure}
-
-		Here the \textit{updateHeight} subroutine updates the height value for a given vertex, the \textit{createLeafBetween} subroutine breaks the connection between adjacent vertices ot insert a new one.
-
-		On the first step we find out if $leftSubtreeMax$ point to an element with greater value than the value to be inserted $e$.
-If so, then, if current element is a leaf, a new element is created between the current element and its left neighbor.
-Otherwise the search proceeds on the left sub-tree of the current element.
-The case, when $leftSubtreeMax$ is smaller than the value $e$ is analogous.
-The procedure ends with updating the height on a newly created element.
-The element is returned as its result value.
-
-		Since on every step we perform a constant amount of work, the complexity of the procedure is $O(h)=O(\log n)$, where $h$ hereafter denotes the height of the tree.
-The operation of removing an element from the queue is performed analogously.
-
-		The split operation is a bit more complex.
-As an input the procedure takes current element and value based on which the split is performed.
-As a result two independent queues are formed.
-The value, by which the split has been performed, belongs to the left sub-queue.
-The procedure is formally described on the Listing \ref{lst:split-alg}.
-
-		\begin{lstlisting}[caption={Queue split algorithm},label={lst:split-alg},captionpos=b]
-split(Node node, int e, ConcatenableQueue leftQueue, ConcatenableQueue rightQueue): 
-  if node.isLeaf
-    leftQueue.root = node
-    leftQueue.maxNode = node	
-    rightQueue.minNode = node.right	
-    cut(node)
-  else:
-    if e == node.leftSubtreeMax.data:
-      leftQueue.root = node.left
-      leftQueue.maxNode = node.leftSubtreeMax
-
-     rightQueue.root = node.right
-     rightQueue.minNode = node.leftSubtreeMax.right
-
-     cut(node.leftSubtreeMax)
-   else if e < node.leftSubtreeMax.data:
-     split(node.left, e, leftQueue, rightQueue)
-     rightQueue.root = concatenateNodes(rightQueue.root, node.right, node.leftSubtreeMax)
-   else:
-     split(node.right, e, leftQueue, rightQueue)
-     leftQueue.root = concatenateNodes(node.left,  leftQueue.root, node.leftSubtreeMax)
-		\end{lstlisting}
-
-		Here the $concatenateNodes$ procedure is used.
-It performs concatenation of two arbitrary elements and uses theirs heights to balance the resulting queue.
-The $cut$ procedure breaks connection between two adjacent leaf elements in a queue and therefore is trivial.
-On the first step in the $split$ operation we check, is the current element is a leaf.
-Is so, its connection are broken and the value of $maxNode$ is updated for the left queue as well as the value of $minNode$ for the right queue.
-If element is not a leaf, then the procedure continues of either left or right sub-tree.
-Here a special corner cases is considered, where $leftSubtreeMax$ contain the dividing value.
-Then the analogous action to the usual search are performed.
-
-		The algorithm of the $concatenateNodes$ procedure is described on the Listing \ref{lst:concatenate-als}.
-
-		\begin{lstlisting}[caption={Merging two queues},label={lst:concatenate-als},captionpos=b]
-Node concatenateNodes(Node leftNode, Node rightNode, Node leftSubtreeMax) {
-  if leftNode == nil:
-    return rightNode
-  else if rightNode == nil: 
-    return leftNode
-  else if leftNode.height == rightNode.height:
-    Node result = Node(leftSubtreeMax, leftNode, rightNode)
-    updateHeight(result)
-    return result
-  else if leftNode.height < rightNode.height:
-    rightNode.left = concatenateNodes(leftNode, rightNode.left, leftSubtreeMax)
-    updateHeight(rightNode)
-    return rightNode
-  else:
-    leftNode.right = concatenateNodes(leftNode.right, rightNode, leftSubtreeMax)
-    updateHeight(leftNode)
-    return leftNode
-		\end{lstlisting}
-
-		First, we consider corner cases where one of the elements is $null$.
-This is needed to ensure correctness of the recursion.
-Then, if the left element is higher than the right, one step down is taken for the left element.
-If the right element is higher - we take a step down for it.
-If the heights are equal, the joining point is found and a new element must be created.
-At each step, it is necessary to update the height of current element because it changes.
-
-		We begin analyzing the complexity of the $split$ procedure by determining the complexity of the $concatenateNodes$ procedure.
-At each iteration, a step is performed either to the left son of the current element or to the right one.
-The execution of the recursive procedure finishes by merging two elements.
-Since each step moves us down one level and a constant amount of work is performed for each level, the total complexity of the $concatenateNodes$ procedure is $O(h)=O(\log n)$.
-
-		The $split$ procedure uses the $concatenateNodes$ function as a subroutine.
-The complexity of a $split$ call is equal to the complexity of $concatenateNodes$.
-The number of recursive $split$ calls for one such operation is $\log n$, so the total complexity of the procedure $\log^2 n$.
-
-		The merge operation of two queues is reduced to the clamping of their root vertices by the $concatenateNodes$ procedure, so its complexity is $O(\log n)$.
-
-\section{Algorithm analysis and performance evaluation}
-\subsection{Complexity}
 % //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
@@
 
-			\begin{itemize}
+		\begin{enumerate}
 			\item
@@
 			Recursive ascent and merging parts of the convex hull $O(\log n)$.
-				\begin{itemize}
+			\begin{alphaenumerate}
 				\item
@@
 				Normalization of the obtained lower part $O(\log n)$.
-				\end{itemize}
-			\end{itemize}
+			\end{alphaenumerate}
+		\end{enumerate}
 
@@
 
+\subsection{Performance}
+\label{sec:performance}
+
 % //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
@@
 
-\subsection{Performance}
-		A number of algorithm performance measurements were performed for different input sizes and the average number of recursive tasks per thread. The results are shown on the Fig. \ref{fig:performance}.
+	A number of algorithm performance measurements were performed for different input sizes and the average number of recursive subproblems per thread.
+The results are shown on the Fig.
+\ref{fig:performance}.
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.5\textwidth, height=0.3\textheight]{performance}}
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=1\textwidth, height=0.4\textheight]{performance}
 		\caption{Performance data}
@@
 	\end{figure}
+
 \section{Conclusion}
@@
 
-\begin{thebibliography}{00}
-	\bibitem{ilastik} C.
-Sommer, C.
-Straehle, U.
-Köthe and F.
-A.
-Hamprecht, ``Ilastik: Interactive learning and segmentation toolkit,'' 2011 IEEE International Symposium on Biomedical Imaging: From Nano to Macro, Chicago, IL, 2011, pp..
-230-233.
-	doi: 10.1109/ISBI.2011.5872394
-
-	\bibitem{imaris} IMARIS Software. Accessed on: 15.04.2019. [Online]. Available: https://imaris.oxinst.com
-
-	\bibitem{imagej} ImageJ: An open platform for scientific image analysis. Accessed on: 15.04.2019. [Online]. Available: https://imagej.net/Welcome
-
-	\bibitem{aggarwal} А. Aggarwal et al., ``Parallel computational geometry,'' Algorithmica 3, 1-4 (November 1988), pp.. 293-327.
-
-	\bibitem{atallah} M.J. Atallah, R. Cole, M.T. Goodrich, ``Cascading divide-and-conquer: a technique for designing parallel algorithms,'' SIAM J. Comput. 18, 1989, pp.. 499-532.
-
-	\bibitem{cole} R.
-Cole, M.T.
-Goodrich, ``Optimal parallel algorithms for polygon and point-set problems,'' In Proceedings of the fourth annual symposium on Computational geometry (SCG '88), ACM, New York, NY, USA, pp..
-201-210.
-
-	\bibitem{amato} N.M.
-Amato, M.T.
-Goodrich and E.A.
-Ramos, ``Parallel algorithms for higher-dimensional convex hulls,'' Proceedings 35th Annual Symposium on Foundations of Computer Science, Santa Fe, NM, USA, 1994, pp..
-683-694.
-
-	\bibitem{chen} D.Z. Chen, ``Efficient geometric algorithms on the EREW PRAM,'' in IEEE Transactions on Parallel and Distributed Systems, vol. 6, no. 1, pp.. 41-47, Jan. 1995.
-	doi: 10.1109/71.363412
-
-	\bibitem{berkman} O. Berkman, B. Schieber, U. Vishkin, ``A fast parallel algorithm for finding the convex hull of a sorted point set,'' Internat. J. Comput. Geom. Appl. 6, 1996, pp.. 231-242.
-
-	\bibitem{goodman} J.E. Goodman and J. O'Rourke, editors,  Handbook of Discrete and Computational Geometry, CRC Press LLC, Boca Raton, FL, 2004.
-
-	\bibitem{akl} Selim G. Akl and Kelly A. Lyons, Parallel Computational Geometry, Englewood Cliffs: Prentice-Hall, 1993.
-
-	\bibitem{jaja} J. JaJa, An Introduction to Parallel Algorithms, Amsterdam: Addison-Wesley, 1992.
-
-	\bibitem{leeuwen} J. Van Leeuwen, Handbook of Theoretical Computer Science, Amsterdam: Elsevier/The MIT Press, 1990.
-
-	\bibitem{reif} J.H. Reif, Synthesis of Parallel Algorithms, San Mateo: Morgan Kaufmann, 1993.
-
-	\bibitem{tereshchenko} V.
-N.
-Tereshchenko, A.
-V.
-Anisimov, Recursion and parallel algorithms in geometric modeling problems, Journal: Cybernetics and Systems Analysis: Vol.
-46, N 2 (2010), pp..
-173-184.
-
-	\bibitem{overmars} Mark H. Overmars, Jan van Leeuwen, ``Maintenance of configurations in the plane,'' Journal of Computer and System Sciences, Volume 23, Issue 2, 1981, pp.. 166-204.
-
-	\bibitem{aho} Alfred V. Aho and John E. Hopcroft, The Design and Analysis of Computer Algorithms, 1st ed. Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA, 1974.
-\end{thebibliography}
+\bibliography{article-SoCG-EA}
 \end{document}

### 2019-12-23 SoCG/article-SoCG.tex
SoCG EA, SoCG, acm siggraph + restructuring

--- 2019-11-20 article/article.tex
@@
     Pair[IT, IT] divide(IT input)
-
 	\end{lstlisting}
@@
 \section{Implementation details}
+\label{sec:implementation-details}
 \subsection{Concatenable queue}
@@
     return result
+
 		\end{lstlisting}
@@
 \section{Algorithm analysis and performance evaluation}
+\label{sec:algorithm-analysis-and-performance-evaluation}
 \subsection{Complexity}
+
 % //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
@@
 
+\subsection{Performance}
+
 % //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
@@
 	\end{figure}
+
 \section{Conclusion}
+\label{sec:coclusion}
 
@@
 
-\begin{thebibliography}{00}
-	\bibitem{ilastik} C.
-Sommer, C.
-Straehle, U.
-Köthe and F.
-A.
-Hamprecht, ``Ilastik: Interactive learning and segmentation toolkit,'' 2011 IEEE International Symposium on Biomedical Imaging: From Nano to Macro, Chicago, IL, 2011, pp..
-230-233.
-	doi: 10.1109/ISBI.2011.5872394
-
-	\bibitem{imaris} IMARIS Software. Accessed on: 15.04.2019. [Online]. Available: https://imaris.oxinst.com
-
-	\bibitem{imagej} ImageJ: An open platform for scientific image analysis. Accessed on: 15.04.2019. [Online]. Available: https://imagej.net/Welcome
-
-	\bibitem{aggarwal} А. Aggarwal et al., ``Parallel computational geometry,'' Algorithmica 3, 1-4 (November 1988), pp.. 293-327.
-
-	\bibitem{atallah} M.J. Atallah, R. Cole, M.T. Goodrich, ``Cascading divide-and-conquer: a technique for designing parallel algorithms,'' SIAM J. Comput. 18, 1989, pp.. 499-532.
-
-	\bibitem{cole} R.
-Cole, M.T.
-Goodrich, ``Optimal parallel algorithms for polygon and point-set problems,'' In Proceedings of the fourth annual symposium on Computational geometry (SCG '88), ACM, New York, NY, USA, pp..
-201-210.
-
-	\bibitem{amato} N.M.
-Amato, M.T.
-Goodrich and E.A.
-Ramos, ``Parallel algorithms for higher-dimensional convex hulls,'' Proceedings 35th Annual Symposium on Foundations of Computer Science, Santa Fe, NM, USA, 1994, pp..
-683-694.
-
-	\bibitem{chen} D.Z. Chen, ``Efficient geometric algorithms on the EREW PRAM,'' in IEEE Transactions on Parallel and Distributed Systems, vol. 6, no. 1, pp.. 41-47, Jan. 1995.
-	doi: 10.1109/71.363412
-
-	\bibitem{berkman} O. Berkman, B. Schieber, U. Vishkin, ``A fast parallel algorithm for finding the convex hull of a sorted point set,'' Internat. J. Comput. Geom. Appl. 6, 1996, pp.. 231-242.
-
-	\bibitem{goodman} J.E. Goodman and J. O'Rourke, editors,  Handbook of Discrete and Computational Geometry, CRC Press LLC, Boca Raton, FL, 2004.
-
-	\bibitem{akl} Selim G. Akl and Kelly A. Lyons, Parallel Computational Geometry, Englewood Cliffs: Prentice-Hall, 1993.
-
-	\bibitem{jaja} J. JaJa, An Introduction to Parallel Algorithms, Amsterdam: Addison-Wesley, 1992.
-
-	\bibitem{leeuwen} J. Van Leeuwen, Handbook of Theoretical Computer Science, Amsterdam: Elsevier/The MIT Press, 1990.
-
-	\bibitem{reif} J.H. Reif, Synthesis of Parallel Algorithms, San Mateo: Morgan Kaufmann, 1993.
-
-	\bibitem{tereshchenko} V.
-N.
-Tereshchenko, A.
-V.
-Anisimov, Recursion and parallel algorithms in geometric modeling problems, Journal: Cybernetics and Systems Analysis: Vol.
-46, N 2 (2010), pp..
-173-184.
-
-	\bibitem{overmars} Mark H. Overmars, Jan van Leeuwen, ``Maintenance of configurations in the plane,'' Journal of Computer and System Sciences, Volume 23, Issue 2, 1981, pp.. 166-204.
-
-	\bibitem{aho} Alfred V. Aho and John E. Hopcroft, The Design and Analysis of Computer Algorithms, 1st ed. Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA, 1974.
-\end{thebibliography}
+\bibliography{article-SoCG}
 \end{document}

### 2019-12-23 acm siggraph/article-acm-siggraph.tex
SoCG EA, SoCG, acm siggraph + restructuring

--- 2019-11-20 article/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
-\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
-		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+%%
+%% This is file `sample-sigconf.tex',
+%% generated with the docstrip utility.
+%%
+%% The original source files were:
+%%
+%% samples.dtx  (with options: `sigconf')
+%% 
+%% IMPORTANT NOTICE:
+%% 
+%% For the copyright see the source file.
+%% 
+%% Any modified versions of this file must be renamed
+%% with new filenames distinct from sample-sigconf.tex.
+%% 
+%% For distribution of the original source see the terms
+%% for copying and modification in the file samples.dtx.
+%% 
+%% This generated file may be distributed as long as the
+%% original source files, as listed above, are part of the
+%% same distribution. (The sources need not necessarily be
+%% in the same archive or directory.)
+%%
+%% The first command in your LaTeX source must be the \documentclass command.
+\documentclass[sigconf]{acmart}
 
-\usepackage{diagbox}
-\usepackage{amsthm}
-\usepackage[formats]{listings}
+\usepackage{listings}
 \lstset{
 	language=Java,
-	basicstyle=\small,
 	breaklines,
@@
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
-\theoremstyle{plane}
-\newtheorem{theorem}{Theorem}[section]
 
+%%
+%% \BibTeX command to typeset BibTeX logo in the docs
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+
+%% Rights management information.  This information is sent to you
+%% when you complete the rights form.  These commands have SAMPLE
+%% values in them; it is your responsibility as an author to replace
+%% the commands and values with those provided to you when you
+%% complete the rights form.
+\setcopyright{acmcopyright}
+\copyrightyear{2018}
+\acmYear{2018}
+\acmDOI{10.1145/1122445.1122456}
+
+%% These commands are for a PROCEEDINGS abstract or paper.
+\acmConference[I3D’19]{ACM SIGGRAPH Symposium on
+Interactive 3D Graphics and Games}{May 05--07, 2020}{San Francisco, USA}
+%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
+ % June 03--05, 2018, Woodstock, NY}
+\acmPrice{15.00}
+\acmISBN{978-1-4503-XXXX-X/18/06}
+
+%%
+%% Submission ID.
+%% Use this when submitting an article to a sponsored event. You'll
+%% receive a unique submission ID from the organizers
+%% of the event, and this ID should be used as the parameter to this command.
+%%\acmSubmissionID{123-A56-BU3}
+
+%%
+%% The majority of ACM publications use numbered citations and
+%% references.  The command \citestyle{authoryear} switches to the
+%% "author year" style.
+%%
+%% If you are preparing content for an event
+%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
+%% citations and references.
+%% Uncommenting
+%% the next command will enable that style.
+%%\citestyle{acmauthoryear}
+
+%%
+%% end of the preamble, start of the body of the document source.
 \begin{document}
 
-\title{Unified data structures for solving optimally a set of interrelated computational geometry problems*}
-\author{
-\IEEEauthorblockN{1\textsuperscript{st} Vasyl Tereshchenko}
-\IEEEauthorblockA{\textit{Faculty of computer science and cybernetics} \\
-\textit{Taras Shevchenko National University of Kyiv}\\
-Kyiv , Ukraine \\
-vtereshch@gmail.com}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Semen Chudakov}
-\IEEEauthorblockA{\textit{Faculty of computer science and cybernetics} \\
-\textit{Taras Shevchenko National University of Kyiv}\\
-Kyiv , Ukraine \\
-semen.chudakov7@gmail.com}
-}
-\maketitle
+%%
+%% The "title" command has an optional parameter,
+%% allowing the author to define a "short title" to be used in page headers.
+\title{Application of concatenable queue for creation unified data structures in 3-D simulation}
 
+%%
+%% The "author" command and its associated commands are used to define
+%% the authors and their affiliations.
+%% Of note is the shared affiliation of the first two authors, and the
+%% "authornote" and "authornotemark" commands
+%% used to denote shared contribution to the research.
+
+%\author{Vasyl Tereshchenko}
+%\authornote{Both authors contributed equally to this research.}
+%\email{vtereshch@gmail.com}
+%\orcid{0000-0002-0139-6049}
+%\author{Semen Chudakov}
+%\authornotemark[1]
+%\email{semen.chudakov7@gmail.com}
+%\affiliation{%
+%  \institution{Taras Shevchenko National University of Kyiv}
+%  \streetaddress{P.O. Box 01601}
+%  \city{Kyiv}
+%  \state{}
+%  \postcode{}
+%}
+
+%\author{Lars Th{\o}rv{\"a}ld}
+%\affiliation{%
+%  \institution{The Th{\o}rv{\"a}ld Group}
+%  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
+%  \city{Hekla}
+%  \country{Iceland}}
+%\email{larst@affiliation.org}
+
+%\author{Valerie B\'eranger}
+%\affiliation{%
+%  \institution{Inria Paris-Rocquencourt}
+%  \city{Rocquencourt}
+%  \country{France}
+%}
+
+%\author{Aparna Patel}
+%\affiliation{%
+% \institution{Rajiv Gandhi University}
+% \streetaddress{Rono-Hills}
+% \city{Doimukh}
+% \state{Arunachal Pradesh}
+% \country{India}}
+
+%\author{Huifen Chan}
+%\affiliation{%
+%  \institution{Tsinghua University}
+%  \streetaddress{30 Shuangqing Rd}
+%  \city{Haidian Qu}
+%  \state{Beijing Shi}
+%  \country{China}}
+
+%\author{Charles Palmer}
+%\affiliation{%
+%  \institution{Palmer Research Laboratories}
+%  \streetaddress{8600 Datapoint Drive}
+%  \city{San Antonio}
+%  \state{Texas}
+%  \postcode{78229}}
+%\email{cpalmer@prl.com}
+
+%\author{John Smith}
+%\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
+%\email{jsmith@affiliation.org}
+
+%\author{Julius P. Kumquat}
+%\affiliation{\institution{The Kumquat Consortium}}
+%\email{jpkumquat@consortium.net}
+
+%%
+%% By default, the full list of authors will be used in the page
+%% headers. Often, this list is too long, and will overlap
+%% other information printed in the page headers. This command allows
+%% the author to define a more concise list
+%% of authors' names for this purpose.
+%\renewcommand{\shortauthors}{Tereshchenko and Chudakov}
+
+%%
+%% The abstract is a short summary of the work to be presented in the
+%% article.
 \begin{abstract}
@@
 
-\begin{IEEEkeywords}
-Algorithmic tools,   Computational geometry, Interrelated problems set, Unified algorithmic environment, Concatenable queue
-\end{IEEEkeywords}
+%%
+%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+%% Please copy and paste the code instead of the example below.
+%%
+\begin{CCSXML}
+<ccs2012>
+ <concept>
+  <concept_id>10010520.10010553.10010562</concept_id>
+  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+  <concept_significance>500</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010575.10010755</concept_id>
+  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+  <concept_significance>300</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10010520.10010553.10010554</concept_id>
+  <concept_desc>Computer systems organization~Robotics</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+ <concept>
+  <concept_id>10003033.10003083.10003095</concept_id>
+  <concept_desc>Networks~Network reliability</concept_desc>
+  <concept_significance>100</concept_significance>
+ </concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Computer systems organization~Embedded systems}
+\ccsdesc[300]{Computer systems organization~Redundancy}
+\ccsdesc{Computer systems organization~Robotics}
+\ccsdesc[100]{Networks~Network reliability}
+
+%%
+%% Keywords. The author(s) should pick words that accurately describe
+%% the work being presented. Separate the keywords with commas.
+\keywords{unified data structure, simulation problem, interrelated problems set, unified algorithmic environment, concatenable queue}
+
+%% A "teaser" image appears between the author and affiliation
+%% information and the body of the document, and typically spans the
+%% page.
+%%
+%% This command processes the author and affiliation and title
+%% information and builds the first part of the formatted document.
+\maketitle
 
 \section{Introduction}
+\label{sec:introduction}
 
@@
 Then, by the criterion, the points $a_2, a_3, ..., a_{k-1}$ must be removed.
-Analogously for the vertical case.
+Similarly for the vertical case.
 
-		Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last one (if there are more than two repetitions).
-The idea behind the algorithm is to use two pointers technique to delete repetitions by overwriting their place with other non-repeating element.
-This way, additional memory usage can be reduced to a constant value.
+		Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last (if the repetition is more than two).
+The idea behind the algorithm is to use two pointers to delete repetitions by overwriting their place with other non-repeating element.
+In this way, additional memory usage can be reduced to a constant value.
 The algorithm makes one pass through the array.
@@
 
-		At the stage of splitting the initial problem, the set of points is divided into left and right parts of equal size.
-Since a array-like data structure is used to store the points, this operations can be completed in $O(1)$ using the formula below:
+		At the stage of splitting the initial problem, the current set of points is divided into left and right parts of equal size.
+Since a list is used to store the points, this operations can be completed in $O(1)$ using the formula below:
 
@@
 
-		For the base case, the set of points can have $2$ or $3$ elements.
-In the first case the highest of two points forms the upper part of the hull, and the lower - the lower part.
+		For the base case, the set of points can have $2$ or $3$ elements. In the first case the highest of two points forms the upper part of the hull, and the lower - the lower part.
 		To consider the base case of $3$ points, we introduce an additional notion of the tangent slope given by two points on the plane.
@@
 
-		In \cite{overmars} an algorithm for merging two convex hulls is described.
-The idea of this algorithm is to maintain the hull in two concatenated queues.
+		\cite{overmars} provides an algorithm for merging two convex hulls.
+The essence of the algorithm is to maintain the hull with the help of two concatenated queues.
 The hull is divided into two parts.
-In this article it is divided into the upper and the lower sub-hulls.
+In this article, the separation occurs from top to bottom.
 Then, using the two-pointer technique and the cases described in \cite{overmars}, the proper tangent line is searched.
-It remains to split the two queues at the found vertices that form the tangent and to merge the remaining parts.
+It remains to split the two queues at the 2 found vertices that form the tangent and to merge the remaining parts.
 An example of performing such a procedure is shown in Fig.
@@
 		It remains to consider the corner cases that arise when performing the merging.
-The first of these cases is related to the ambiguity of the position of the utmost points in the described representation.
+The first of these cases is related to the ambiguity of the position of the utmost points in the described representation of the convex hull.
 The leftmost point of the left hull and the rightmost point of the right hull must belong to the upper parts of the view before finding the tangent line, because otherwise such tangent may be found incorrectly.
@@
 
-		To avoid such a situation, it is necessary to move the indicated points to the upper sub-hulls before merging them.
+		To avoid such a situation, it is necessary to move the indicated points from their upper parts before merging the sub-hulls.
 For the rightmost point of the left hull and the leftmost point of the right hull we have the following cases.
 Similarly to the previous argument, they must be transferred to the upper parts of the hulls.
-And after merging these points must be transferred to the lower parts of the hull, if they do not belong to the resulting upper part of the final hull.
+And after merging these points must be transferred to the lower parts of the hull, if they do not belong to the created upper part of the final hull.
 Otherwise, the formed hull may be incorrect.
@@
 Then searching for the left and right pivoting vertices in the concatenable queue is performed.
-After that, the queue is split over the found vertices.
-Fig.
-\ref{fig:correct_convex_hull} shows correct convex hull.
+After that, the queue is splits over the found vertices.
+		Fig. \ref{fig:correct_convex_hull} shows correct convex hull.
 
@@
 The construction of such an object requires the combination of an algorithmic database together with the necessary data structures.
-In fact, it is needed to create an interface of generic algorithm based on ``divide-and-conquer'' strategy, which will then be used on a specific input data.
+In fact, it is necessary to create an interface of generic algorithm based on ``divide-and-conquer'' strategy, which will then be used on a specific set of input data.
 
@@
 		Each of these components will represent a function in the future interface.
-Here there is a clear separation between the input type for the algorithm and the type of the result it returns.
+Here there is a clear separation between the input type for the algorithm and the type of result it returns.
 These two types should be parameters of the algorithm model.
@@
 		A large number of computational geometry algorithms, such as computing minimal spanning tree, the Delaunay triangulation, the Voronoi diagram and the convex hull accept the list of points.
-However, it would be wrong to limit the input type in the algorithm interface to a list of points.
-The reason for this is the fact that some algorithms can use the results of other algorithms as input data.
+However, would be wrong limit the input type in the algorithm interface to a list of points.
+The reason for this is that some algorithms can use the results of other algorithms as input data.
 A well known example is the construction of a Delaunay triangulation based on the Voronoi diagram maintained in a special data structure.
@@
 			Recursive ascent and merging parts of the convex hull $O(\log n)$.
-				\begin{itemize}
+			\begin{enumerate}
 				\item
@@
 				Normalization of the obtained lower part $O(\log n)$.
-				\end{itemize}
-			\end{itemize}
+			\end{enumerate}
+		\end{enumerate}
 
@@
 \subsection{Performance}
-		A number of algorithm performance measurements were performed for different input sizes and the average number of recursive tasks per thread. The results are shown on the Fig. \ref{fig:performance}.
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.5\textwidth, height=0.3\textheight]{performance}}
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+% ----------------------------------------------- PERFORMANCE ---------------------------------------------------------------------
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+
+	A number of algorithm performance measurements were performed for different input sizes and the average number of recursive subproblems per thread.
+The results are shown on the Fig.
+\ref{fig:performance}.
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.4\textwidth,height=0.2\textheight]{performance}
 		\caption{Performance data}
@@
 
-\begin{thebibliography}{00}
-	\bibitem{ilastik} C.
-Sommer, C.
-Straehle, U.
-Köthe and F.
-A.
-Hamprecht, ``Ilastik: Interactive learning and segmentation toolkit,'' 2011 IEEE International Symposium on Biomedical Imaging: From Nano to Macro, Chicago, IL, 2011, pp..
-230-233.
-	doi: 10.1109/ISBI.2011.5872394
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{article-acm-siggraph}
 
-	\bibitem{imaris} IMARIS Software. Accessed on: 15.04.2019. [Online]. Available: https://imaris.oxinst.com
-
-	\bibitem{imagej} ImageJ: An open platform for scientific image analysis. Accessed on: 15.04.2019. [Online]. Available: https://imagej.net/Welcome
-
-	\bibitem{aggarwal} А. Aggarwal et al., ``Parallel computational geometry,'' Algorithmica 3, 1-4 (November 1988), pp.. 293-327.
-
-	\bibitem{atallah} M.J. Atallah, R. Cole, M.T. Goodrich, ``Cascading divide-and-conquer: a technique for designing parallel algorithms,'' SIAM J. Comput. 18, 1989, pp.. 499-532.
-
-	\bibitem{cole} R.
-Cole, M.T.
-Goodrich, ``Optimal parallel algorithms for polygon and point-set problems,'' In Proceedings of the fourth annual symposium on Computational geometry (SCG '88), ACM, New York, NY, USA, pp..
-201-210.
-
-	\bibitem{amato} N.M.
-Amato, M.T.
-Goodrich and E.A.
-Ramos, ``Parallel algorithms for higher-dimensional convex hulls,'' Proceedings 35th Annual Symposium on Foundations of Computer Science, Santa Fe, NM, USA, 1994, pp..
-683-694.
-
-	\bibitem{chen} D.Z. Chen, ``Efficient geometric algorithms on the EREW PRAM,'' in IEEE Transactions on Parallel and Distributed Systems, vol. 6, no. 1, pp.. 41-47, Jan. 1995.
-	doi: 10.1109/71.363412
-
-	\bibitem{berkman} O. Berkman, B. Schieber, U. Vishkin, ``A fast parallel algorithm for finding the convex hull of a sorted point set,'' Internat. J. Comput. Geom. Appl. 6, 1996, pp.. 231-242.
-
-	\bibitem{goodman} J.E. Goodman and J. O'Rourke, editors,  Handbook of Discrete and Computational Geometry, CRC Press LLC, Boca Raton, FL, 2004.
-
-	\bibitem{akl} Selim G. Akl and Kelly A. Lyons, Parallel Computational Geometry, Englewood Cliffs: Prentice-Hall, 1993.
-
-	\bibitem{jaja} J. JaJa, An Introduction to Parallel Algorithms, Amsterdam: Addison-Wesley, 1992.
-
-	\bibitem{leeuwen} J. Van Leeuwen, Handbook of Theoretical Computer Science, Amsterdam: Elsevier/The MIT Press, 1990.
-
-	\bibitem{reif} J.H. Reif, Synthesis of Parallel Algorithms, San Mateo: Morgan Kaufmann, 1993.
-
-	\bibitem{tereshchenko} V.
-N.
-Tereshchenko, A.
-V.
-Anisimov, Recursion and parallel algorithms in geometric modeling problems, Journal: Cybernetics and Systems Analysis: Vol.
-46, N 2 (2010), pp..
-173-184.
-
-	\bibitem{overmars} Mark H. Overmars, Jan van Leeuwen, ``Maintenance of configurations in the plane,'' Journal of Computer and System Sciences, Volume 23, Issue 2, 1981, pp.. 166-204.
-
-	\bibitem{aho} Alfred V. Aho and John E. Hopcroft, The Design and Analysis of Computer Algorithms, 1st ed. Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA, 1974.
-\end{thebibliography}
 \end{document}
+\endinput

### 2020-01-08 eurocg20 EA/article-eurocg20-ea.tex
euroCG 2020 & extended abstract

--- 2019-12-23 SoCG/article-SoCG.tex
@@
-\documentclass[a4paper,UKenglish,cleveref, autoref]{socg-lipics-v2019}
-%This is a template for producing LIPIcs articles. 
-%See lipics-manual.pdf for further information.
-%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
-%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
-%for section-numbered lemmas etc., use "numberwithinsect"
-%for enabling cleveref support, use "cleveref"
-%for enabling cleveref support, use "autoref"
-%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
+% for section-numbered lemmas etc., use "numberwithinsect"
+\documentclass[a4paper,english,numberwithinsect,notab]{eurocg20-submission}
 
-\bibliographystyle{plainurl}% the mandatory bibstyle
+% the recommended bibstyle
+\bibliographystyle{plainurl}
 \graphicspath{{images/}}
@@
 
+% -------------------------------------------------------------------
+\usepackage{microtype} % if unwanted, comment out
+
+% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand\polylog{{\rm polylog}}
+
+% Author metadata::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \title{Unified data structures for solving optimally a set of interrelated computational geometry problems}
@@
 
-\author{Vasyl Tereshchenko}{
-	Faculty of computer science and cybernetics, Taras Shevchenko National University of Kyiv, Ukraine}
-{vtereshch@gmail.com}{}{}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
-Please provide at least the name of the affiliation and the country.
-The full address is optional
-%\footnote{}
-\author{Semen Chudakov}{Faculty of computer science and cybernetics, Taras Shevchenko National University of Kyiv, Ukraine}
-{semen.chudakov7@gmail.com}{}{}
+\author[1]{Vasyl Tereshchenko}
+\author[2]{Semen Chudakov}
+\affil[1]{
+	Faculty of computer science and cybernetics, Taras Shevchenko National University of Kyiv, Ukraine\\
+  \texttt{vtereshch@gmail.com}}
+\affil[2]{Faculty of computer science and cybernetics, Taras Shevchenko National University of Kyiv, Ukraine\\
+  \texttt{semen.chudakov7@gmail.com}}
+%mandatory. First: Use abbreviated first/middle names.
+%Second (only in severe cases): Use first author plus 'et. al.'
+\authorrunning{V. Tereshchenko and S. Chudakov}
+\ArticleNo{100}
 
-\authorrunning{V. Tereshchenko and S. Chudakov}%TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
-
-\Copyright{Vasyl Tereshchenko and Semen Chudakov}%TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\ccsdesc[500]{Theory of computation~Computational geometry}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
-
-\keywords{Algorithmic tools,   Computational geometry, Interrelated problems set, Unified algorithmic environment, Concatenable queue}%TODO mandatory; please add comma-separated list of keywords
-
-\category{}%optional, e.g. invited paper
-
-\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversion{A full version of the paper is available at \url{...}.}
-
-\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-
-%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
-Please enter author specific funding statements as fifth argument of the \author macro.
-
-\acknowledgements{}%optional
-
-%\nolinenumbers %uncomment to disable line numbering
-
-%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{}
-\EventNoEds{2}
-\EventLongTitle{36th International Symposium on Computational Geometry (SoCG 2020)}
-\EventShortTitle{SoCG 2020}
-\EventAcronym{SoCG}
-\EventYear{2020}
-\EventDate{June  23--26, 2020}
-\EventLocation{Zürich, Switzerland}
-\EventLogo{socg-logo}
-\SeriesVolume{}
-\ArticleNo{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%TODO mandatory: add short abstract of the document
 \begin{abstract}
-	The paper is devoted to the development and  of an efficient algorithmic model for solving a set of interrelated computational geometry problems.
+	This paper is devoted to the development and  of an efficient algorithmic model for solving a set of interrelated computational geometry problems.
 To do this, a unified algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources.
@@
 Furthermore we offer a way to execute the algorithms both sequentially and in parallel.
-	In the future the algorithmic environment can be improved to support other computational models with similar properties for solving problems.
-As an example, the Voronoi diagram or the Delaunay triangulation can be considered.
 \end{abstract}
@@
 	Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of problems.
-The core of this set are problems of computational geometry and computer graphics.
 To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time.
-Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy.
+Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package do not result in desirable efficiency and accuracy.
 It is worth noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems such as in \cite{aggarwal,atallah,cole,amato,chen,berkman,goodman,akl,jaja,leeuwen,reif}.
@@
 
-	In this article we first describe how the convex hull algorithm for a static set of points is decomposed into separate stages and incorporated into our unified algorithmic environment model (UAEM).
+	%In this article we first describe how the convex hull algorithm for a static set of points is decomposed into separate stages and incorporated into our unified algorithmic environment model (UAEM).
 Then we provide detailed explanation on how the concatenable queue which is used in the algorithm is implemented.
@@
 
-	Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last one (if there are more than two repetitions).
+	Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last one.
 The idea behind the algorithm is to use two pointers technique to delete repetitions by overwriting their place with other non-repeating element.
-This way, additional memory usage can be reduced to a constant value.
-The algorithm makes one pass through the array.
-At each step, a constant amount of work is performed to decide whether to delete the current item.
+At each step, constant work is performed to decide whether to overwrite the current item.
 Given this, the complexity of the above algorithm is $O(n)$.
 
-	To perform the preprocessing described above, it is needed to:
+	%To perform the preprocessing described above, it is needed to:
 
-	\begin{enumerate}
-		\item
-		Sort points by $y$ (if $y$ coordinates are equal, the $x$ coordinates are compared).
-		\item
-		Delete repetitions by $y$ coordinate using the described algorithm.
-		\item
-		Sort points by $x$ (if $x$ coordinates are equal, the $y$ coordinates are compared).
-		\item
-		Delete repetitions by $x$ coordinate using the described algorithm.
-	\end{enumerate}
+	%\begin{enumerate}
+	%	\item
+	%	Sort points by $y$ (if $y$ coordinates are equal, the $x$ coordinates are compared).
+	%	\item
+	%	Delete repetitions by $y$ coordinate using the described algorithm.
+	%	\item
+	%	Sort points by $x$ (if $x$ coordinates are equal, the $y$ coordinates are compared).
+	%	\item
+	%	Delete repetitions by $x$ coordinate using the described algorithm.
+	%\end{enumerate}
 
-	In the result we get a set of points for which we can apply the recursive convex hull algorithm.
+	%Finally, we get a set of points for which we can apply the recursive convex hull algorithm.
 
@@
 	At the stage of splitting the initial problem, the set of points is divided into left and right parts of equal size.
-Since a array-like data structure is used to store the points, this operations can be completed in $O(1)$ using the formula below:
+Since a array-like data structure is used to store the points, this operations can be done in $O(1)$ by computing middle positiong in the array.
 
-	\begin{equation}
-		M_{i,j}=\frac{i+j}{2}
-	\end{equation}
-	The recursion stops when there are no more than $3$ points in the set.
-
-	For the base case, the set of points can have $2$ or $3$ elements.
-In the first case the highest of two points forms the upper part of the hull, and the lower - the lower part.
-To consider the base case of $3$ points, we introduce an additional notion of the tangent slope given by two points on the plane.
+	%\begin{equation}
+	%	M_{i,j}=\frac{i+j}{2}
+	%\end{equation}
+	The recursion stops when there are $2$ or $3$ elements in the array.
+First case is triial.
+To consider the base case of $3$ points, we introduce a notion of the tangent slope given by two points on the plane.
 For arbitrary points $a_1, a_2$ such that $x(a_1)<x(a_2)$ slope is denoted as $\lambda$:
@@
 
-	In \cite{overmars} an algorithm for merging two convex hulls is described.
+	%In \cite{overmars} an algorithm for merging two convex hulls is described.
 The idea of this algorithm is to maintain the hull in two concatenated queues.
@@
 
-	\begin{figure}[t]
-		\centering
-		\includegraphics[width=0.8\textwidth, height=0.3\textheight]{ch_union}
-		\caption{Merging step of two hulls}
-		\label{fig:ch_union}
-	\end{figure}
+	%\begin{figure}[t]
+	%	\centering
+	%	\includegraphics[width=0.8\textwidth, height=0.3\textheight]{ch_union}
+	%	\caption{Merging step of two hulls}
+	%	\label{fig:ch_union}
+	%\end{figure}
 
+	In \cite{overmars} an algorithm for merging two convex hulls is described.
 It remains to consider the corner cases that arise when performing the merging.
@@
 
-	We start creating the generic interface by listing its components:
-
-	\begin{itemize}
-		\item 
-		Preprocessing.
-		\item 
-		Splitting task into sub-tasks.
-		\item 
-		Solving sub-tasks.
-		\item 
-		Merging obtained results.
-		\item 
-		Checking, if a given input data is a base case for the algorithm.
-		\item 
-		Solving the base case.
-	\end{itemize}
-
-	Each of these components will represent a function in the future interface.
-Here there is a clear separation between the input type for the algorithm and the type of the result it returns.
-These two types should be parameters of the algorithm model.
-One should also pay attention to the input and output types of functions  in the interface.
-
-	A large number of computational geometry algorithms, such as computing minimal spanning tree, the Delaunay triangulation, the Voronoi diagram and the convex hull accept the list of points.
-However, it would be wrong to limit the input type in the algorithm interface to a list of points.
-The reason for this is the fact that some algorithms can use the results of other algorithms as input data.
-A well known example is the construction of a Delaunay triangulation based on the Voronoi diagram maintained in a special data structure.
-
-	Listing \ref{lst:algmodel} shows the constructed algorithm model. $IT$ denotes the input type and $OT$ - output type.
+	The proposed generic interface for the ``divide-and-conquer'' algorithm is described on the Listing \ref{lst:algmodel}.
 
@@
 	\end{lstlisting}
+
+	%We start creating the generic interface by listing its components:
+
+	%\begin{itemize}
+	%	\item 
+	%	Preprocessing.
+	%	\item 
+	%	Splitting task into sub-tasks.
+	%	\item 
+	%	Solving sub-tasks.
+	%	\item 
+	%	Merging obtained results.
+	%	\item 
+	%	Checking, if a given input data is a base case for the algorithm.
+	%	\item 
+	%	Solving the base case.
+	%\end{itemize}
+
+	%Each of these components will represent a function in the future interface.
+Here there is a clear separation between the input type for the algorithm and the type of the result it returns.
+These two types should be parameters of the algorithm model.
+One should also pay attention to the input and output types of functions  in the interface.
+
+	%A large number of computational geometry algorithms, such as computing minimal spanning tree, the Delaunay triangulation, the Voronoi diagram and the convex hull accept the list of points.
+However, it would be wrong to limit the input type in the algorithm interface to a list of points.
+The reason for this is the fact that some algorithms can use the results of other algorithms as input data.
+A well known example is the construction of a Delaunay triangulation based on the Voronoi diagram maintained in a special data structure.
+
+	%Listing \ref{lst:algmodel} shows the constructed algorithm model. $IT$ denotes the input type and $OT$ - output type.
+
+%	\begin{lstlisting}[caption={Algorithm model based on the ``divide-and-conquer'' principle},label={lst:algmodel},captionpos=t,float,abovecaptionskip=-\medskipamount]
+%interface DaCAlgorithm[IT, OT]:
+%    boolean isBaseCase(IT input)
+%    int inputSize(IT input)
+
+%    OT solveBaseCase(IT input)
+%    IT preprocess(IT input)
+
+%    OT merge(OT first, OT second)
+%    Pair[IT, IT] divide(IT input)
+%	\end{lstlisting}
 
@@
 	As shown in \cite{overmars}, the concatenable queue is the key data structure for the algorithm described above and is therefore the basis for the UAEM.
-Now we will focus on how to efficiently implement it in our algorithmic environment.
 
-	Concatenable queue is an Abstract Data Type, that supports following operations:
+	Concatenable queue is an Abstract Data Type. Its operations are shown on Table \ref{table:cqueue-operations} together with theirs time complexities in our implementation:
 
-	\begin{itemize}
-		\item
-		ADD\_ELEMENT();
-		\item
-		REMOVE\_ELEMENT();
-		\item
-		GET\_MINIMUM();
-		\item
-		CONTAINS();
-		\item
-		SPLIT();
-		\item
-		MERGE().
-	\end{itemize}
+	\begin{table}[htbp]
+		\caption{Concatebable queue operations}
+		\label{table:cqueue-operations}
+		\begin{center}
+			\begin{tabular}{|c|c|}
+				\hline
+				\textbf{Operation} & \textbf{Complexity} \\
+				\hline
+				ADD\_ELEMENT() & $O(\log n)$ \\
+				\hline
+				REMOVE\_ELEMENT() & $O(\log n)$ \\
+				\hline
+				GET\_MINIMUM() & $O(\log n)$ \\
+				\hline
+				CONTAINS() & $O(\log n)$ \\
+				\hline
+				SPLIT() & $O(\log^2 n)$ \\
+				\hline
+				MERGE() & $O(\log n)$ \\
+				\hline
+			\end{tabular} 
+		\end{center}
+	\end{table}
 
-	By default the elements in a concatenable queue are kept i a certain predefined order \cite[pp..~155-157]{aho}.
+%	\begin{itemize}
+%		\item
+%		ADD\_ELEMENT();
+%		\item
+%		REMOVE\_ELEMENT();
+%		\item
+%		GET\_MINIMUM();
+%		\item
+%		CONTAINS();
+%		\item
+%		SPLIT();
+%		\item
+%		MERGE().
+%	\end{itemize}
 
-	In this article the concatenable queue is implemented as a binary  $B+$ tree.
+	%By default the elements in a concatenable queue are kept i a certain predefined order \cite[pp..~155-157]{aho}.
+
+	%In this article the concatenable queue is implemented as a binary  $B+$ tree.
 Its vertices are divided into non-leaf and leaf ones.
@@
 For the leaf vertices those pointers point to the left and right neighboring leaf vertices or $null$ if the vertex is utmost in the tree.
-	Additionally every vertex keeps a pointer to a vertex with the largest element in its left sub-tree, which  allows to perform binary search \cite[pp..~155-157]{aho}.
+	%Additionally every vertex keeps a pointer to a vertex with the largest element in its left sub-tree, which  allows to perform binary search \cite[pp..~155-157]{aho}.
 The height of each vertex is kept for the balancing during the split and merge operations.
@@
 
-	From now we will go into details on how this data structure is implemented.
+	%From now we will go into details on how this data structure is implemented.
 
-	The contains operations is pretty straightforward and uses binary search over the tree so its complexity is $O(\log n)$, where $n$ hereafter denotes the numbers of vertices in the queue.
+	%The contains operations is pretty straightforward and uses binary search over the tree so its complexity is $O(\log n)$, where $n$ hereafter denotes the numbers of vertices in the queue.
 
-	Algorithm of inserting an element in a queue looks like as follows.
+	%Algorithm of inserting an element in a queue looks like as follows.
 First, the position of a new vertex is searched.
@@
 
-	\begin{figure}[htbp]
-		\begin{lstlisting}[caption={Queue insertion algorithm},label={lst:insert-alg},captionpos=b]
-Node insert(Node node, int e):
-    Node result = nil
-    if e <= node.leftSubtreeMax.data:
-        if node.isLeaf:
-            if e == node.data:
-                node.data = e
-            else:
-                Node createdLeaf = createLeafBetween(e, node.left, node)
-                result = Node(createdLeaf, createdLeaf, node)
-        else:
-            node.left = insert(node.left, e)
-    else:
-        if node.isLeaf:
-            Node createdLeaf = createLeafBetween(e, node, node.right)
-            result = Node(node, node, createdLeaf)
-        else:
-            node.right = insert(node.right, e)
+	%The algorithm of inserting an element in a queue is described on the Listing \ref{lst:insert-alg}.
 
-    if result == nil:
-        result = node
+%	\begin{figure}[htbp]
+%		\begin{lstlisting}[caption={Queue insertion algorithm},label={lst:insert-alg},captionpos=b]
+%Node insert(Node node, int e):
+%  Node result = nil
+%    if e <= node.leftSubtreeMax.data:
+%        if node.isLeaf:
+%            if e == node.data:
+%                node.data = e
+%            else:
+%                Node createdLeaf = createLeafBetween(e, node.left, node)
+%                result = Node(createdLeaf, createdLeaf, node)
+%        else:
+%            node.left = insert(node.left, e)
+%    else:
+%        if node.isLeaf:
+%            Node createdLeaf = createLeafBetween(e, node, node.right)
+%            result = Node(node, node, createdLeaf)
+%        else:
+%            node.right = insert(node.right, e)
+%
+%    if result == nil:
+%        result = node
+%
+%    updateHeight(result)
+%    return result
+%
+%		\end{lstlisting}
+%	\end{figure}
 
-    updateHeight(result)
-    return result
+%	Here the \textit{updateHeight} subroutine updates the height value for a given vertex, the \textit{createLeafBetween} subroutine breaks the connection between adjacent vertices ot insert a new one.
 
-		\end{lstlisting}
-	\end{figure}
-
-	Here the \textit{updateHeight} subroutine updates the height value for a given vertex, the \textit{createLeafBetween} subroutine breaks the connection between adjacent vertices ot insert a new one.
-
-	On the first step we find out if $leftSubtreeMax$ point to an element with greater value than the value to be inserted $e$.
+%	On the first step we find out if $leftSubtreeMax$ point to an element with greater value than the value to be inserted $e$.
 If so, then, if current element is a leaf, a new element is created between the current element and its left neighbor.
@@
 
-	Since on every step we perform a constant amount of work, the complexity of the procedure is $O(h)=O(\log n)$, where $h$ hereafter denotes the height of the tree.
+%	Since on every recursion step we perform a constant amount of work, the complexity of the procedure is $O(h)=O(\log n)$, where $h$ hereafter denotes the height of the tree.
 The operation of removing an element from the queue is performed analogously.
 
-	The split operation is a bit more complex.
-As an input the procedure takes current element and value based on which the split is performed.
+%	The split operation is a bit more complex. 
+%	As an input the procedure takes current element and value based on which the split is performed.
 As a result two independent queues are formed.
 The value, by which the split has been performed, belongs to the left sub-queue.
-The procedure is formally described on the Listing \ref{lst:split-alg}.
+%	Its algorithm is described on the Listing \ref{lst:split-alg}.
 
-	\begin{lstlisting}[caption={Queue split algorithm},label={lst:split-alg},captionpos=b]
-split(Node node, int e, ConcatenableQueue leftQueue, ConcatenableQueue rightQueue):
-    if node.isLeaf
-        leftQueue.root = node
-        leftQueue.maxNode = node
-        rightQueue.minNode = node.right
-        cut(node)
-    else:
-        if e == node.leftSubtreeMax.data:
-            leftQueue.root = node.left
-            leftQueue.maxNode = node.leftSubtreeMax
+%	\begin{lstlisting}[caption={Queue split algorithm},label={lst:split-alg},captionpos=b]
+%split(Node node, int e, ConcatenableQueue leftQueue, ConcatenableQueue rightQueue):
+%    if node.isLeaf
+%        leftQueue.root = node
+%        leftQueue.maxNode = node
+%        rightQueue.minNode = node.right
+%        cut(node)
+%    else:
+%        if e == node.leftSubtreeMax.data:
+%            leftQueue.root = node.left
+%            leftQueue.maxNode = node.leftSubtreeMax
+%
+%            rightQueue.root = node.right
+%            rightQueue.minNode = node.leftSubtreeMax.right
+%
+%            cut(node.leftSubtreeMax)
+%        else if e < node.leftSubtreeMax.data:
+%            split(node.left, e, leftQueue, rightQueue)
+%            rightQueue.root = concatenateNodes(rightQueue.root, node.right, node.leftSubtreeMax)
+%        else:
+%            split(node.right, e, leftQueue, rightQueue)
+%            leftQueue.root = concatenateNodes(node.left,  leftQueue.root, node.leftSubtreeMax)
+%	\end{lstlisting}
 
-            rightQueue.root = node.right
-            rightQueue.minNode = node.leftSubtreeMax.right
-
-            cut(node.leftSubtreeMax)
-        else if e < node.leftSubtreeMax.data:
-            split(node.left, e, leftQueue, rightQueue)
-            rightQueue.root = concatenateNodes(rightQueue.root, node.right, node.leftSubtreeMax)
-        else:
-            split(node.right, e, leftQueue, rightQueue)
-            leftQueue.root = concatenateNodes(node.left,  leftQueue.root, node.leftSubtreeMax)
-	\end{lstlisting}
-
-	Here the $concatenateNodes$ procedure is used.
+%	Here the $concatenateNodes$ procedure is used.
 It performs concatenation of two arbitrary elements and uses theirs heights to balance the resulting queue.
 The $cut$ procedure breaks connection between two adjacent leaf elements in a queue and therefore is trivial.
-On the first step in the $split$ operation we check, is the current element is a leaf.
+%	On the first step in the $split$ operation we check, is the current element is a leaf.
 Is so, its connection are broken and the value of $maxNode$ is updated for the left queue as well as the value of $minNode$ for the right queue.
@@
 
-	The algorithm of the $concatenateNodes$ procedure is described on the Listing \ref{lst:concatenate-als}.
+%	The algorithm of the $concatenateNodes$ procedure is described on the Listing \ref{lst:concatenate-als}.
 
-	\begin{lstlisting}[caption={Merging two queues},label={lst:concatenate-als},captionpos=b]
-Node concatenateNodes(Node leftNode, Node rightNode, Node leftSubtreeMax) {
-    if leftNode == nil:
-        return rightNode
-    else if rightNode == nil:
-        return leftNode
-    else if leftNode.height == rightNode.height:
-        Node result = Node(leftSubtreeMax, leftNode, rightNode)
-        updateHeight(result)
-        return result
-    else if leftNode.height < rightNode.height:
-        rightNode.left = concatenateNodes(leftNode, rightNode.left, leftSubtreeMax)
-        updateHeight(rightNode)
-        return rightNode
-    else:
-        leftNode.right = concatenateNodes(leftNode.right, rightNode, leftSubtreeMax)
-        updateHeight(leftNode)
-        return leftNode
-	\end{lstlisting}
+%	\begin{lstlisting}[caption={Merging two queues},label={lst:concatenate-als},captionpos=b]
+%Node concatenateNodes(Node leftNode, Node rightNode, Node leftSubtreeMax) {
+%    if leftNode == nil:
+%        return rightNode
+%    else if rightNode == nil:
+%        return leftNode
+%    else if leftNode.height == rightNode.height:
+%        Node result = Node(leftSubtreeMax, leftNode, rightNode)
+%        updateHeight(result)
+%        return result
+%    else if leftNode.height < rightNode.height:
+%        rightNode.left = concatenateNodes(leftNode, rightNode.left, leftSubtreeMax)
+%        updateHeight(rightNode)
+%        return rightNode
+%    else:
+%        leftNode.right = concatenateNodes(leftNode.right, rightNode, leftSubtreeMax)
+%        updateHeight(leftNode)
+%        return leftNode
+%	\end{lstlisting}
 
-	First, we consider corner cases where one of the elements is $null$.
+%	First, we consider corner cases where one of the elements is $null$.
 This is needed to ensure correctness of the recursion.
@@
 
-	We begin analyzing the complexity of the $split$ procedure by determining the complexity of the $concatenateNodes$ procedure.
+%	We begin analyzing the complexity of the $split$ procedure by determining the complexity of the $concatenateNodes$ procedure.
 At each iteration, a step is performed either to the left son of the current element or to the right one.
@@
 
-	The $split$ procedure uses the $concatenateNodes$ function as a subroutine.
+%	The $split$ procedure uses the $concatenateNodes$ function as a subroutine.
 The complexity of a $split$ call is equal to the complexity of $concatenateNodes$.
@@
 
-	The merge operation of two queues is reduced to the clamping of their root vertices by the $concatenateNodes$ procedure, so its complexity is $O(\log n)$.
+%	The merge operation of two queues is reduced to the clamping of their root vertices by the $concatenateNodes$ procedure, so its complexity is $O(\log n)$.
 
@@
 			Recursive ascent and merging parts of the convex hull $O(\log n)$.
-			\begin{alphaenumerate}
+			\begin{enumerate}
 				\item
@@
 				Normalization of the obtained lower part $O(\log n)$.
-			\end{alphaenumerate}
+			\end{enumerate}
 		\end{enumerate}
@@
 
-\bibliography{article-SoCG}
+\bibliography{article-eurocg20-ea}
 \end{document}

### 2020-01-08 eurocg20/article-eurocg20.tex
euroCG 2020 & extended abstract

--- 2019-12-23 SoCG/article-SoCG.tex
@@
 To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time.
-Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy.
+Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package do not result in desirable efficiency and accuracy.
 It is worth noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems such as in \cite{aggarwal,atallah,cole,amato,chen,berkman,goodman,akl,jaja,leeuwen,reif}.
@@
 
-\bibliography{article-SoCG}
+\bibliography{article-eurocg20}
 \end{document}

### 2020-01-08 templates/eurocg20/eurocg20_example.tex
euroCG 2020 & extended abstract

% for section-numbered lemmas etc., use "numberwithinsect"
\documentclass[a4paper,english,numberwithinsect]{eurocg20-submission}

% the recommended bibstyle
\bibliographystyle{plainurl}

% -------------------------------------------------------------------
\usepackage{microtype} % if unwanted, comment out

%helpful if your graphic files are in another directory
%\graphicspath{{./graphics/}}

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\polylog{{\rm polylog}}

% Author metadata::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{An Example Contribution for EuroCG 2020\footnote{Supported by
our friends.}}
%optional, in case that the title is too long;
%the running title should fit into the top page column
\titlerunning{A Contribution to EuroCG 2020}

\author[1]{Antonio Example}
\author[2]{Sylvia Veryknown}
\affil[1]{Important University\\
  \texttt{aexample@cs.important.de}}
\affil[2]{Department of Mathematics and Computer
        Science, University of Somewhere\\
  \texttt{sveryknown@math.somewhere.nl}}
%mandatory. First: Use abbreviated first/middle names.
%Second (only in severe cases): Use first author plus 'et. al.'
\authorrunning{A. Example and S. Veryknown}
\ArticleNo{100}

% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
  This example file was adapted from Wolfang Mulzer's example file for EuroCG
  2018, which in turn was adapted from Bettina Speckmann's example file for
  EuroCG 2005. The current style uses two style-files, \texttt{eurocg20.cls}
  and \texttt{eurocg20-submission.cls}. The former was adapted from the
  LIPIcs-style, with kind permission from Dagstuhl publishing. The latter file
  provides proper line numbering and is adapted from the style file developed
  for SoCG 2019 by Michael Hoffmann. Thanks again to all of these people.

  Here you should probably write a concise, informative, and exciting abstract
  for your paper.
\end{abstract}

\section{Introduction}

\subsection{Problem Statement and Solution}

\subsubsection{Problem Setup}

We consider only the two-dimensional setting.
We assume \dots

\subparagraph{Precise Problem Formulation.}

Describe your problem as clearly as possibly, instead of the usual \dots

\begin{conj}
Could it really be like this?
\end{conj}
\begin{obs}
Probably not \dots
\end{obs}

\subsection{Basic Definitions}
\begin{definition}
Some things are just not definable \dots
\end{definition}

\subsection{Related Results from the Literature}

We improve upon the following well-known algorithm of Grace of
Florence~\cite{g-atpwog-2006} in the following way: \dots

\section{The New Algorithm}

%\section{Correctness}

\section{Complexity Analysis}

\begin{theorem}
This is the most important theorem.
\end{theorem}
\begin{proof}
It even comes with a proof \dots
\end{proof}

We would like to remind you how cute the logo of the Canadian
Conference on Computational Geometry 2003 was,
see Figure~\ref{fig:logo}.

\begin{figure}[ht]
  \centering
  \includegraphics[scale=0.5]{example_figure}
  \caption{This was the logo of CCCG 2003.}
  \label{fig:logo}
\end{figure}

There should be some more text explaining 
research results in some additional sections, 
but since this is only an example file \dots

An enumeration:
\begin{itemize}
\item a
\begin{itemize}
  \item 0
  \item 1
\end{itemize}
\item b
\end{itemize}

\begin{lemma}
  % Some mathematics, not entirely convincing.
  The following formula holds
  for all integers $n>0$\textup:
\begin{equation}
  \label{eq:sum-formula}
  \sum_{i=1}^{n} i = \frac{n(n+1)}{2}
\end{equation}
\end{lemma}
\begin{proof} (Not entirely convincing)
Let \(T(n) := \frac{n(n-1)}{2}\) denote the claimed formula.
\begin{align}
  T(n) - T(n-1) &= \frac{n(n+1)}{2} - \frac{(n-1)n}{2}
\nonumber
  \\
                &= \frac{n(n+1) - (n-1)n}{2}
\nonumber
  \\
                &= \frac{n^2+n - (n^2+n)}{2} = \frac {2n}{2} = n
\label{eq:diff}                  
\end{align}
The induction basis $T(0)=\frac{0\cdot 1}2 = 0$, together with~\eqref{eq:diff},
establishes~\eqref{eq:sum-formula}.
\end{proof}

\begin{lemma}
  And then we also found this lemma, which we state without proof.
  \qed
\end{lemma}

\section{Conclusion}

What we did is amazing and improves everything that was there before,
in particular when compared to~\cite{g-atpwog-2006}.

\subparagraph*{Acknowledgments.} We thank the organizers for
the tasty cookies.

\bibliography{eurocg20_example}

\end{document}

### 2020-02-27 WSCG20/article-wscg20.tex
iadis, spaa20, WSCG20 & calender

--- 2019-12-23 acm siggraph/article-acm-siggraph.tex
@@
-%%
-%% This is file `sample-sigconf.tex',
-%% generated with the docstrip utility.
-%%
-%% The original source files were:
-%%
-%% samples.dtx  (with options: `sigconf')
-%% 
-%% IMPORTANT NOTICE:
-%% 
-%% For the copyright see the source file.
-%% 
-%% Any modified versions of this file must be renamed
-%% with new filenames distinct from sample-sigconf.tex.
-%% 
-%% For distribution of the original source see the terms
-%% for copying and modification in the file samples.dtx.
-%% 
-%% This generated file may be distributed as long as the
-%% original source files, as listed above, are part of the
-%% same distribution. (The sources need not necessarily be
-%% in the same archive or directory.)
-%%
-%% The first command in your LaTeX source must be the \documentclass command.
-\documentclass[sigconf]{acmart}
+% WSCG sample document 
+%
+% based on Gabriel Zachmann's sample
+% http://zach.in.tu-clausthal.de/latex/
+%
+% modified Apr 2012 to match WSCG Word template
+%
+\documentclass[twoside,twocolumn,10pt]{article}
+%\documentclass[twoside,twocolumn,draft]{article}
 
+%  for debugging
+%\tracingall%\tracingonline=0
+%\tracingparagraphs
+%\tracingpages
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                             Packages
+
+\usepackage{wscg}
+\RequirePackage{ifpdf}
+\ifpdf
+ \RequirePackage[pdftex]{graphicx}
+ \RequirePackage[pdftex]{color}
+\else
+ \RequirePackage[dvips,draft]{graphicx}
+ \RequirePackage[dvips]{color}
+\fi
+\usepackage{amsthm}
+\usepackage{nopageno}       % no page numbers at all; uncomment for final version
 \usepackage{listings}
@@
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
+%\usepackage[english]{babel}     % default = english
+%\usepackage{mypicture}      % loads graphicx.sty, color.sty, eepic.sty
+%\usepackage{array}          % better tabular's & arrays, plus math tabular's
+%\usepackage{tabularx}      % for selfadjusting p-columns
+%\usepackage{theorem}
+%\setlength{\extrarowheight}{1ex}   % additional space between rows
+%\usepackage{booktabs}      % typographically much better
+%\usepackage{mdwlist}        % for compacted lists, and more versatile lists
+%\usepackage[intlimits]{amsmath} % more math stuff, see texdoc amsldoc
+%\usepackage{mymath}         % own commands, loads amssymb & array.sty
+%\usepackage{hyphenat}      % hyphenatable -, /, etc.
+%\usepackage[sort&compress]{natbib}% better \cite commands, more flexible
+%\usepackage[sort&compress,super]{natbib} % better \cite commands, more flexible
+%\newcommand{\citenumfont}[1]{\textit{#1}}
 
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                Title
 
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{10.1145/1122445.1122456}
+\title{Application of concatenable queue for parallel computational geometry algorithms}
 
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[I3D’19]{ACM SIGGRAPH Symposium on
-Interactive 3D Graphics and Games}{May 05--07, 2020}{San Francisco, USA}
-%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
- % June 03--05, 2018, Woodstock, NY}
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-
-%%
-%% end of the preamble, start of the body of the document source.
-\begin{document}
-
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
-\title{Application of concatenable queue for creation unified data structures in 3-D simulation}
-
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
-%% used to denote shared contribution to the research.
-
-%\author{Vasyl Tereshchenko}
-%\authornote{Both authors contributed equally to this research.}
-%\email{vtereshch@gmail.com}
-%\orcid{0000-0002-0139-6049}
-%\author{Semen Chudakov}
-%\authornotemark[1]
-%\email{semen.chudakov7@gmail.com}
-%\affiliation{%
-%  \institution{Taras Shevchenko National University of Kyiv}
-%  \streetaddress{P.O. Box 01601}
-%  \city{Kyiv}
-%  \state{}
-%  \postcode{}
+%\author{
+%\parbox{0.25\textwidth}{\centering
+%Vasyl Tereshchenko\\[1mm]
+%Taras Shevchenko National University of Kyiv\\
+%Kyiv, Ukraine\\[1mm]
+%vtereshch@gmail.com
+%}
+%\hspace{0.05\textwidth}
+%\parbox{0.25\textwidth}{\centering
+%Semen Chudakov\\[1mm]
+%Taras Shevchenko National University of Kyiv\\
+%Kyiv, Ukraine\\[1mm]
+%semen.chudakov7@gmail.com
+%}
 %}
 
-%\author{Lars Th{\o}rv{\"a}ld}
-%\affiliation{%
-%  \institution{The Th{\o}rv{\"a}ld Group}
-%  \streetaddress{1 Th{\o}rv{\"a}ld Circle}
-%  \city{Hekla}
-%  \country{Iceland}}
-%\email{larst@affiliation.org}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                          Hyperref
 
-%\author{Valerie B\'eranger}
-%\affiliation{%
-%  \institution{Inria Paris-Rocquencourt}
-%  \city{Rocquencourt}
-%  \country{France}
-%}
+% no hyperlinks
+\usepackage{url}
+\urlstyle{tt}
+% Donald Arsenau's fix for missing kerning of "//" and ":/"
+\makeatletter
+\def\Uslash{\mathbin{\mathchar`\/}\@ifnextchar{/}{\kern-.15em}{}}
+\g@addto@macro\UrlSpecials{\do \/ {\Uslash}}
+\def\Ucolon{\mathbin{\mathchar`:}\@ifnextchar{/}{\kern-.1em}{}}
+\g@addto@macro\UrlSpecials{\do : {\Ucolon}}
+\makeatother
 
-%\author{Aparna Patel}
-%\affiliation{%
-% \institution{Rajiv Gandhi University}
-% \streetaddress{Rono-Hills}
-% \city{Doimukh}
-% \state{Arunachal Pradesh}
-% \country{India}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                              My Commands
 
-%\author{Huifen Chan}
-%\affiliation{%
-%  \institution{Tsinghua University}
-%  \streetaddress{30 Shuangqing Rd}
-%  \city{Haidian Qu}
-%  \state{Beijing Shi}
-%  \country{China}}
+%\DeclareMathOperator{\sgn}{sgn}
+%\theorembodyfont{\upshape}
+%\theoremstyle{break}
+%\theoremheaderfont{\bfseries\normalsize}
 
-%\author{Charles Palmer}
-%\affiliation{%
-%  \institution{Palmer Research Laboratories}
-%  \streetaddress{8600 Datapoint Drive}
-%  \city{San Antonio}
-%  \state{Texas}
-%  \postcode{78229}}
-%\email{cpalmer@prl.com}
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
+\newtheorem{lemma}{Lemma}
 
-%\author{John Smith}
-%\affiliation{\institution{The Th{\o}rv{\"a}ld Group}}
-%\email{jsmith@affiliation.org}
+%\newtheorem{thrm}{Theorem}
+%\newtheorem{lem}{Lemma}
+%\newtheorem{defn}{Definition}
 
-%\author{Julius P. Kumquat}
-%\affiliation{\institution{The Kumquat Consortium}}
-%\email{jpkumquat@consortium.net}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                Document
 
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-%\renewcommand{\shortauthors}{Tereshchenko and Chudakov}
+\begin{document}
+\twocolumn[{\csname @twocolumnfalse\endcsname
+\maketitle  % full width title
 
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
 \begin{abstract}
+\noindent
 	The paper is devoted to the development and  of an efficient algorithmic model for solving a set of interrelated computational geometry problems.
@@
 \end{abstract}
+\subsection*{Keywords}
+unified data structure, simulation problem, interrelated problems set, unified algorithmic environment, concatenable queue
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
+\vspace*{1.0\baselineskip}
+}]
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{unified data structure, simulation problem, interrelated problems set, unified algorithmic environment, concatenable queue}
-
-%% A "teaser" image appears between the author and affiliation
-%% information and the body of the document, and typically spans the
-%% page.
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+\copyrightspace
 	Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of problems.
@@
 In such case some identical steps, such as preprocessing and building data structures, are performed several times.
-
 	Therefore, an important objective in developing the algorithmic models is to create a universal tool, which would have means to efficiently solve a set of problems.
@@
 This model does not repeat computations and the intermediate results are highly reused during the algorithms, which yields good performance.
-
 	In this article we first describe how the convex hull algorithm for a static set of points is decomposed into separate stages and incorporated into our unified algorithmic environment model (UAEM).
@@
 Finally we make complexity analysis for the algorithm and evaluate its performance.
-
 \section{Unified algorithmic environment}
 \label{sec:unified-algorithmic-environment}
+
 \subsection{Algorithms stages}
@@
 The principle will be show on a convex hull algorithm which is similar to the one describe in \cite{overmars} but operates on a static set of points.
-
 	The notion of a convex hull is simple.
@@
 Similarly for the vertical case.
-
 		Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last (if the repetition is more than two).
@@
 Given this, the complexity of the above algorithm is $O(n)$.
-
 		To perform the preprocessing described above, it is needed to:
@@
 Since a list is used to store the points, this operations can be completed in $O(1)$ using the formula below:
-
 		\begin{equation}
@@
 		The recursion stops when there are no more than $3$ points in the set.
-
 		For the base case, the set of points can have $2$ or $3$ elements. In the first case the highest of two points forms the upper part of the hull, and the lower - the lower part.
@@
 For arbitrary points $a_1, a_2$ such that $x(a_1)<x(a_2)$ slope is denoted as $\lambda$:
-
 		\begin{equation}
@@
 
-		\begin{table}[htbp]
+		\begin{table}[htb]
 			\caption{3-points base cases}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{ch_union}}
+		\begin{figure}[htb]
+			\centering
+			\includegraphics[width=0.4\textwidth, height=0.2\textheight]{ch_union}
 			\caption{Merging step of two hulls}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_search}}
+		\begin{figure}[htb]
+			\centering
+			\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_search}
 			\caption{Example of an incorrect position of the utmost left in the left sub-hull}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_edge_points}}
+		\begin{figure}[htb]
+			\centering
+			\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_edge_points}
 			\caption{Example of a convex hull for a wrong position of the utmost left points of the left sub-hull}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_lower_subhull}}
+		\begin{figure}[htb]
+			\centering
+			\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_lower_subhull}
 			\caption{An example of a non-integral hull after merging along the reference lines}
@@
 		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{correct_convex_hull}}
+			\centering
+			\includegraphics[width=0.4\textwidth, height=0.2\textheight]{correct_convex_hull}
 			\caption{Correctly constructed convex hull}
@@
 In fact, it is necessary to create an interface of generic algorithm based on ``divide-and-conquer'' strategy, which will then be used on a specific set of input data.
-
 		We start creating the generic interface by listing its components:
@@
 interface DaCAlgorithm[IT, OT]:
-
   boolean isBaseCase(IT input)
@@
 \subsection{Sequential and parallel execution}
-
 		Although this model very accurately describes the class of algorithms, it does not make it possible to solve the problem directly by having input data.
@@
 Now we will focus on how to efficiently implement it in our algorithmic environment.
-
 		Concatenable queue is an Abstract Data Type, that supports following operations:
-
 		\begin{itemize}
@@
 For the leaf vertices those pointers point to the left and right neighboring leaf vertices or $null$ if the vertex is utmost in the tree.
+
 		Additionally every vertex keeps a pointer to a vertex with the largest element in its left sub-tree, which  allows to perform binary search \cite[pp..~155-157]{aho}.
@@
   updateHeight(result)
+
   return result
@@
       leftQueue.maxNode = node.leftSubtreeMax
-
       rightQueue.root = node.right
       rightQueue.minNode = node.leftSubtreeMax.right
-
       cut(node.leftSubtreeMax)
@@
 		We will argue the complexity of the algorithm by listing the complexities of the main stages it consists of.
-
 		\begin{enumerate}
@@
 
-	\begin{figure}[h]
+	\begin{figure}[htb]
 		\centering
-		\includegraphics[width=0.4\textwidth,height=0.2\textheight]{performance}
+		\includegraphics[width=0.4\textwidth, height=0.2\textheight]{performance}
 		\caption{Performance data}
@@
 
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{article-acm-siggraph}
+\begin{thebibliography}{99}
+\label{references}
 
+\bibitem{imagej} Imagej: An open platform for scientific image analysis. https://imagej.net/Welcome.
+Accessed: 15.04.2019.
+
+\bibitem{imaris} Imaris software. https://imaris.oxinst.com. Accessed: 15.04.2019.
+
+\bibitem{aggarwal} A. Aggarwal, B. Chazelle, L. Guibas, C. O'dunlaing, and C. Yap. Parallel computational ge-
+ometry. Algorithmica, 3(1-4):293-327, November 1988. URL: https://doi.org/10.1007/
+BF01762120, doi:10.1007/BF01762120.
+
+\bibitem{aho} Alfred V. Aho and John E. Hopcroft. The Design and Analysis of Computer Algorithms.
+Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA, 1st edition, 1974.
+
+\bibitem{akl} Selim G. Akl and Kelly A. Lyons. Parallel Computational Geometry. Prentice-Hall, Inc.,
+Upper Saddle River, NJ, USA, 1993.
+
+\bibitem{amato} N. M. Amato, M. T. Goodrich, and E. A. Ramos. Parallel algorithms for higher-dimensional
+convex hulls. In Proceedings 35th Annual Symposium on Foundations of Computer Science,
+pages 683-694, Nov 1994. doi:10.1109/SFCS.1994.365724.
+
+\bibitem{atallah} M. J. Atallah, R. Cole, and M. T. Goodrich. Cascading divide-and-conquer: A technique
+for designing parallel algorithms. SIAM J. Comput., 18(3):499-532, June 1989. URL:
+http://dx.doi.org/10.1137/0218035, doi:10.1137/0218035.
+
+\bibitem{berkman} Omer Berkman, Baruch Schieber, and Uzi Vishkin. A fast parallel algorithm for finding
+the convex hull of a sorted point set. Int. J. Comput. Geometry Appl., 6:231-242, 1996.
+
+\bibitem{chen} D. Z. Chen. Efficient geometric algorithms on the erew pram. IEEE Transactions on
+Parallel and Distributed Systems, 6(1):41-47, Jan 1995. doi:10.1109/71.363412.
+
+\bibitem{cole} R. Cole and M. T. Goodrich. Optimal parallel algorithms for polygon and point-set prob-
+lems. In Proceedings of the Fourth Annual Symposium on Computational Geometry, SCG
+'88, pages 201-210, New York, NY, USA, 1988. ACM. URL: http://doi.acm.org/10.
+1145/73393.73414, doi:10.1145/73393.73414.
+
+\bibitem{goodman} Jacob E. Goodman and Joseph O'Rourke, editors. Handbook of Discrete and Computational
+Geometry. CRC Press, Inc., Boca Raton, FL, USA, 1997.
+
+\bibitem{jaja} J. JaJa. An Introduction to Parallel Algorithms. Addison Wesley, 1997.
+
+\bibitem{overmars} Mark H. Overmars and Jan van Leeuwen. Maintenance of configurations in the plane.
+Journal of Computer and System Sciences, 23(2):166 - 204, 1981.
+
+\bibitem{reif} John H. Reif. Synthesis of Parallel Algorithms. Morgan Kaufmann Publishers Inc., San
+Francisco, CA, USA, 1st edition, 1993.
+
+\bibitem{ilastik} C. Sommer, C. Straehle, U. Koethe, and F. A. Hamprecht. Ilastik: Interactive learning
+and segmentation toolkit. In 2011 IEEE International Symposium on Biomedical Imaging:
+From Nano to Macro, pages 230-233, March 2011. doi:10.1109/ISBI.2011.5872394.
+
+\bibitem{tereshchenko} V. N. Tereshchenko and A. V. Anisimov. Recursion and parallel algorithms in geometric
+modeling problems. Cybernetics and Systems Analysis, 46(2):173-184, 2010.
+
+\bibitem{leeuwen} Jan van Leeuwen, editor. Handbook of Theoretical Computer Science (Vol. A): Algorithms
+and Complexity. MIT Press, Cambridge, MA, USA, 1990.
+\end{thebibliography}
+
+%-------------------------------------------------------------------------
+% example of algorithm typesetting
+% to allow this, uncomment line
+% \RequirePackage[noend]{myalgorithm}
+% in the wscg.sty file
+% and download that package from Gabriel Zachmann's page http://zach.in.tu-clausthal.de/latex/
+%
+%
+%\begin{algorithm}
+%\hrule
+%  \centering
+%\begin{algorithmic}
+%    \STMT $d_{l,r} = f_B(P_1), f_B(P_n)$
+%    \WHILE{ $|d_l| > \epsilon $ and $|d_r| > \epsilon $ and $l<r$}
+%        \STMT $d_x = f_B(P_x)$
+%        \IF{ $d_x < 0$ }
+%            \STMT $l, r = x, r$
+%        \ELSE
+%            \STMT $l, r = l, x$
+%        \ENDIF
+%    \ENDWHILE
+%\end{algorithmic}
+%\hrule
+%\caption{Example of some pseudo-code}
+%\label{fg:code}
+%\end{algorithm}
+
+%-------------------------------------------------------------------------
+
+%\bibliographystyle{ACM-Reference-Format}
+%\bibliography{article-wscg20}
 \end{document}
-\endinput

### 2020-02-27 spaa20/article-spaa20.tex
iadis, spaa20, WSCG20 & calender

--- 2019-12-23 acm siggraph/article-acm-siggraph.tex
@@
 %% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{10.1145/1122445.1122456}
+%\setcopyright{acmcopyright}
+%\copyrightyear{2020}
+%\acmYear{2020}
+%\acmDOI{10.1145/1122445.1122456}
 
 %% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[I3D’19]{ACM SIGGRAPH Symposium on
-Interactive 3D Graphics and Games}{May 05--07, 2020}{San Francisco, USA}
+%\acmConference[I3D’19]{ACM Symposium on Parallelism in Algorithms and Architectures}{July 14--17, 2020}{Philadelphia, PA, USA}
 %\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  % June 03--05, 2018, Woodstock, NY}
-\acmPrice{15.00}
-\acmISBN{978-1-4503-XXXX-X/18/06}
+%\acmPrice{15.00}
+%\acmISBN{978-1-4503-XXXX-X/18/06}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Application of concatenable queue for creation unified data structures in 3-D simulation}
+\title{Application of concatenable queue for parallel computational geometry algorithms}
 
@@
 %%
-\begin{CCSXML}
-<ccs2012>
- <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-  <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
 
@@
 %% the work being presented. Separate the keywords with commas.
-\keywords{unified data structure, simulation problem, interrelated problems set, unified algorithmic environment, concatenable queue}
+\keywords{unified data structure, parallel algorithms, interrelated problems set, unified algorithmic environment, concatenable queue}
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{article-acm-siggraph}
+\bibliography{article-spaa20}
 

### 2020-02-27 templates/wscg20/wscg-template.tex
iadis, spaa20, WSCG20 & calender

% WSCG sample document 
%
% based on Gabriel Zachmann's sample
% http://zach.in.tu-clausthal.de/latex/
%
% modified Apr 2012 to match WSCG Word template
%
\documentclass[twoside,twocolumn,10pt]{article}
%\documentclass[twoside,twocolumn,draft]{article}

%  for debugging
%\tracingall%\tracingonline=0
%\tracingparagraphs
%\tracingpages

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                             Packages

\usepackage{wscg}           % includes a number of other packages (e.g., myalgorithm)
\RequirePackage{ifpdf}
\ifpdf
 \RequirePackage[pdftex]{graphicx}
 \RequirePackage[pdftex]{color}
\else
 \RequirePackage[dvips,draft]{graphicx}
 \RequirePackage[dvips]{color}
\fi
%\usepackage[german,english]{babel}     % default = english
%\usepackage{mypicture}      % loads graphicx.sty, color.sty, eepic.sty
%\usepackage{array}          % better tabular's & arrays, plus math tabular's
%\usepackage{tabularx}      % for selfadjusting p-columns
%\setlength{\extrarowheight}{1ex}   % additional space between rows
%\usepackage{booktabs}      % typographically much better
%\usepackage{mdwlist}        % for compacted lists, and more versatile lists
%\usepackage[intlimits]{amsmath} % more math stuff, see texdoc amsldoc
%\usepackage{mymath}         % own commands, loads amssymb & array.sty
%\usepackage{hyphenat}      % hyphenatable -, /, etc.
%\usepackage{theorem}
%\usepackage[sort&compress]{natbib}% better \cite commands, more flexible
%\usepackage[sort&compress,super]{natbib} % better \cite commands, more flexible
%\newcommand{\citenumfont}[1]{\textit{#1}}

\usepackage{nopageno}       % no page numbers at all; uncomment for final version

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                Title

\title{WSCG Sample LaTeX file}

\author{
\parbox{0.25\textwidth}{\centering
First Author\\[1mm]
author's affiliation\\
1st line of address\\
2nd line of address\\
Country (ZIP) code, City, State\\[1mm]
e@mail
}
\hspace{0.05\textwidth}
\parbox{0.25\textwidth}{\centering
Second Author\\[1mm]
author's affiliation\\
1st line of address\\
2nd line of address\\
Country (ZIP) code, City, State\\[1mm]
e@mail
}
\hspace{0.05\textwidth}
\parbox{0.25\textwidth}{\centering
Third Author\\[1mm]
author's affiliation\\
1st line of address\\
2nd line of address\\
Country (ZIP) code, City, State\\[1mm]
e@mail
}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                          Hyperref

% no hyperlinks
\usepackage{url}
\urlstyle{tt}

% Donald Arsenau's fix for missing kerning of "//" and ":/"
\makeatletter
\def\Uslash{\mathbin{\mathchar`\/}\@ifnextchar{/}{\kern-.15em}{}}
\g@addto@macro\UrlSpecials{\do \/ {\Uslash}}
\def\Ucolon{\mathbin{\mathchar`:}\@ifnextchar{/}{\kern-.1em}{}}
\g@addto@macro\UrlSpecials{\do : {\Ucolon}}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                              My Commands

%\DeclareMathOperator{\sgn}{sgn}

%\theorembodyfont{\upshape}
%\theoremstyle{break}
%\theoremheaderfont{\bfseries\normalsize}

%\newtheorem{lem}{Lemma}
%\newtheorem{defn}{Definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                Document

\begin{document}

\twocolumn[{\csname @twocolumnfalse\endcsname

\maketitle  % full width title

\begin{abstract}
\noindent
We describe the formatting guidelines for the Journal of WSCG and WSCG proceedings adapted from the ACM and SIGGRAPH proceedings and recent WSCG templates.  Please, try to fix format of your contribution as close as possible if you use other tools.

\end{abstract}

\subsection*{Keywords}
Keywords are your own designated keywords - Times New Roman, 10pts.

\vspace*{1.0\baselineskip}
}]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\copyrightspace

We ask authors to follow this guideline and make paper look exactly like as this document. The easiest way to do this is simply to download a template from \cite{jou01a} and replace the content with your own.

\section{Page size}
Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.

All material on all pages should fit within a rectangle of 16 x 23.7 cm (6.3"x 9.33"), centered on the page horizontally, beginning 2.5 cm (1") from the top of the page and ending with 3,5 cm (1.4") from the bottom.  The right and left margins should be 2.5 cm (1"). The text should be in two 7.6 cm (3") columns with a 0.8 cm (0.3") gutter.

\section{Typeset text}
\subsection*{Normal or Body Text}
Please use a 10-point Times Roman font, or other Roman font with serifs, as close as possible in appearance to Times Roman in which these guidelines have been set. The goal is to have a 10-point text, as you see here. Please use sans-serif or non-proportional fonts only for special purposes, such as distinguishing source code text. If Times Roman is not available, try the font named Computer Modern Roman. On a Macintosh, use the font named Times.  Right margins should be justified, not ragged.

\subsection*{Title and Authors}
The title (Helvetica 18-point bold), authors' names (Helvetica 10-point) and affiliations (Helvetica 10 point) run across the full width of the page -- one column wide. We also recommend e-mail address (Helvetica 10 point). See the top of this page for three addresses. If only one address is needed, center all address text. For two addresses, use two centered tabs, and so on. For more than three authors, you may have to improvise.\footnote{If necessary, you may place some address information in a footnote, or in a named section at the end of your paper, but margins must remain empty.}

\subsection*{First Page Copyright Notice}
Please include 3.8 cm (1.5") text box with the text shown at the bottom of the left column of the first page with the copyright notice.

\subsection*{Others Pages}
Others pages start at the top of the page (margin 2.5 cm) and continue in double-column format.  The two columns on the last even page should be as close to equal length as possible.

{\bfseries Total length of a paper is max. 8 pages.}

Footnotes should be Times New Roman 9-point, and justified to the full width of the column.

Please, use the standard Journal of WSCG format for references -- that is, a numbered list at the end of the article, ordered alphabetically by first author, and referenced by a name in brackets \cite{con00a}. See the examples of citations at the end of this document. Within this template file, use the style named references for the text of your citation.

The references are also in 9 pt., but that section (see Section \ref{references}) is ragged right. References should be published materials accessible to the public. Internal technical reports may be cited only if they are easily accessible (i.e. you can give the address to obtain the report within your citation) and may be obtained by any reader. Proprietary information may not be cited. Private communications should be acknowledged, not referenced, e.g. "[Adam, personal communication]").

\subsection*{Page Numbering, Headers and Footers}
Do not include headers, footers or page numbers in your submission. These will be added when the publications are assembled.

\begin{figure}[htb]
    \centering
    \rule{6cm}{3cm}
    \caption{Insert caption to place caption below figure.}
    \label{fig:box}
\end{figure}

\begin{table}[htb]
	\centering
	\begin{tabular}{|l|l|l|l|}
	\hline
	Graphics & Top & In-between & Bottom \\
	\hline
	Tables & End & Last & First \\
	\hline
	Figures & Good & Similar & Very well \\
	\hline
	\end{tabular}
	\caption{Table captions should be placed below the table}
\end{table}

\section{Figures/Captions}
Place Tables/Figures/Images in text as close to the reference as possible (see Fig.\ref{fig:box}). It may extend across both columns to a maximum width of 16 cm (6.3"). Captions should be Times New Roman 10-points.  They should be numbered (e.g., "Table 1" or "Figure 2"), please note that the word for Table and Figure are spelled out. Figure's and Table's captions should be centered beneath the image, picture or a table.

\section{Sections}
The heading of a section should be in Times New Roman 12-point bold in all-capitals flush left with an additional 6-points of white space above the section head.  Sections and subsequent sub- sections should be numbered and flush left. For a section head and a subsection head together (such as Section 3 and Subsection 3.1), use no additional space above the subsection head.

\subsection{Subsections}
The heading of subsections should be in Times New Roman 12-point bold with only the initial letters capitalized. (Note: For subsections and subsubsections, a word like the or a is not capitalized unless it is the first word of the header.)

\subsubsection{Subsubsections}
The heading for subsubsections should be in Times New Roman 11-point italic with initial letters capitalized and 6-points of white space above the subsubsection head.

\section{Acknowledgments}
Our thanks to ACM SIGCHI and SIGGRAPH for allowing us to modify templates they had developed.

%-------------------------------------------------------------------------
% example of algori typesetting
% to allow this, uncomment line 
% \RequirePackage[noend]{myalgorithm}
% in the wscg.sty file
% and download that package from Gabriel Zachmann's page http://zach.in.tu-clausthal.de/latex/
%
%
%\begin{algorithm}
%\hrule
%  \centering
%\begin{algorithmic}
%    \STMT $d_{l,r} = f_B(P_1), f_B(P_n)$
%    \WHILE{ $|d_l| > \epsilon $ and $|d_r| > \epsilon $ and $l<r$}
%        \STMT $d_x = f_B(P_x)$
%        \IF{ $d_x < 0$ }
%            \STMT $l, r = x, r$
%        \ELSE
%            \STMT $l, r = l, x$
%        \ENDIF
%    \ENDWHILE
%\end{algorithmic}
%\hrule
%\caption{Example of some pseudo-code}
%\label{fg:code}
%\end{algorithm}

%-------------------------------------------------------------------------

\begin{thebibliography}{99}
\label{references}
\bibitem[And01a]{and01a} Anderson, R.E. Social impacts of computing: Codes of professional ethics. Social Science, pp.453-469, 2001.
\bibitem[Con00a]{con00a} Conger., S., and Loch, K.D. (eds.). Ethics and computer use. Com.of ACM 38, No.12, 2000.
\bibitem[Con00b]{con00b} Mackay, W.E. Ethics, lies and videotape, in Conf.proc. CHI'00, Denver CO, ACM Press, pp.138-145, 2000.
\bibitem[Jou01a]{jou01a} Journal of WSCG \& WSCG templates: http://wscg.zcu.cz/jwscg/template.doc (MSWord)
http://wscg.zcu.cz/jwscg/template.pdf (PDF)
\end{thebibliography}

{\bfseries
Last page should be fully used by text, figures etc. Do not leave empty space, please.

Do not lock the PDF -- additional text and info will be inserted, i.e. ISSN/ISBN etc. 
}

\end{document}

### 2020-03-27 ComPE20/article-compe20.tex
ComPE20, eurocg20

--- 2019-11-20 article/article.tex
@@
 \documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 \usepackage{cite}
@@
 
-\usepackage{diagbox}
 \usepackage{amsthm}
-\usepackage[formats]{listings}
+\usepackage{listings}
 \lstset{
 	language=Java,
-	basicstyle=\small,
 	breaklines,
@@
 \DeclareGraphicsExtensions{.pdf,.png,.jpg}
-\theoremstyle{plane}
-\newtheorem{theorem}{Theorem}[section]
+
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
+\newtheorem{lemma}{Lemma}
 
 \begin{document}
+
+\title{Application of concatenable queue for parallel computational geometry algorithms*\\}
 
@@
 }
+
 \maketitle
@@
 \begin{abstract}
-		The paper is devoted to the development and  of an efficient algorithmic model for solving a set of interrelated computational geometry problems.
-To do this, a unified algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources.
+	This paper is devoted to the development of an algorithmic model, which will be able to solve a set of interrelated computational geometry problems efficiently.
+To do this, an algorithmic environment with unified data structure is created, which allows to implement complex use cases efficiently with respect to computational resources.
 We build the environment on the basis of the ``divide and conquer'' strategy.
@@
 The data structure is implemented in a form of a binary tree.
-This allows to perform operations needed in algorithm for a set of problems in $O(\log n)$ time.
+This allows to perform operations needed in algorithms for a set of problems in $O(\log n)$ time.
 Furthermore we offer a way to execute the algorithms both sequentially and in parallel.
@@
 \begin{IEEEkeywords}
-Algorithmic tools,   Computational geometry, Interrelated problems set, Unified algorithmic environment, Concatenable queue
+unified data structure, simulation problem, interrelated problems set, unified algorithmic environment, concatenable queue
 \end{IEEEkeywords}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
+\label{sec:introduction}
 
-		Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of problems.
+	Nowadays, advanced computer simulations and visualizations of complex scientific researches as well as large scale technical projects require to simultaneously solve a set of problems.
 The core of this set are problems of computational geometry and computer graphics.
 To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time.
-Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy.
+Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package do not result in desirable efficiency and accuracy.
 It is worth noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems such as in \cite{aggarwal,atallah,cole,amato,chen,berkman,goodman,akl,jaja,leeuwen,reif}.
 Every such algorithm requires its own computational resources and is executed independently from others.
-In such case some identical steps, such as preprocessing and building data structures, are performed several times.
+In such cases some identical steps, such as preprocessing and building data structures, are performed several times.
 
-		Therefore, an important objective in developing the algorithmic models is to create a universal tool, which would have means to efficiently solve a set of problems.
-This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of the unified data structures.
+	Therefore, an important objective in developing algorithmic models is to create a universal tool, which would have means to efficiently solve a set of problems.
+This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of unified data structures.
 In \cite{tereshchenko} the notion of a unified algorithmic environment is introduced, which is based on the ``divide-and-conquer'' principle and takes into account the aforementioned features of the algorithms.
-In particular, the preprocessing and splitting the initial set of data to form the recursion tree is common for all problems and is executed only once.
+In particular, preprocessing and splitting the initial set of data to form recursion tree is common for all problems and is executed only once.
 During the merge stage intermediate results are maintained in a weighted concatenable queue.
@@
 \section{Unified algorithmic environment}
+\label{sec:unified-algorithmic-environment}
+
 \subsection{Algorithms stages}
@@
 
-		In this section we describe the principle of how we decompose each algorithm into distinct parts.
+	In this section we described the principle of how we decompose each algorithm into distinct parts.
 This partition is then used to avoid repeating the computations in the algorithmic environment.
-The principle will be show on a convex hull algorithm which is similar to the one describe in \cite{overmars} but operates on a static set of points.
+The principle will be shown on a convex hull algorithm which is similar to the one describe in \cite{overmars} but operates on a static set of points.
 
 	The notion of a convex hull is simple.
-For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$.
-In practice to solve such problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
+For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprises $S$.
+In practice to solve such a problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
+	From now on we will consider the case where $k=2$.
 
@@
 For $a = (x_a, y_a)$ we denote $x(a)=x_a$, $y(a)=y_a$.
-Let points $a_1, a_2, ..., a_k$ lie on one horizontal line and $x(a_1) < x(a_2) <...
-<x (a_k) $.
+Let the points $a_1, ..., a_k$ lie on one horizontal line and $x(a_1) < ...
+< x (a_k) $.
 Then, by the criterion, the points $a_2, a_3, ..., a_{k-1}$ must be removed.
@@
 
-		Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last one (if there are more than two repetitions).
-The idea behind the algorithm is to use two pointers technique to delete repetitions by overwriting their place with other non-repeating element.
-This way, additional memory usage can be reduced to a constant value.
-The algorithm makes one pass through the array.
-At each step, a constant amount of work is performed to decide whether to delete the current item.
-Given this, the complexity of the above algorithm is $O(n)$.
+	The algorithm of removing "inner" repetitions in a sorted array is trivial.
 
@@
 		\item
-			Delete repetitions by $y$ coordinate using the described algorithm.
+		Delete "inner" repetitions by $y$ coordinate using the described algorithm.
 		\item
@@
 		\item
-			Delete repetitions by $x$ coordinate using the described algorithm.
+		Delete "inner" repetitions by $x$ coordinate.
 	\end{enumerate}
@@
 
-		At the stage of splitting the initial problem, the set of points is divided into left and right parts of equal size.
-Since a array-like data structure is used to store the points, this operations can be completed in $O(1)$ using the formula below:
+	At the stage of splitting the initial problem, the set of points is separated into left and right parts of equal size.
+Since an array-like data structure is used to store the points, this operations can be completed in $O(1)$ using the formula below:
 
@@
 
-		For the base case, the set of points can have $2$ or $3$ elements.
-In the first case the highest of two points forms the upper part of the hull, and the lower - the lower part.
-To consider the base case of $3$ points, we introduce an additional notion of the tangent slope given by two points on the plane.
-For arbitrary points $a_1, a_2$ such that $x(a_1)<x(a_2)$ slope is denoted as $\lambda$:
-
-		\begin{equation}
-			\lambda(a_1, a_2)=\frac{y(a_2)-y(a_1)}{x(a_2)-x(a_1)}
-		\end{equation}
-		According to this definition, the possible cases for points $a_1,a_2,a_3$ are given in Table \ref{table:3points}:
-
-		\begin{table}[htbp]
-			\caption{3-points base cases}
-			\label{table:3points}
-			\begin{center}
-				\begin{tabular}{|c|c|c|c|}
-					\hline
-					\textbf{$\lambda(a_1, a_2) > \lambda(a_2, a_3)$} & \textbf{$y(a_1) < y(a_2)$} & upper part & lower part\\
-					\hline
-					false & false & $a_1, a_3$ & $a_2$ \\
-					\hline
-					false & true & $a_1, a_3$ & $a_2$ \\
-					\hline
-					true & false & $a_2, a_3$ & $a_1$ \\
-					\hline
-					true & true & $a_1, a_2$ & $a_3$ \\
-					\hline
-				\end{tabular} 
-			\end{center}
-		\end{table}
+	For the base case, the set of points can have $2$ or $3$ elements. In those two cases the convex hull can be trivially constructed.
 
@@
 Then, using the two-pointer technique and the cases described in \cite{overmars}, the proper tangent line is searched.
-It remains to split the two queues at the found vertices that form the tangent and to merge the remaining parts.
-An example of performing such a procedure is shown in Fig.
-\ref{fig:ch_union}.
+	It remains to split the two queues at the found vertices that form the tangent and to merge the remaining parts. An example of performing such a procedure is shown in Fig. \ref{fig:ch_union}.
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{ch_union}}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.4\textwidth, height=0.2\textheight]{ch_union}
 		\caption{Merging step of two hulls}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_search}}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_search}
 		\caption{Example of an incorrect position of the utmost left in the left sub-hull}
@@
 Similarly to the previous argument, they must be transferred to the upper parts of the hulls.
-And after merging these points must be transferred to the lower parts of the hull, if they do not belong to the resulting upper part of the final hull.
+And after merging, these points must be transferred to the lower parts of the hull, if they do not belong to the resulting upper part of the final hull.
 Otherwise, the formed hull may be incorrect.
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_edge_points}}
-			\caption{Example of a convex hull for a wrong position of the utmost left points of the left sub-hull}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_edge_points}
+		\caption{Example of a convex hull for a wrong position of the utmost left point of the left sub-hull}
 		\label{fig:incorect_edge_points}
@@
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_lower_subhull}}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_lower_subhull}
 		\caption{An example of a non-integral hull after merging along the reference lines}
@@
 Fig.
-\ref{fig:correct_convex_hull} shows correct convex hull.
+\ref{fig:correct_convex_hull} shows the correct convex hull.
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.4\textwidth, height=0.2\textheight]{correct_convex_hull}}
+	\begin{figure}[t]
+		\centering
+		\includegraphics[width=0.4\textwidth, height=0.2\textheight]{correct_convex_hull}
 		\caption{Correctly constructed convex hull}
@@
 The construction of such an object requires the combination of an algorithmic database together with the necessary data structures.
-In fact, it is needed to create an interface of generic algorithm based on ``divide-and-conquer'' strategy, which will then be used on a specific input data.
+In fact, it is needed to create an interface for generic algorithms based on a ``divide-and-conquer'' strategy, which will then be used on specific input data.
 
@@
 	Although this model very accurately describes the class of algorithms, it does not make it possible to solve the problem directly by having input data.
-This in fact allows to divide implementation of the algorithm from how it is executed.
+This in fact allows to separate implementation of the algorithm from how it is executed.
 Next the principles of sequential and parallel execution are discussed.
@@
 	When executing sequentially an algorithm, its individual sub-problems are computed one by one.
-We first check if current input is a base case and if so we can directly compute it by calling $solveBaseCase$ procedure.
-Otherwise input is split with $divide$ and obtained sub-problem are solved sequentially.
-Finally obtained results are merged with $merge$ procedure.
+We first check if the current input is a base case and if so we can directly compute it by calling $solveBaseCase$ procedure.
+Otherwise the input is split with $divide$ and the obtained sub-problem are solved sequentially.
+Finally the obtained results are merged with $merge$ procedure.
 
@@
 
-		To construct the concurrent execution algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$.
-which runs the functions $function1$ and $function2$ simultaneously.
-We use it to solve sub-problem obtained after splitting a given input.
+	To construct the concurrent execution algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$ which runs the functions $function1$ and $function2$ simultaneously.
+We use it to solve sub-problems obtained after splitting a given input.
 Other than that parallel version is identical to the sequential one.
 
-		Practically, from the implementation standpoint performance of parallel execution was improved by introducing a limit on the size of sub-tasks that can be calculated in parallel.
+	From the implementation standpoint, the performance of parallel execution was improved by introducing a limit on the size of sub-tasks that can be calculated in parallel.
 This allowed to put a threshold on the amount of work for one thread.
@@
 Going back a new non-leaf vertex is created - the parent for the new element and one of its neighbor.
-The algorithm is formally described on the Listing \ref{lst:insert-alg}.
+The algorithm is formally described in Listing \ref{lst:insert-alg}.
 
@@
 The value, by which the split has been performed, belongs to the left sub-queue.
-The procedure is formally described on the Listing \ref{lst:split-alg}.
+The procedure is formally described in Listing \ref{lst:split-alg}.
 
@@
 
-		The algorithm of the $concatenateNodes$ procedure is described on the Listing \ref{lst:concatenate-als}.
+	The algorithm of the $concatenateNodes$ procedure is described in Listing \ref{lst:concatenate-als}.
 
@@
 \subsection{Performance}
-		A number of algorithm performance measurements were performed for different input sizes and the average number of recursive tasks per thread. The results are shown on the Fig. \ref{fig:performance}.
 
-		\begin{figure}[htbp]
-			\centerline{\includegraphics[width=0.5\textwidth, height=0.3\textheight]{performance}}
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+% ----------------------------------------------- PERFORMANCE ---------------------------------------------------------------------
+% //////////////////////////////////////////////////////////////////////////////////////////////////////////////////////////
+
+	A number of algorithm performance measurements were performed for different input sizes and the average number of recursive subproblems per thread.
+The results are shown in Fig.
+\ref{fig:performance}.
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.4\textwidth, height=0.2\textheight]{performance}
 		\caption{Performance data}
@@
 	\end{figure}
+
 \section{Conclusion}
+\label{sec:coclusion}
 
-We`ve considered in details the process of designing and implementing the UAEM as well unified data structures for it.
+	We've considered in details the process of designing and implementing the UAEM as well as unified data structures for it.
 In this model a generic interface of a ``divide-and-conquer'' algorithm was created.
 This allows us to execute the algorithms which are implemented according to this model both sequentially and in parallel.
-Apart from that concatenable queue was implemented and served as the basis for the model described above.
+Apart from that a concatenable queue was implemented and served as the basis for the model described above.
 
-Using the data structure allowed to significantly reduce the time and computational resources for solving set of problems, such as constructing the convex hull.
+	Using the data structure allowed to significantly reduce the time and computational resources for solving a set of problems, such as constructing the convex hull.
 The algorithmic environment was implemented in Java programming language using its standard library.
-The main advantages of the developed algorithm are optimized preprocessing stage and the efficiently implemented merge step, due to the usage of concatenable queue.
+The main advantages of the developed algorithm are an optimized preprocessing stage and the efficiently implemented merge step, due to the usage of concatenable queue.
 
 	The performance comparison for both types of execution allows to conclude that the algorithm has high level of parallelism.
-We`ve achieved speedup of $28\%$ in the best case.
+We've achieved speedup of $28\%$ in the best case.
 It is easy to extend functionality of the created environment either by adding new or modifying existing algorithms.
@@
 
-\begin{thebibliography}{00}
-	\bibitem{ilastik} C.
-Sommer, C.
-Straehle, U.
-Köthe and F.
-A.
-Hamprecht, ``Ilastik: Interactive learning and segmentation toolkit,'' 2011 IEEE International Symposium on Biomedical Imaging: From Nano to Macro, Chicago, IL, 2011, pp..
-230-233.
-	doi: 10.1109/ISBI.2011.5872394
+\bibliographystyle{./IEEEtran}
+\bibliography{./IEEEabrv,./article-compe20}
 
-	\bibitem{imaris} IMARIS Software. Accessed on: 15.04.2019. [Online]. Available: https://imaris.oxinst.com
-
-	\bibitem{imagej} ImageJ: An open platform for scientific image analysis. Accessed on: 15.04.2019. [Online]. Available: https://imagej.net/Welcome
-
-	\bibitem{aggarwal} А. Aggarwal et al., ``Parallel computational geometry,'' Algorithmica 3, 1-4 (November 1988), pp.. 293-327.
-
-	\bibitem{atallah} M.J. Atallah, R. Cole, M.T. Goodrich, ``Cascading divide-and-conquer: a technique for designing parallel algorithms,'' SIAM J. Comput. 18, 1989, pp.. 499-532.
-
-	\bibitem{cole} R.
-Cole, M.T.
-Goodrich, ``Optimal parallel algorithms for polygon and point-set problems,'' In Proceedings of the fourth annual symposium on Computational geometry (SCG '88), ACM, New York, NY, USA, pp..
-201-210.
-
-	\bibitem{amato} N.M.
-Amato, M.T.
-Goodrich and E.A.
-Ramos, ``Parallel algorithms for higher-dimensional convex hulls,'' Proceedings 35th Annual Symposium on Foundations of Computer Science, Santa Fe, NM, USA, 1994, pp..
-683-694.
-
-	\bibitem{chen} D.Z. Chen, ``Efficient geometric algorithms on the EREW PRAM,'' in IEEE Transactions on Parallel and Distributed Systems, vol. 6, no. 1, pp.. 41-47, Jan. 1995.
-	doi: 10.1109/71.363412
-
-	\bibitem{berkman} O. Berkman, B. Schieber, U. Vishkin, ``A fast parallel algorithm for finding the convex hull of a sorted point set,'' Internat. J. Comput. Geom. Appl. 6, 1996, pp.. 231-242.
-
-	\bibitem{goodman} J.E. Goodman and J. O'Rourke, editors,  Handbook of Discrete and Computational Geometry, CRC Press LLC, Boca Raton, FL, 2004.
-
-	\bibitem{akl} Selim G. Akl and Kelly A. Lyons, Parallel Computational Geometry, Englewood Cliffs: Prentice-Hall, 1993.
-
-	\bibitem{jaja} J. JaJa, An Introduction to Parallel Algorithms, Amsterdam: Addison-Wesley, 1992.
-
-	\bibitem{leeuwen} J. Van Leeuwen, Handbook of Theoretical Computer Science, Amsterdam: Elsevier/The MIT Press, 1990.
-
-	\bibitem{reif} J.H. Reif, Synthesis of Parallel Algorithms, San Mateo: Morgan Kaufmann, 1993.
-
-	\bibitem{tereshchenko} V.
-N.
-Tereshchenko, A.
-V.
-Anisimov, Recursion and parallel algorithms in geometric modeling problems, Journal: Cybernetics and Systems Analysis: Vol.
-46, N 2 (2010), pp..
-173-184.
-
-	\bibitem{overmars} Mark H. Overmars, Jan van Leeuwen, ``Maintenance of configurations in the plane,'' Journal of Computer and System Sciences, Volume 23, Issue 2, 1981, pp.. 166-204.
-
-	\bibitem{aho} Alfred V. Aho and John E. Hopcroft, The Design and Analysis of Computer Algorithms, 1st ed. Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA, 1974.
-\end{thebibliography}
 \end{document}

### 2020-03-27 WSCG20/article-wscg20.tex
ComPE20, eurocg20

@@
 
-%\DeclareMathOperator{\sgn}{sgn}
-%\theorembodyfont{\upshape}
-%\theoremstyle{break}
-%\theoremheaderfont{\bfseries\normalsize}
-
 \newtheorem{theorem}{Theorem}
@@
 \newtheorem{lemma}{Lemma}
-
-%\newtheorem{thrm}{Theorem}
-%\newtheorem{lem}{Lemma}
-%\newtheorem{defn}{Definition}
 
@@
 \noindent
-	The paper is devoted to the development and  of an efficient algorithmic model for solving a set of interrelated computational geometry problems.
-To do this, a unified algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources.
+	This paper is devoted to the development of an algorithmic model, which will be able to solve a set of interrelated computational geometry problems efficiently.
+To do this, an algorithmic environment with unified data structure is created, which allows to implement complex use cases efficiently with respect to computational resources.
 We build the environment on the basis of the ``divide and conquer'' strategy.
@@
 \copyrightspace
-	Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of problems.
+
+	Nowadays, advanced computer simulations and visualizations of complex scientific researches as well as large scale technical projects require to simultaneously solve a set of problems.
 The core of this set are problems of computational geometry and computer graphics.
 To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time.
-Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package does not result in desirable efficiency and accuracy.
+Existing methods (iLastic \cite{ilastik}, IMARIS \cite{imaris}, ImageJ \cite{imagej}), that are based on a set of algorithms implementations organized in a package do not result in desirable efficiency and accuracy.
 It is worth noting, that there are a lot of parallel algorithms designed to solve specifically certain computational geometry problems such as in \cite{aggarwal,atallah,cole,amato,chen,berkman,goodman,akl,jaja,leeuwen,reif}.
 Every such algorithm requires its own computational resources and is executed independently from others.
-In such case some identical steps, such as preprocessing and building data structures, are performed several times.
-	Therefore, an important objective in developing the algorithmic models is to create a universal tool, which would have means to efficiently solve a set of problems.
-This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of the unified data structures.
+In such cases some identical steps, such as preprocessing and building data structures, are performed several times.
+
+	Therefore, an important objective in developing algorithmic models is to create a universal tool, which would have means to efficiently solve a set of problems.
+This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of unified data structures.
 In \cite{tereshchenko} the notion of a unified algorithmic environment is introduced, which is based on the ``divide-and-conquer'' principle and takes into account the aforementioned features of the algorithms.
-In particular, the preprocessing and splitting the initial set of data to form the recursion tree is common for all problems and is executed only once.
+In particular, preprocessing and splitting the initial set of data to form recursion tree is common for all problems and is executed only once.
 During the merge stage intermediate results are maintained in a weighted concatenable queue.
 This model does not repeat computations and the intermediate results are highly reused during the algorithms, which yields good performance.
+
 	In this article we first describe how the convex hull algorithm for a static set of points is decomposed into separate stages and incorporated into our unified algorithmic environment model (UAEM).
@@
 Finally we make complexity analysis for the algorithm and evaluate its performance.
+
 \section{Unified algorithmic environment}
@@
 
-	In this section we describe the principle of how we decompose each algorithm into distinct parts.
+	In this section we described the principle of how we decompose each algorithm into distinct parts.
 This partition is then used to avoid repeating the computations in the algorithmic environment.
-The principle will be show on a convex hull algorithm which is similar to the one describe in \cite{overmars} but operates on a static set of points.
+The principle will be shown on a convex hull algorithm which is similar to the one describe in \cite{overmars} but operates on a static set of points.
+
 	The notion of a convex hull is simple.
-For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$.
-In practice to solve such problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
+For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprises $S$.
+In practice to solve such a problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
+	From now on we will consider the case where $k=2$.
 
@@
 For $a = (x_a, y_a)$ we denote $x(a)=x_a$, $y(a)=y_a$.
-Let points $a_1, a_2, ..., a_k$ lie on one horizontal line and $x(a_1) < x(a_2) <...
-<x (a_k) $.
+Let the points $a_1, ..., a_k$ lie on one horizontal line and $x(a_1) < ...
+< x (a_k) $.
 Then, by the criterion, the points $a_2, a_3, ..., a_{k-1}$ must be removed.
-Similarly for the vertical case.
-		Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last (if the repetition is more than two).
-The idea behind the algorithm is to use two pointers to delete repetitions by overwriting their place with other non-repeating element.
-In this way, additional memory usage can be reduced to a constant value.
-The algorithm makes one pass through the array.
-At each step, a constant amount of work is performed to decide whether to delete the current item.
-Given this, the complexity of the above algorithm is $O(n)$.
+Analogously for the vertical case.
+
+	The algorithm of removing "inner" repetitions in a sorted array is trivial.
+
 	To perform the preprocessing described above, it is needed to:
@@
 
-		At the stage of splitting the initial problem, the current set of points is divided into left and right parts of equal size.
-Since a list is used to store the points, this operations can be completed in $O(1)$ using the formula below:
+	At the stage of splitting the initial problem, the set of points is separated into left and right parts of equal size.
+Since an array-like data structure is used to store the points, this operations can be completed in $O(1)$ using the formula below:
+
 	\begin{equation}
@@
 	The recursion stops when there are no more than $3$ points in the set.
-		For the base case, the set of points can have $2$ or $3$ elements. In the first case the highest of two points forms the upper part of the hull, and the lower - the lower part.
-		To consider the base case of $3$ points, we introduce an additional notion of the tangent slope given by two points on the plane.
-For arbitrary points $a_1, a_2$ such that $x(a_1)<x(a_2)$ slope is denoted as $\lambda$:
-		\begin{equation}
-			\lambda(a_1, a_2)=\frac{y(a_2)-y(a_1)}{x(a_2)-x(a_1)}
-		\end{equation}
-		According to this definition, the possible cases for points $a_1,a_2,a_3$ are given in Table \ref{table:3points}:
 
-		\begin{table}[htb]
-			\caption{3-points base cases}
-			\label{table:3points}
-			\begin{center}
-				\begin{tabular}{|c|c|c|c|}
-					\hline
-					\textbf{$\lambda(a_1, a_2) > \lambda(a_2, a_3)$} & \textbf{$y(a_1) < y(a_2)$} & upper part & lower part\\
-					\hline
-					false & false & $a_1, a_3$ & $a_2$ \\
-					\hline
-					false & true & $a_1, a_3$ & $a_2$ \\
-					\hline
-					true & false & $a_2, a_3$ & $a_1$ \\
-					\hline
-					true & true & $a_1, a_2$ & $a_3$ \\
-					\hline
-				\end{tabular}
-			\end{center}
-		\end{table}
+	For the base case, the set of points can have $2$ or $3$ elements. In those two cases the convex hull can be trivially constructed.
 
@@
 
-		\cite{overmars} provides an algorithm for merging two convex hulls.
-The essence of the algorithm is to maintain the hull with the help of two concatenated queues.
+	In \cite{overmars} an algorithm for merging two convex hulls is described.
+The idea of this algorithm is to maintain the hull in two concatenated queues.
 The hull is divided into two parts.
-In this article, the separation occurs from top to bottom.
+In this article it is divided into the upper and the lower sub-hulls.
 Then, using the two-pointer technique and the cases described in \cite{overmars}, the proper tangent line is searched.
-It remains to split the two queues at the 2 found vertices that form the tangent and to merge the remaining parts.
-An example of performing such a procedure is shown in Fig.
-\ref{fig:ch_union}.
+	It remains to split the two queues at the found vertices that form the tangent and to merge the remaining parts. An example of performing such a procedure is shown in Fig. \ref{fig:ch_union}.
 
-		\begin{figure}[htb]
+	\begin{figure}[t]
 		\centering
@@
 	It remains to consider the corner cases that arise when performing the merging.
-The first of these cases is related to the ambiguity of the position of the utmost points in the described representation of the convex hull.
+The first of these cases is related to the ambiguity of the position of the utmost points in the described representation.
 The leftmost point of the left hull and the rightmost point of the right hull must belong to the upper parts of the view before finding the tangent line, because otherwise such tangent may be found incorrectly.
@@
 
-		\begin{figure}[htb]
+	\begin{figure}[t]
 		\centering
@@
 
-		To avoid such a situation, it is necessary to move the indicated points from their upper parts before merging the sub-hulls.
+	To avoid such a situation, it is necessary to move the indicated points to the upper sub-hulls before merging them.
 For the rightmost point of the left hull and the leftmost point of the right hull we have the following cases.
 Similarly to the previous argument, they must be transferred to the upper parts of the hulls.
-And after merging these points must be transferred to the lower parts of the hull, if they do not belong to the created upper part of the final hull.
+And after merging, these points must be transferred to the lower parts of the hull, if they do not belong to the resulting upper part of the final hull.
 Otherwise, the formed hull may be incorrect.
@@
 
-		\begin{figure}[htb]
+	\begin{figure}[t]
 		\centering
 		\includegraphics[width=0.4\textwidth, height=0.2\textheight]{incorect_edge_points}
-			\caption{Example of a convex hull for a wrong position of the utmost left points of the left sub-hull}
+		\caption{Example of a convex hull for a wrong position of the utmost left point of the left sub-hull}
 		\label{fig:incorect_edge_points}
@@
 Then searching for the left and right pivoting vertices in the concatenable queue is performed.
-After that, the queue is splits over the found vertices.
-		Fig. \ref{fig:correct_convex_hull} shows correct convex hull.
+After that, the queue is split over the found vertices.
+Fig.
+\ref{fig:correct_convex_hull} shows the correct convex hull.
 
-		\begin{figure}[htbp]
+	\begin{figure}[t]
 		\centering
@@
 The construction of such an object requires the combination of an algorithmic database together with the necessary data structures.
-In fact, it is necessary to create an interface of generic algorithm based on ``divide-and-conquer'' strategy, which will then be used on a specific set of input data.
+In fact, it is needed to create an interface for generic algorithms based on a ``divide-and-conquer'' strategy, which will then be used on specific input data.
+
 	We start creating the generic interface by listing its components:
@@
 	Each of these components will represent a function in the future interface.
-Here there is a clear separation between the input type for the algorithm and the type of result it returns.
+Here there is a clear separation between the input type for the algorithm and the type of the result it returns.
 These two types should be parameters of the algorithm model.
@@
 	A large number of computational geometry algorithms, such as computing minimal spanning tree, the Delaunay triangulation, the Voronoi diagram and the convex hull accept the list of points.
-However, would be wrong limit the input type in the algorithm interface to a list of points.
-The reason for this is that some algorithms can use the results of other algorithms as input data.
+However, it would be wrong to limit the input type in the algorithm interface to a list of points.
+The reason for this is the fact that some algorithms can use the results of other algorithms as input data.
 A well known example is the construction of a Delaunay triangulation based on the Voronoi diagram maintained in a special data structure.
@@
 \subsection{Sequential and parallel execution}
+
 	Although this model very accurately describes the class of algorithms, it does not make it possible to solve the problem directly by having input data.
-This in fact allows to divide implementation of the algorithm from how it is executed.
+This in fact allows to separate implementation of the algorithm from how it is executed.
 Next the principles of sequential and parallel execution are discussed.
@@
 Now we will focus on how to efficiently implement it in our algorithmic environment.
+
 	Concatenable queue is an Abstract Data Type, that supports following operations:
+
 	\begin{itemize}
@@
 For the leaf vertices those pointers point to the left and right neighboring leaf vertices or $null$ if the vertex is utmost in the tree.
-
 	Additionally every vertex keeps a pointer to a vertex with the largest element in its left sub-tree, which  allows to perform binary search \cite[pp..~155-157]{aho}.
@@
 		We will argue the complexity of the algorithm by listing the complexities of the main stages it consists of.
+
 		\begin{enumerate}
@@
 	A number of algorithm performance measurements were performed for different input sizes and the average number of recursive subproblems per thread.
-The results are shown on the Fig.
+The results are shown in Fig.
 \ref{fig:performance}.
 
-	\begin{figure}[htb]
+	\begin{figure}[h]
 		\centering
@@
 
-	We`ve considered in details the process of designing and implementing the UAEM as well unified data structures for it.
+	We've considered in details the process of designing and implementing the UAEM as well as unified data structures for it.
 In this model a generic interface of a ``divide-and-conquer'' algorithm was created.
 This allows us to execute the algorithms which are implemented according to this model both sequentially and in parallel.
-Apart from that concatenable queue was implemented and served as the basis for the model described above.
+Apart from that a concatenable queue was implemented and served as the basis for the model described above.
 
-	Using the data structure allowed to significantly reduce the time and computational resources for solving set of problems, such as constructing the convex hull.
+	Using the data structure allowed to significantly reduce the time and computational resources for solving a set of problems, such as constructing the convex hull.
 The algorithmic environment was implemented in Java programming language using its standard library.
-The main advantages of the developed algorithm are optimized preprocessing stage and the efficiently implemented merge step, due to the usage of concatenable queue.
+The main advantages of the developed algorithm are an optimized preprocessing stage and the efficiently implemented merge step, due to the usage of concatenable queue.
 
 	The performance comparison for both types of execution allows to conclude that the algorithm has high level of parallelism.
-We`ve achieved speedup of $28\%$ in the best case.
+We've achieved speedup of $28\%$ in the best case.
 It is easy to extend functionality of the created environment either by adding new or modifying existing algorithms.

### 2020-03-27 eurocg20 EA/article-eurocg20-ea.tex
ComPE20, eurocg20

@@
 \begin{abstract}
-	This paper is devoted to the development and  of an efficient algorithmic model for solving a set of interrelated computational geometry problems.
-To do this, a unified algorithmic environment with unified data structures is created, which allows to implement complex use cases efficiently with respect to computational resources.
+	This paper is devoted to the development of an algorithmic model, which will be able to solve a set of interrelated computational geometry problems efficiently.
+To do this, an algorithmic environment with unified data structure is created, which allows to implement complex use cases efficiently with respect to computational resources.
 We build the environment on the basis of the ``divide and conquer'' strategy.
@@
 
-	Nowadays, advanced computer simulations and visualizing of complex scientific researches as well as large scale technical projects requires to simultaneously solve a set of problems.
+	Nowadays, advanced computer simulations and visualizations of complex scientific researches as well as large scale technical projects require to simultaneously solve a set of problems.
 To solve such problems it is needed to create suitable algorithmic frameworks, that would yield accurate results in real time.
@@
 Every such algorithm requires its own computational resources and is executed independently from others.
-In such case some identical steps, such as preprocessing and building data structures, are performed several times.
+In such cases some identical steps, such as preprocessing and building data structures, are performed several times.
 
-	Therefore, an important objective in developing the algorithmic models is to create a universal tool, which would have means to efficiently solve a set of problems.
-This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of the unified data structures.
+	Therefore, an important objective in developing algorithmic models is to create a universal tool, which would have means to efficiently solve a set of problems.
+This tool should also execute identical steps of the algorithms once and be able to represent results of those steps in a form of unified data structures.
 In \cite{tereshchenko} the notion of a unified algorithmic environment is introduced, which is based on the ``divide-and-conquer'' principle and takes into account the aforementioned features of the algorithms.
-In particular, the preprocessing and splitting the initial set of data to form the recursion tree is common for all problems and is executed only once.
+In particular, preprocessing and splitting the initial set of data to form recursion tree is common for all problems and is executed only once.
 During the merge stage intermediate results are maintained in a weighted concatenable queue.
@@
 \label{sec:unified-algorithmic-environment}
-\subsection{Algorithms stages}
+\subsection{Stages of the algorithms}
 
@@
 
-	In this section we describe the principle of how we decompose each algorithm into distinct parts.
+	In this section we described the principle of how we decompose each algorithm into distinct parts.
 This partition is then used to avoid repeating the computations in the algorithmic environment.
-The principle will be show on a convex hull algorithm which is similar to the one describe in \cite{overmars} but operates on a static set of points.
+The principle will be shown on a convex hull algorithm which is similar to the one describe in \cite{overmars} but operates on a static set of points.
 
 	The notion of a convex hull is simple.
-For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprise $S$.
-In practice to solve such problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
+For a set of points $S$ in a $k$-dimensional space it is a smallest convex set, that comprises $S$.
+In practice to solve such a problem, means to find a subset in $S$, which can be a "skeleton" for the convex hull.
+From now on we will consider the case where $k=2$.
 
@@
 For $a = (x_a, y_a)$ we denote $x(a)=x_a$, $y(a)=y_a$.
-Let points $a_1, a_2, ..., a_k$ lie on one horizontal line and $x(a_1) < x(a_2) <...
+Let the points $a_1, a_2, ..., a_k$ lie on one horizontal line and $x(a_1) < x(a_2) <...
 <x (a_k) $.
@@
 	Consider an algorithm that, in a sorted array, for each group of identical elements, deletes all but the first and the last one.
-The idea behind the algorithm is to use two pointers technique to delete repetitions by overwriting their place with other non-repeating element.
+The idea behind the algorithm is to use a two pointers technique to delete repetitions by overwriting their place with other non-repeating elements.
 At each step, constant work is performed to decide whether to overwrite the current item.
@@
 	At the stage of splitting the initial problem, the set of points is divided into left and right parts of equal size.
-Since a array-like data structure is used to store the points, this operations can be done in $O(1)$ by computing middle positiong in the array.
+Since an array-like data structure is used to store the points, this operations can be done in $O(1)$ by computing middle position of the array.
 
@@
 	The recursion stops when there are $2$ or $3$ elements in the array.
-First case is triial.
+The former case is trivial.
 To consider the base case of $3$ points, we introduce a notion of the tangent slope given by two points on the plane.
-For arbitrary points $a_1, a_2$ such that $x(a_1)<x(a_2)$ slope is denoted as $\lambda$:
+For arbitrary points $a_1, a_2$ such that $x(a_1)<x(a_2)$ their slope is denoted as $\lambda$:
 
@@
 	\end{equation}
-	According to this definition, the possible cases for points $a_1,a_2,a_3$ are given in Table \ref{table:3points}:
+	According to this definition, the possible cases for the points $a_1,a_2,a_3$ are given in Table \ref{table:3points}:
 
@@
 		\includegraphics[width=0.8\textwidth, height=0.3\textheight]{incorect_edge_points}
-		\caption{Example of a convex hull for a wrong position of the utmost left points of the left sub-hull}
+		\caption{Example of a convex hull for a wrong position of the utmost left point of the left sub-hull}
 		\label{fig:incorect_edge_points}
@@
 Fig.
-\ref{fig:correct_convex_hull} shows correct convex hull.
+\ref{fig:correct_convex_hull} shows the correct convex hull.
 
@@
 The construction of such an object requires the combination of an algorithmic database together with the necessary data structures.
-In fact, it is needed to create an interface of generic algorithm based on ``divide-and-conquer'' strategy, which will then be used on a specific input data.
+In fact, it is needed to create an interface for generic algorithms based on a ``divide-and-conquer'' strategy, which will then be used on specific input data.
 
-	The proposed generic interface for the ``divide-and-conquer'' algorithm is described on the Listing \ref{lst:algmodel}.
+	The proposed generic interface for the ``divide-and-conquer'' algorithm is described in Listing \ref{lst:algmodel}.
 
@@
 
-	To construct the concurrent execution algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$.
-which runs the functions $function1$ and $function2$ simultaneously.
-We use it to solve sub-problem obtained after splitting a given input.
+	To construct the concurrent execution algorithm, we use the following parallel computation abstraction $computeInParallel(function1, function2)$ which runs the functions $function1$ and $function2$ simultaneously.
+We use it to solve sub-problems obtained after splitting a given input.
 Other than that parallel version is identical to the sequential one.
 
-	Practically, from the implementation standpoint performance of parallel execution was improved by introducing a limit on the size of sub-tasks that can be calculated in parallel.
+	From the implementation standpoint, the performance of parallel execution was improved by introducing a limit on the size of sub-tasks that can be calculated in parallel.
 This allowed to put a threshold on the amount of work for one thread.
@@
 
-	As shown in \cite{overmars}, the concatenable queue is the key data structure for the algorithm described above and is therefore the basis for the UAEM.
+	As shown in \cite{overmars}, the concatenable queue is the key data structure for the algorithm described above and is therefore the basis for the unified algorithmic model.
 
-	Concatenable queue is an Abstract Data Type. Its operations are shown on Table \ref{table:cqueue-operations} together with theirs time complexities in our implementation:
+	Concatenable queue is an Abstract Data Type. Its operations are shown on Table \ref{table:cqueue-operations} together with their time complexities in our implementation:
 
 	\begin{table}[htbp]
-		\caption{Concatebable queue operations}
+		\caption{Concatenable queue operations}
 		\label{table:cqueue-operations}
@@
 Going back a new non-leaf vertex is created - the parent for the new element and one of its neighbor.
-The algorithm is formally described on the Listing \ref{lst:insert-alg}.
+The algorithm is formally described in Listing \ref{lst:insert-alg}.
 
-	%The algorithm of inserting an element in a queue is described on the Listing \ref{lst:insert-alg}.
+	%The algorithm of inserting an element in a queue is described in Listing \ref{lst:insert-alg}.
 
@@
 The value, by which the split has been performed, belongs to the left sub-queue.
-%	Its algorithm is described on the Listing \ref{lst:split-alg}.
+%	Its algorithm is described in Listing \ref{lst:split-alg}.
 
@@
 
-%	The algorithm of the $concatenateNodes$ procedure is described on the Listing \ref{lst:concatenate-als}.
+%	The algorithm of the $concatenateNodes$ procedure is described in Listing \ref{lst:concatenate-als}.
 
@@
 	A number of algorithm performance measurements were performed for different input sizes and the average number of recursive subproblems per thread.
-The results are shown on the Fig.
+The results are shown in Fig.
 \ref{fig:performance}.
@@
 
-	We`ve considered in details the process of designing and implementing the UAEM as well unified data structures for it.
+	We've considered in details the process of designing and implementing the unified algorithmic model as well as unified data structures for it.
 In this model a generic interface of a ``divide-and-conquer'' algorithm was created.
 This allows us to execute the algorithms which are implemented according to this model both sequentially and in parallel.
-Apart from that concatenable queue was implemented and served as the basis for the model described above.
+Apart from that a concatenable queue was implemented and served as the basis for the model described above.
 
-	Using the data structure allowed to significantly reduce the time and computational resources for solving set of problems, such as constructing the convex hull.
+	Using the data structure allowed to significantly reduce the time and computational resources for solving a set of problems, such as constructing the convex hull.
 The algorithmic environment was implemented in Java programming language using its standard library.
-The main advantages of the developed algorithm are optimized preprocessing stage and the efficiently implemented merge step, due to the usage of concatenable queue.
+The main advantages of the developed algorithm are an optimized preprocessing stage and the efficiently implemented merge step, due to the usage of concatenable queue.
 
